### 2018-10-29 README.Rmd
file structure as in Simon Maddisons workflow + some data

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# percolatransect

The goal of percolatransect is to try the percolation analysis as given by Simon Maddison with my own data.

### Citation

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Installation

You can install percolatransect from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("SCSchmidt/percolatransect")
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2018-10-29 paper.Rmd
file structure as in Simon Maddisons workflow + some data

---
title: "Title Goes Here"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(percolatransect) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

## here I document what I did and tried with the perlocation analysis by Simon Maddison

Frage: upper_ - and lower_threashold in radius_values.txt?

```{r}

```

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository("../..")
```

### 2018-10-29 R/cluster_frequency_script.v2.15.R

@@ -1,0 +1,243 @@
+# CLUSTER FREQENCY PLOTTING SCRIPT
+# Simon Maddison, 10th May 2015
+# Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs # of clusters
+# Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
+# Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
+# Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot 
+# 	(currently max size). Changed outputs to multi-page pdf files
+# Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
+# Version 2.5: 23/4/16 -
+#	Added in computations for clusters of single nodes
+# 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
+#	Table of max, mean and median exported
+# Version 2.6: 26/4/16 -
+# 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius, 
+# 	Exclude clusters with less than a certain threshold of nodes (parameter)
+# 	Also exclude largest cluster from mean
+# 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
+# Version 2.7: 29/4/16 -
+#	As per Elsa's published paper, plot max cluster size vs. radius as well
+# 	Page format improved to generate pdf A4 format
+# 	Bug fixed when adding clusters of size 1 (if null value)
+# Version 2.8: 4/5/16 - 
+#	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
+# Version 2.9: 6/5/16 -
+#	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
+# Version 2.10: 8/5/16 - source text file format changed to include map information
+# Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
+#	File is member_cluster_by_radius.csv
+# Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
+#	Make the image square or else it distorts the plot (note that this does not happen in pdf)
+# 	Remove simple cluster rank plots, no longer useful
[…]

### 2018-10-29 R/clustering_script.v3.4.R

@@ -1,0 +1,103 @@
+# CLUSTERING SCRIPT, RUNS AFTER NODES LIST SCRIPT
+# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+# Cite as:	arXiv:1504.08318 [physics.soc-ph]
+# Version 3
+# This is version 3, incorporating adjustments and enhancements to code 10/5/15 & 2/10/15
+# This code computes the clusters, based on matrix of inter-nodal distances computed in script
+#  	create_nodes_list_d.vxxx.R
+# Note that the list of nodes and internodal distances is not a complete matrix, but only includes
+# 	distances below a certain threshold. This keeps the data sizes manageable.
+# Note that the original used library bigmemory but this is not available for windows so all refs removed.
+# Note that when nodes are individual, they are no longer in a cluster. (31/1/16)
+# Version 3.1: 20/04/16 - Note that this intrinsically cannot generate clusters with only one node.
+#   	Need to post process means in the analysis script
+# Version 3.2: 6/5/16 - Changed Index name to fit within 8 chars -> PlcIndex
+# Version 3.3: 18/5/16 - output data into a single file, indexed on PlcIndex and radius instead of separate
+#	files. Read in PlcIndex.csv generated by create_nodes_list_d....R
+# Version 3.4: 7/11/17 - path of working directory amended for new PC
+
+library(igraph)
+setwd("D:/Iron_Age_Hillforts/Percolation")
+# paths
+path_source <- paste(getwd(),"/source_data",sep="")
+path_results <- paste(getwd(),"/working_data",sep="")
+data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
+
+# Read in list of site Indices; file created by create_nodes_list_d.R
+file_name <- paste(path_results,"/","PlcIndex.csv",sep="")
+# This is used as the basis for the output file
+mem_clust_by_r <- read.csv(file_name,header=TRUE)
+
+# Read in distance thresholds - this ensures same values used in all scripts
+# Edit the  file radius_values.txt to change these.
+file_name <- paste(path_results,"/","radius_values.txt",sep="")
+radius_values <- read.csv(file_name,header=TRUE)
+upper_radius <- radius_values$upper_radius
+lower_radius <- radius_values$lower_radius
+step_value <- radius_values$step_value
+
[…]

### 2018-10-29 R/create_nodes_list_d.v4.6.R

@@ -1,0 +1,133 @@
+# CREATE NODES LIST SCRIPT
+# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+# Cite as:	arXiv:1504.08318 [physics.soc-ph]
+# This is now version 3, incorporating corrections, performance and style improvements 10/5/15
+# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs, 
+# that is to say a partial matrix of distances between nodes.
+# Distances are computed for each node with each successive node, working through the list.
+# For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
+# This uses an approach that creates file with only distances below a limit, e.g. 100km. 
+# This will then not be a fully interconnected network; 
+# 	need to ensure that this does not adversely affect clustering computation.
+# Note original used the bigmemory library but this is not available for windows, so all refs removed.
+# Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
+# 	This data written out to text files.
+# Version 4.1: 4/4/2016 -
+# NOTE: problems with a matrix with #REF entries in .csv - 
+#	No check for this, and caused problems with matrix manipulation
+# Removed conversions to and from matrix data format for data, from original source. Not necessary
+# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also 
+#     that input data now has additional Lat Long fields added, which are not used here
+# Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
+# Version 4.4: 8/5/16 - Change of source text file format to include map data
+# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed 
+# Version 4.6: 07/11/17 - Change working directory for updated machine
+
+setwd("D:/Iron_Age_Hillforts/Percolation")
+# paths
+path_source <- paste(getwd(),"/source_data",sep="")
+path_results <- paste(getwd(),"/working_data",sep="")
+
+# Read in source file name defined in file source_file.txt
+file_name <- paste(path_results,"/","source_file.txt",sep="")
[…]

### 2018-10-29 R/create_nodes_list_d.v4.6_SCS.R

@@ -1,0 +1,132 @@
+# CREATE NODES LIST SCRIPT
+# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+# Cite as:	arXiv:1504.08318 [physics.soc-ph]
+# This is now version 3, incorporating corrections, performance and style improvements 10/5/15
+# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
+# that is to say a partial matrix of distances between nodes.
+# Distances are computed for each node with each successive node, working through the list.
+# For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
+# This uses an approach that creates file with only distances below a limit, e.g. 100km.
+# This will then not be a fully interconnected network;
+# 	need to ensure that this does not adversely affect clustering computation.
+# Note original used the bigmemory library but this is not available for windows, so all refs removed.
+# Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
+# 	This data written out to text files.
+# Version 4.1: 4/4/2016 -
+# NOTE: problems with a matrix with #REF entries in .csv -
+#	No check for this, and caused problems with matrix manipulation
+# Removed conversions to and from matrix data format for data, from original source. Not necessary
+# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
+#     that input data now has additional Lat Long fields added, which are not used here
+# Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
+# Version 4.4: 8/5/16 - Change of source text file format to include map data
+# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
+# Version 4.6: 07/11/17 - Change working directory for updated machine
+
+# paths
+path_source <- paste(getwd(),"/analysis/data/raw_data",sep="")
+path_results <- paste(getwd(),"/analysis/data/derived_data",sep="")
+
+# Read in source file name defined in file source_file.txt
+file_name <- paste(path_results,"/","source_file.txt",sep="")
[…]

### 2018-10-29 R/mapping_clusters.v4.10.R

@@ -1,0 +1,222 @@
+# CLUSTER MAPPING SCRIPT
+# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+# Cite as:	arXiv:1504.08318 [physics.soc-ph]
+# Version 3a: 10/5/15 & 2/10/15 - with additions to include county boundary outlines, 
+# This code maps the clusters overlaid on an outline of the British Isles or Ireland including county outlines
+# England and Wales shape files added from Portsmouth University files 31/1/16
+# Version 4: 24/3/16. Changes to plots made to:
+# 	Include identity of clusters (i.e.cluster index) in legend - done
+# 	Plot the source of the original data (e.g. Atlas, Hogg etc.) (taken from source file name)- done
+# 	Parameterise the shape file to be used for plotting ... 
+#	Take out graded grey colours for clusters > 15
+# Version 4.1: 29/3/16 changed outputs to be multi-page pdf
+#	NOTE: Ireland not plotting points TO BE RESOLVED
+# Version 4.2: 6/4/16 - error in plot of all site corrected; removed 'xy'; all refs now to xy_data
+# Version 4.3: 10/4/16 - output shape file with all data points, with same projection as input map
+#     NOTE: esri shape file driver truncates names to 10 characters but this should not be a
+#     problem at the moment. Prob of e.g. PlacesIndex, ClusterNumber etc.
+# 	shape file name is name of source file without .csv etc. extension
+# Version 4.4: 29/4/16 - paging upgraded to export to A4 and use the full page
+# Version 4.5: 6/5/16 - changed Index name to fit within 8 chars -> PlcIndex
+# Version 4.6: 8/5/16 - working on Ireland plot to fix. Problem seemed to be an old Ireland map with 
+#	an obsolete coordinate system
+#	Add in external input to country and shape file for source, 
+#	file is added to source_file.txt - map name and shape file name, headers also added
+#	source_file, map_name, shape_file
+#	REQUIRES CHANGE TO ALL OTHER PROGRAMS (done)
+# Version 4.7: 18/5/16 -  Cluster data now comes in a single file (member_cluster_by_radius.csv) 
+#   	output cluster ranks as new file site_cluster_rank_by_radius, lists by PlcIndex the cluster rank
+#	indexed by radius
[…]

### 2018-10-29 R/create_nodes_list_d.v4.6_SCS.R
ran first of four parts of analysis. need to continue

@@ -1,132 +1,0 @@
-# CREATE NODES LIST SCRIPT
-# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-# Cite as:	arXiv:1504.08318 [physics.soc-ph]
-# This is now version 3, incorporating corrections, performance and style improvements 10/5/15
-# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
-# that is to say a partial matrix of distances between nodes.
-# Distances are computed for each node with each successive node, working through the list.
-# For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
-# This uses an approach that creates file with only distances below a limit, e.g. 100km.
-# This will then not be a fully interconnected network;
-# 	need to ensure that this does not adversely affect clustering computation.
-# Note original used the bigmemory library but this is not available for windows, so all refs removed.
-# Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
-# 	This data written out to text files.
-# Version 4.1: 4/4/2016 -
-# NOTE: problems with a matrix with #REF entries in .csv -
-#	No check for this, and caused problems with matrix manipulation
-# Removed conversions to and from matrix data format for data, from original source. Not necessary
-# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
-#     that input data now has additional Lat Long fields added, which are not used here
-# Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
-# Version 4.4: 8/5/16 - Change of source text file format to include map data
-# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
-# Version 4.6: 07/11/17 - Change working directory for updated machine
-
-# paths
-path_source <- paste(getwd(),"/analysis/data/raw_data",sep="")
-path_results <- paste(getwd(),"/analysis/data/derived_data",sep="")
-
-# Read in source file name defined in file source_file.txt
-file_name <- paste(path_results,"/","source_file.txt",sep="")
[…]

### 2018-10-29 create_nodes_list_d.v4.6.R

@@ -2,28 +2,28 @@
 # Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
 # Cite as:	arXiv:1504.08318 [physics.soc-ph]
 # This is now version 3, incorporating corrections, performance and style improvements 10/5/15
-# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs, 
+# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
 # that is to say a partial matrix of distances between nodes.
 # Distances are computed for each node with each successive node, working through the list.
 # For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
-# This uses an approach that creates file with only distances below a limit, e.g. 100km. 
-# This will then not be a fully interconnected network; 
+# This uses an approach that creates file with only distances below a limit, e.g. 100km.
+# This will then not be a fully interconnected network;
 # 	need to ensure that this does not adversely affect clustering computation.
 # Note original used the bigmemory library but this is not available for windows, so all refs removed.
 # Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
 # 	This data written out to text files.
 # Version 4.1: 4/4/2016 -
-# NOTE: problems with a matrix with #REF entries in .csv - 
+# NOTE: problems with a matrix with #REF entries in .csv -
 #	No check for this, and caused problems with matrix manipulation
 # Removed conversions to and from matrix data format for data, from original source. Not necessary
-# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also 
+# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
 #     that input data now has additional Lat Long fields added, which are not used here
 # Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
 # Version 4.4: 8/5/16 - Change of source text file format to include map data
-# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed 
+# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
 # Version 4.6: 07/11/17 - Change working directory for updated machine
[…]

### 2019-06-05 paper.Rmd
begin plan paper - vergleich der datensätze untereinander
vergleich mit alten density funktionen?

@@
 
-## here I document what I did and tried with the perlocation analysis by Simon Maddison
+## different cluster analysis visualisation
 
-Frage: upper_ - and lower_threashold in radius_values.txt?
+Einladen der Daten und verbindung:
+```{r}
+sNL1 <- read_csv("analysis_results/sNL/1m_sNL/analysis_by_radius_sNL1.csv")
+sBZ1  <- read_csv("analysis_results/sBZ/sBZ_1m/analysis_by_radius.csv")
 
-```{r}
+sNL1$period  <- "Spätneolihitikum"
+sBZ1$period  <-  "Spätbronzezeit"
 
+radius1 <- rbind(sNL1,sBZ1)
+
+```
+
+## try new things
+
+```{r anzahl cluster}
+library(ggplot2)
+ggplot( data = radius1)+
+  geom_line(aes(x = radius, y = num_clust, col = period))
+```
+
+```{r max größe cluster}
+ggplot( data = radius1)+
+  geom_line(aes(x = radius, y = max_clust_size, col = period))
+```
+
+```{r mean cluster size}
+ggplot( data = radius1)+
+  geom_line(aes(x = radius, y = mean_clust_size, col = period))
+```
+
+```{r anzahl cluster}
+ggplot( data = radius1)+
+  geom_line(aes(x = radius, y = max_normalized, col = period))
+```
+# next point: Vergleich mit meinen density daten?
+
+# Idee: Daten einladen, teilen, etc, run source,
+
+copied from old:
+```{r message=FALSE, include=FALSE, cache=FALSE}
+
+#load data
+BefSchnitt <- read.csv2('../data/Schnittbefunde4.csv')
+
+# order dating
+BefSchnitt$epoche <- ordered(BefSchnitt$epoche, levels = c("Neolithikum", "Bronzezeit", "Eisenzeit", "undat."))
+BefSchnitt$abschnitt <- ordered(BefSchnitt$abschnitt, levels =c('aelter', 'frueh','mittel', 'spaet'))
+BefSchnitt$kultur <- ordered(BefSchnitt$kultur, levels=c("Baalberge", "Bernburg", "Kugelamphorenkultur", "Trichterbecher", "Salzmuende", "Schnurkeramik", "Glockenbecher", "Aunjetitz", "Saalemuendungsgruppe", "sBZ/aeEZ", "Hausurnenkultur"))
+
+library(maptools)
+library(spatstat)
+library(rgdal)
+library(ggplot2)
+library(pastecs)
+
+# subset settlement features
+
+siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
+
+#Subset for cultures
+siedlung_SnK_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
+siedlung_fBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='frueh')
+siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
+siedlung_aeEZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Eisenzeit' & siedlung_BefSchnitt$abschnitt=='aelter')
+siedlung_sBZaeEZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='sBZ/aeEZ')
+
+siedlung_sBZ_aeEZ <- rbind(siedlung_sBZaeEZ_Bef, siedlung_aeEZ_Bef)
+
+###2. create spatstat-Objects (> ppp(x.coordinates, y.coordinates, x.range, y.range bzw window))
+
+window <- readOGR(dsn='../data', layer='win_Schnitt')
+win <- as(window, "SpatialPolygons")
+W <-as(win, "owin")
+
+siedlung_SnK_Bef_pp <- ppp(siedlung_SnK_Bef$X, 
+ siedlung_SnK_Bef$Y, 
+ W)
+siedlung_fBZ_Bef_pp <- ppp(siedlung_fBZ_Bef$X, 
+ siedlung_fBZ_Bef$Y, 
+ W)
+siedlung_sBZ_Bef_pp <- ppp(siedlung_sBZ_Bef$X, 
+ siedlung_sBZ_Bef$Y, 
+ W)
+siedlung_aeEZ_Bef_pp <- ppp(siedlung_aeEZ_Bef$X, 
+  siedlung_aeEZ_Bef$Y, 
+  W)
+siedlung_sBZ_aeEZ_pp <-ppp(siedlung_sBZ_aeEZ$X,
+ siedlung_sBZ_aeEZ$Y,
+ W)
+
+# Warnung: dublicated points in sBZ und aeEZ.
+siedlung_sBZ_Bef_pp <- unique(siedlung_sBZ_Bef_pp) # dopplungen raus
+siedlung_aeEZ_Bef_pp <- unique(siedlung_aeEZ_Bef_pp) # dopplungen raus
+siedlung_sBZ_aeEZ_pp <- unique(siedlung_sBZ_aeEZ_pp) # dopplungen raus
+
+# calculate distance matrix and create vector and dataframe
+siedlSnK_dist_v <- sort(as.vector(pairdist.ppp(siedlung_SnK_Bef_pp)))# Entfernung aller SnK-Punkte zueinander
+siedlSnK_dist_v <-subset(siedlSnK_dist_v, siedlSnK_dist_v > 0) # 0-Werte raus
+siedlSnK_dist_df <- as.data.frame(siedlSnK_dist_v)
+
+siedlfBZ_dist_v <- sort(as.vector(pairdist.ppp(siedlung_fBZ_Bef_pp)))# Entfernung aller fBZ-Punkte zueinander
+siedlfBZ_dist_v <-subset(siedlfBZ_dist_v, siedlfBZ_dist_v > 0) # 0-Werte raus
+siedlfBZ_dist_df <- as.data.frame(siedlfBZ_dist_v)
+
+siedlsBZ_dist_v <- sort(as.vector(pairdist.ppp(siedlung_sBZ_Bef_pp)))# Entfernung aller sBZ-Punkte zueinander
+siedlsBZ_dist_v <-subset(siedlsBZ_dist_v, siedlsBZ_dist_v > 0) # 0-Werte raus
+siedlsBZ_dist_df <- as.data.frame(siedlsBZ_dist_v)
+
+siedlaeEZ_dist_v <-sort(as.vector(pairdist.ppp(siedlung_aeEZ_Bef_pp)))# Entfernung aller aeEZ-Punkte zueinander
+siedlaeEZ_dist_v <-subset(siedlaeEZ_dist_v, siedlaeEZ_dist_v > 0) # 0-Werte raus
+siedlaeEZ_dist_df <- as.data.frame(siedlaeEZ_dist_v)
+
+siedlsBZ_aeEZ_dist_v <- sort(as.vector(pairdist.ppp(siedlung_sBZ_aeEZ_pp )))# Entfernung aller sBZ/aeEZ-Punkte zueinander
+siedlsBZ_aeEZ_dist_v <-subset(siedlsBZ_aeEZ_dist_v, siedlsBZ_aeEZ_dist_v > 0) # 0-Werte raus
+siedlsBZ_aeEZ_dist_df <- as.data.frame(siedlsBZ_aeEZ_dist_v)
+
+# subset to only 1000m
+
+siedlSnK_dist_df_1000 <-subset(siedlSnK_dist_df, siedlSnK_dist_df > 0 & siedlSnK_dist_df < 1000 )
+
+siedlfBZ_dist_df_1000 <-subset(siedlfBZ_dist_df, siedlfBZ_dist_df > 0 & siedlfBZ_dist_df < 1000 )
+
+siedlsBZ_dist_df_1000 <-subset(siedlsBZ_dist_df, siedlsBZ_dist_df > 0 & siedlsBZ_dist_df < 1000 )
+
+siedlsBZ_aeEZ_dist_df_1000 <-subset(siedlsBZ_aeEZ_dist_df, siedlsBZ_aeEZ_dist_df > 0 & siedlsBZ_aeEZ_dist_df < 1000 )
+
+siedlsBZ_aeEZ_dist_df_1000 <-subset(siedlsBZ_aeEZ_dist_df, siedlsBZ_aeEZ_dist_df > 0 & siedlsBZ_aeEZ_dist_df < 1000 )
+
+# create cumulative sums and percentage of those
+
+siedlSnK_dist_df_1000$n <-c(1:nrow(siedlSnK_dist_df_1000)) # sagt, wie viele so oder kleiner (weil vorher nach Größe sortiert)
+siedlSnK_dist_df_1000$prozent <-c(siedlSnK_dist_df_1000$n/nrow(siedlSnK_dist_df_1000)) # macht aus der Anzahl eine Prozentanzahl zur Vergleichbarkeit
+
+siedlfBZ_dist_df_1000$n <-c(1:nrow(siedlfBZ_dist_df_1000))
+siedlfBZ_dist_df_1000$prozent <-c(siedlfBZ_dist_df_1000$n/nrow(siedlfBZ_dist_df_1000))
+
+siedlsBZ_dist_df_1000$n <-c(1:nrow(siedlsBZ_dist_df_1000))
+siedlsBZ_dist_df_1000$prozent <-c(siedlsBZ_dist_df_1000$n/nrow(siedlsBZ_dist_df_1000))
+
+siedlsBZ_aeEZ_dist_df_1000$n <-c(1:nrow(siedlsBZ_aeEZ_dist_df_1000))
+siedlsBZ_aeEZ_dist_df_1000$prozent <-c(siedlsBZ_aeEZ_dist_df_1000$n/nrow(siedlsBZ_aeEZ_dist_df_1000))
+
+siedlsBZ_aeEZ_dist_df_1000$n <-c(1:nrow(siedlsBZ_aeEZ_dist_df_1000))
+siedlsBZ_aeEZ_dist_df_1000$prozent <-c(siedlsBZ_aeEZ_dist_df_1000$n/nrow(siedlsBZ_aeEZ_dist_df_1000))
+
+```
+
+new:
+
+```{r anzahl cluster}
+ggplot( data = radius1)+
+  geom_line(aes(x = radius, y = max_normalized, col = period))+
+  geom_density()
 ```

### 2019-06-05 cluster_frequency_script.v2.16.R

@@ -46,7 +46,7 @@
 # 	each file is a list of Place indices, with the identity of each cluster
 # 	which it is a member of.
 
-setwd("E:/MA_Erweiterung/percolatransect")
+setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 # paths
 path_source <- paste(getwd(),"/source_data",sep="")
 path_working <- paste(getwd(),"/working_data",sep="")
@@ -209,3 +209,4 @@ for(cluster_min in cluster_min_values)
 
 	dev.off()
 }
+

### 2019-06-05 clustering_script.v3.6.R

@@ -22,7 +22,7 @@
 # 	NOTE: no modification necessary to work for fractional values of radius, e.g. step size of 0.1km???????????????
 
 library(igraph)
-setwd("E:/MA_Erweiterung/percolatransect")
+setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 # paths
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")

### 2019-06-05 create_nodes_list_d.v4.7.R

@@ -26,8 +26,7 @@
 #	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
 #	so that a unit value of 1 shows through as metres, and a value of 1000 as km. Other values accomodated
 
-setwd("E:/MA_Erweiterung/percolatransect")
-# paths
+setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")
 
@@ -53,7 +52,7 @@ radius_unit <- radius_values$radius_unit
 ptm <- proc.time()
 # For computation time
 
-data <- read.csv(source_file, sep = "\t") # added tab-seperated
+data <- read.csv(source_file, sep = ",") # crazy mistakes happen if this is wrong...
 # This file needs three columns: PlcIndex, Easting, Northing in this order.
 # Additional fields Lat Long not used for this program.
 # Note that the Easting and Northing need to be UK grid references with the Alphabetic

### 2019-06-05 data_prep.R

@@ -1,0 +1,29 @@
+#Data cleaning and prep for Sophie
+
+# load data
+BefSchnitt <- read.csv2('source_data/Schnittbefunde4.csv', sep = "\t", dec = ",")
+
+# bringing the periods in the right order
+BefSchnitt$epoche <- ordered(BefSchnitt$epoche, levels = c("Neolithikum", "Bronzezeit", "Eisenzeit", "undat."))
+BefSchnitt$abschnitt <- ordered(BefSchnitt$abschnitt, levels =c('aelter', 'frueh','mittel', 'spaet'))
+BefSchnitt$kultur <- ordered(BefSchnitt$kultur, levels=c("Baalberge", "Bernburg", "Kugelamphorenkultur", "Trichterbecher", "Salzmuende", "Schnurkeramik", "Glockenbecher", "Aunjetitz", "Saalemuendungsgruppe", "sBZ/aeEZ", "Hausurnenkultur"))
+
+# subset settlement features
+siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
+
+#Subset the settlement features for relevant cultures
+# there are 389 features dated as late bronze age and early iron age, that are being analysed in both epochs
+siedlung_SnK_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
+siedlung_SnK_Bef <-siedlung_SnK_Bef[c('PlcIndex', 'Easting', 'Northing')]
+write.csv(siedlung_SnK_Bef, "/home/sophie/Dokumente/Konferenzen/percolatransect/source_data/BefundesNL-minimal.csv", row.names = FALSE)
+
+siedlung_fBZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='frueh')
+siedlung_fBZ_Bef <-siedlung_fBZ_Bef[c("PlcIndex", 'Easting', 'Northing')]
+write.csv(siedlung_fBZ_Bef, "/home/sophie/Dokumente/Konferenzen/percolatransect/source_data/BefundefBZ-minimal.csv")
+
[…]

### 2019-06-05 mapping_clusters.v4.12.R

@@ -44,7 +44,7 @@ library(maptools)
 library(rgdal)
 library(stringr)
 
-setwd("E:/MA_Erweiterung/percolatransect")
+setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 # paths for results and output maps
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")

### 2019-06-25 paper.Rmd
updated mit hinweisen von simon

@@
 ---
-title: "Title Goes Here"
+title: "Percolation analysis of transect data"
 author:
-  - Author One
+  -Schmidt, Sophie C.
   - Author Two
@@
 output: 
-    bookdown::html_document2:
+    bookdown::word_document2:
       fig_caption: yes
       reference_docx: "../templates/template.docx" # Insert path for the DOCX file
-bibliography: references.bib
-csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
+
 abstract: |
@@
 
-library(percolatransect) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
+#library(percolatransect) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
 ```
+
+##
 
@@
 ```{r}
-sNL1 <- read_csv("analysis_results/sNL/1m_sNL/analysis_by_radius_sNL1.csv")
-sBZ1  <- read_csv("analysis_results/sBZ/sBZ_1m/analysis_by_radius.csv")
+#Data cleaning and prep for Sophie
+
+# load data
+BefSchnitt <- read.csv2('source_data/Schnittbefunde4.csv', sep = "\t", dec = ",")
+
+# bringing the periods in the right order
+BefSchnitt$epoche <- ordered(BefSchnitt$epoche, levels = c("Neolithikum", "Bronzezeit", "Eisenzeit", "undat."))
+BefSchnitt$abschnitt <- ordered(BefSchnitt$abschnitt, levels =c('aelter', 'frueh','mittel', 'spaet'))
+BefSchnitt$kultur <- ordered(BefSchnitt$kultur, levels=c("Baalberge", "Bernburg", "Kugelamphorenkultur", "Trichterbecher", "Salzmuende", "Schnurkeramik", "Glockenbecher", "Aunjetitz", "Saalemuendungsgruppe", "sBZ/aeEZ", "Hausurnenkultur"))
+
+# subset settlement features
+siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
+
+#Subset the settlement features for relevant cultures
+# there are 389 features dated as late bronze age and early iron age, that are being analysed in both epochs
+siedlung_SnK_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
+siedlung_SnK_Bef <-siedlung_SnK_Bef[c('PlcIndex', 'Easting', 'Northing')]
+write.csv(siedlung_SnK_Bef, "source_data/BefundesNL-minimal.csv", row.names = FALSE)
+
+siedlung_fBZ_Bef <- subset(siedlung_BefSchnitt,
+                           siedlung_BefSchnitt$epoche=='Bronzezeit' &
+                             siedlung_BefSchnitt$abschnitt=='frueh')
+siedlung_fBZ_Bef <- siedlung_fBZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
+write.csv(siedlung_fBZ_Bef, "source_data/BefundefBZ-minimal.csv", row.names = FALSE)
+
+siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
+siedlung_sBZ_Bef <-siedlung_sBZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
+write.csv(siedlung_sBZ_Bef, "source_data/BefundesBZ-minimal.csv")
+
+siedlung_sBZ_aeEZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Eisenzeit' & siedlung_BefSchnitt$abschnitt=='aelter')
+siedlung_sBZ_Bef <-siedlung_sBZ_aeEZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
+write.csv(siedlung_sBZ_Bef, "source_data/BefundesBZ_aeEZ-minimal.csv")
+
+```
+
+## run analysis and save results of every run.
+
+### input in source _file.txt
+source_file,map_name,shape_file_name,DTM_file_name
+BefundesNL-minimal.csv, late neolithic features, alle_Schnitt-Fundstellen.shp,
+
+source_file,map_name,shape_file_name,DTM_file_name
+BefundefBZ-minimal.csv, early bronze age features, alle_Schnitt-Fundstellen.shp,
+
+source_file,map_name,shape_file_name,DTM_file_name
+BefundesBZ-minimal.csv, late bronze age features, alle_Schnitt-Fundstellen.shp,
+
+source_file,map_name,shape_file_name,DTM_file_name
+BefundesBZ_aeEZ-minimal.csv, late bronze age to early iron age features, alle_Schnitt-Fundstellen.shp,
+
+### input in radius_values.txt (stays)
+
+upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
+500,2,1, 1000,0,0,1
+
+Außer bei der fBZ: da muss der minimale Radius 4 sein.
+## run code (each time new after changing source_file.txt and saving results somewhere)
+
+```{r}
+source("create_nodes_list_d.v4.7.R")
+source("clustering_script.v3.6.R")
+#source("mapping_clusters.v4.12.R")# Fehler in ogrInfo(dsn = dsn, layer = layer, encoding = encoding, use_iconv = use_iconv, : Cannot open data source...
+weeiiiiird...
+nochmal auf anderer Maschine testen.
+
+source("cluster_frequency_script.v2.16.R")
+
+```
+
+Jeweils die Daten in die vorgesehenen Ordnern verschieben.
+
+## für vergleichende plots:
+
+```{r combine all tables}
+library(utils)
+
+sNL1 <- read.csv("analysis_results/sNL/1m_sNL/analysis_by_radius.csv")
+fBZ1  <- read.csv("analysis_results/fBZ/analysis_by_radius.csv")
+sBZ1  <- read.csv("analysis_results/sBZ/sBZ_1m/analysis_by_radius.csv")
+aeEZ1  <- read.csv("analysis_results/aeEZ/analysis_by_radius.csv")
 
 sNL1$period  <- "Spätneolihitikum"
+fBZ1$period  <- "Frühbronzezeit"
 sBZ1$period  <-  "Spätbronzezeit"
+aeEZ1$period <- "ältere Eisenzeit"
 
-radius1 <- rbind(sNL1,sBZ1)
+radius1 <- rbind(sNL1,sBZ1, fBZ1, aeEZ1)
 
@@
 
-```{r anzahl cluster}
+```{r mean cluster size}
 library(ggplot2)
-ggplot( data = radius1)+
-  geom_line(aes(x = radius, y = num_clust, col = period))
-```
 
-```{r max größe cluster}
-ggplot( data = radius1)+
-  geom_line(aes(x = radius, y = max_clust_size, col = period))
-```
-
-```{r mean cluster size}
 ggplot( data = radius1)+
@@
 ```{r anzahl cluster}
+library(ggplot2)
 ggplot( data = radius1)+
-  geom_line(aes(x = radius, y = max_normalized, col = period))
+  geom_line(aes(x = radius, y = max_normalized, col = period))+
+  theme_light()+
+  labs(x ="percolation radius", y = "normalized maximum cluster size",
+       title = "Comparison of different time periods")
+
+ggsave("normalized_max_clusters.png", height = 10, width =  20, units = "cm", dpi = 300  )
+
 ```
+# auslesen der "knackpunkte"?
+
+```{r }
+## not happy with results here. esp. for EZ.
+# google terms: knee of curve, "trade off point"
+#https://dataplatform.cloud.ibm.com/analytics/notebooks/54d79c2a-f155-40ec-93ec-ed05b58afa39/view?access_token=6d8ec910cf2a1b3901c721fcb94638563cd646fe14400fecbb76cea6aaae2fb1
+
+#https://www.rdocumentation.org/packages/SamSPECTRAL/versions/1.26.0/topics/kneepointDetection
+
+points <-  c(1,1+which(diff(sNL1$max_normalized)!=0))
+
+sNL1points<- as.data.frame(cbind(sNL1$radius[points], sNL1$max_normalized[points]))
+
+pointssBZ <-  c(1,1+which(diff(sBZ1$max_normalized)!=0))
+
+sBZ1points<- as.data.frame(cbind(sBZ1$radius[pointssBZ], sBZ1$max_normalized[pointssBZ]))
+
+pointssBZ <-  c(1,1+which(diff(sBZ1$max_normalized)!=0))
+
+sBZ1points<- as.data.frame(cbind(sBZ1$radius[pointssBZ], sBZ1$max_normalized[pointssBZ]))
+
+pointsaeEZ <-c(1,1+which(diff(aeEZ1$max_normalized)!=0))
+aeEZpoints <-as.data.frame(cbind(aeEZ1$radius[pointsaeEZ],
+aeEZ1$max_normalized[pointsaeEZ]))
+
+ggplot()+
+  geom_line(data = radius1, aes(x = radius, y = max_normalized, col = period))+
+  geom_point(data = sNL1points, aes(x = sNL1points$V1,  y =sNL1points$V2), alpha = 0.5)+
+  geom_point(data = sBZ1points, aes(x=sBZ1points$V1, y=sBZ1points$V2), alpha = 0.5)+
+  geom_point(data = aeEZpoints, aes(x=aeEZpoints$V1, y=aeEZpoints$V2))
+
+```
+Die Points sind bereits wichtige Radii-Angaben, weil der URsprungsdatensatz ja auch einfach bei 1 = 1m anfängt.
+
+Welcher Knickpunkt ist wichtig? Wendepunkte berechnen:
+
+```{r}
+
+# calculate turning points of distance measure vectors
+
+#install.packages("ecp")
+library("ecp")
+
+turn_sNL <- e.divisive(as.matrix(diff(sNL1$max_normalized)), k = 1, min.size = nrow(sNL1)/10) #looks for change points, needs matrix, k number of changepoints estimated, min.size = minimum number of observations between change points -> decided to be a tenth of the number of observations so it's not every small change that's documented
+
+sNL_turn_r <-sNL1$radius[turn_sNL$estimates]
+
+# same late bronze age
+turn_sBZ <- e.divisive(as.matrix(diff(sBZ1$max_normalized)), k = 1, min.size = nrow(sBZ1)/10)
+
+sBZ_turn_r <-sBZ1$radius[turn_sBZ$estimates]
+
+# same early iron age
+aeEZ_turn  <- e.divisive(as.matrix(diff(aeEZ1$max_normalized)), k = 1, min.size = nrow(aeEZ1)/10)
+
+aeEZ_turn_r <- aeEZ1$radius[aeEZ_turn$estimates]
+
+```
+
+##Tabelle anschauen
+
+```{r}
+sNL_turn_r[2]
+sBZ_turn_r[2]
+aeEZ_turn_r[2]
+```
+
 # next point: Vergleich mit meinen density daten?
@@
 copied from old:
-```{r message=FALSE, include=FALSE, cache=FALSE}
+```{r eval=FALSE, message=FALSE, cache=FALSE, include=FALSE}
 
@@
 
-```{r anzahl cluster}
+```{r anzahl cluster2, eval=FALSE, include=FALSE}
 ggplot( data = radius1)+
@@
 ```
-
-The current Git commit details are:
-
-```{r}
-# what commit is this file at? You may need to change the path value
-# if your Rmd is not in analysis/paper/
-git2r::repository("../..")
-```

### 2019-06-25 cluster_frequency_script.v2.16.R

@@ -46,7 +46,7 @@
 # 	each file is a list of Place indices, with the identity of each cluster
 # 	which it is a member of.
 
-setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
+#setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 # paths
 path_source <- paste(getwd(),"/source_data",sep="")
 path_working <- paste(getwd(),"/working_data",sep="")

### 2019-06-25 clustering_script.v3.6.R

@@ -22,7 +22,7 @@
 # 	NOTE: no modification necessary to work for fractional values of radius, e.g. step size of 0.1km???????????????
 
 library(igraph)
-setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
+#setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 # paths
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")

### 2019-06-25 create_nodes_list_d.v4.7.R

@@ -26,7 +26,7 @@
 #	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
 #	so that a unit value of 1 shows through as metres, and a value of 1000 as km. Other values accomodated
 
-setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
+#setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")
 

### 2019-06-25 data_prep.R

@@ -15,15 +15,18 @@ siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
 # there are 389 features dated as late bronze age and early iron age, that are being analysed in both epochs
 siedlung_SnK_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
 siedlung_SnK_Bef <-siedlung_SnK_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_SnK_Bef, "/home/sophie/Dokumente/Konferenzen/percolatransect/source_data/BefundesNL-minimal.csv", row.names = FALSE)
+write.csv(siedlung_SnK_Bef, "source_data/BefundesNL-minimal.csv", row.names = FALSE)
 
 siedlung_fBZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='frueh')
 siedlung_fBZ_Bef <-siedlung_fBZ_Bef[c("PlcIndex", 'Easting', 'Northing')]
-write.csv(siedlung_fBZ_Bef, "/home/sophie/Dokumente/Konferenzen/percolatransect/source_data/BefundefBZ-minimal.csv")
+write.csv(siedlung_fBZ_Bef, "source_data/BefundefBZ-minimal.csv")
 
 siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
 siedlung_sBZ_Bef <-siedlung_sBZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_sBZ_Bef, "/home/sophie/Dokumente/Konferenzen/percolatransect/source_data/BefundesBZ-minimal.csv")
+write.csv(siedlung_sBZ_Bef, "source_data/BefundesBZ-minimal.csv")
 
 
-#siedlung_sBZ_aeEZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Eisenzeit' & siedlung_BefSchnitt$abschnitt=='ael
[…]

### 2019-06-25 mapping_clusters.v4.12.R

@@ -44,7 +44,7 @@ library(maptools)
 library(rgdal)
 library(stringr)
 
-setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
+#setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
 # paths for results and output maps
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")

### 2019-07-11 paper.Rmd
übertragung des papers ins Rmd. plan: redoc ausprobieren!

@@
 
-##
+### Strip excavation in Germany
+The second case study is located in Saxony-Anhalt, middle Germany.
+During the early 2000s the street “Bundesstraße 6” was built near the town of Köthen.
+The area of the street, approach roads, exits and retention reservoirs were machine test trenched by the Heritage Management to find archaeological sites.
+Along the ca.
+13 km long and mostly 40 m broad part of the street over 6000 features were uncovered (Fahr in prep.), but I will focus on features from four different time periods: The late Neolithic (represented by Corded Ware Culture), early Bronze Age (Unetice culture), later Bronze Age (group “Saalemündungsgruppe”) and early Iron Age (group “Hausurnenkultur”).
+For these periods the aim is to find the clusters which delineate a site with the help of percolation analysis.
+The radius will estimate the distance between features that belong together into one site.
 
-## different cluster analysis visualisation
+#### Data set
 
-Einladen der Daten und verbindung:
 ```{r}
@@
 siedlung_sBZ_aeEZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Eisenzeit' & siedlung_BefSchnitt$abschnitt=='aelter')
-siedlung_sBZ_Bef <-siedlung_sBZ_aeEZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_sBZ_Bef, "source_data/BefundesBZ_aeEZ-minimal.csv")
+siedlung_sBZ_aeEZ_Bef <- siedlung_sBZ_aeEZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
+write.csv(siedlung_sBZ_aeEZ_Bef, "source_data/BefundesBZ_aeEZ-minimal.csv")
 
 ```
+
+There are 1595 features cataloged as belonging to these periods (specific number of features belonging to the periods cf table x).
+
+Epoch               |	Culture                              |	n settlement  features
+Neolithic	          |Schnurkeramik (Corded Ware Culture)             |	34
+Bronze Age          |	Aunjetitz (Unetice Culture)	                    | 25
+Bronze Age          |	Saalemündungsgruppe (River Saale Outfall Group) |	1005
+Bronze Age/Iron Age |	Late Bronze Age / early Iron Age                |	389
+Iron Age            |	Hausurnenkultur (House Urn Culture)	            | 129
+Iron Age            |	NA                                              |	13
+sum	                |                                                 |	1595
+
+Because of the test trenching it is assumed, that all features and sites along the transect have been found, even though there are gaps between the actual excavation areas and many features remain undated.
+Machine trenching has been shown to be the most effective way to find sites [@hey_2006].
+Admittedly even then not all sites are discovered, especially Neolithic ones have the least probability to be found, which may be one reason for the small number of Neolithic features in the transect.
+The late Bronze age and the early iron age are not easily seperable in the settlements, because the ceramics are very similar.
+Researchers agree [@wagner_2004, 8 ; @heske_2005, 95] that there seems to be a settlement continuation between the two phases, while the burial practices change.
+Consequently many features have been dated in both periods.
+I deal with this by adding the uncertainly dated features to the late bronze age analysis as well as to the early iron age analysis.
+
+#### Theoretical Issues
+The term “site” has been at the center of a lively debate in survey archaeology over the last 40 years.
+Until the 70’s it has mostly been defined as a place [@dunnell_1992, 23-24] - a find spot, which is similar to German archaeology, where the term used, “Fundplatz”, means exactly that.
+In the German archaeological inventories, though, a site may contain several culturally distinct loci “Fundstellen” [@dauber_1950, 96], which are usually cataloged as a settlement, a burial ground, a hoard or as a single find spot of a period [@eggert_2005, 56].
+Two questions arise, when deciding how to classify a site as a settlement: Qualitatively, what kind of finds or features define a settlement [@linke_1976, 8], and quantitatively, of how far apart two “find spots” are supposed to be.
+If two sherds of the same time period are found 50 m apart - are these two sites or belong they to one site?
+In every larger settlement or landscape archaeological study this topic is being discussed and in the end a decision felled, which the authors agree, is kind of arbitrary and should actually rely on empiric studies [@malmer_1962; @mischka_2007].
+Since the middle of the 1970s there has been the discussion of a non- or off-site approach to anglophone archaeology.
+The terms were introduced by Thomas [-@thomas_1975] and Foley [-@foley_1981] and describe the analysis of finds "between sites".
+This approach understands the archaeological record  as a continual distribution in space, with spots of higher densities, the so-called “sites”, and areas of lower density [@wobst_1983, 39].
+At this point the continuously excavated data set of the street and the clustering analysis percolation can be fruitfully connected: As percolation works with radii around points it may assist in quantitatively assessing which distances between features are common.
+Assuming a connection between underground features and surface finds enables us to transfer the distances of the features to those of finds and may inform landscape archaeological surveys on the decision on attributing single finds to an already known site or registering a new site.
+Of course, settlement features only comprise the “build space” of a settlement.
+Though features in-between sites may exist, like traps or temporary storage facilities, places like working areas or fields which may be detected by off-site surface find distributions, won’t be included.
+
+### Percolation
+
+```{r eval=FALSE, include=FALSE}
 
@@
 
-```{r}
 source("create_nodes_list_d.v4.7.R")
@@
 
-Jeweils die Daten in die vorgesehenen Ordnern verschieben.
+```{r combine all tables}
+#Jeweils die Daten in die vorgesehenen Ordnern verschieben.
 
@@
 
-```{r combine all tables}
 library(utils)
@@
 
-sNL1$period  <- "Spätneolihitikum"
+sNL1$period  <- "Spätneolithikum"
 fBZ1$period  <- "Frühbronzezeit"
@@
 
-## try new things
+As this analysis is concerned with a very fine level of detail, the starting point and the step size of the percolation algorithm was chosen to be 1m.
+Only in case of the Unetice Culture a larger starting radius of 4m was chosen, because the smallest distance of features to each other in this time period is 4 m.
+The size of a prehistoric village in middle Germany can’t be assumed to be larger than a kilometer in diameter, therefore the largest radius used was 500m. 
+For the four different time periods different patterns of cluster development could be detected, which conforms to an assumption of differing settlement strategies through the times.
+They are visualised together in figure xyz
 
-```{r mean cluster size}
+```{r mean cluster size, eval=FALSE, include=FALSE}
 library(ggplot2)
-
+# not included because the mean cluster size ist too different because of hugely different sample sizes
 ggplot( data = radius1)+
@@
   labs(x ="percolation radius", y = "normalized maximum cluster size",
-       title = "Comparison of different time periods")
+       title = "Comparison of different time periods")+
+  scale_color_discrete(breaks = c("Spätneolithikum", "Frühbronzezeit", "Spätbronzezeit", "ältere Eisenzeit"),
+                       labels = c("late Neolithic", "early Bronze Age", "late Bronze Age", "early Iron Age"))
 
@@
 ```
-# auslesen der "knackpunkte"?
+
+To the naked eye it is visible that there are different turning points at which the distribution flattens.
+This is a sign of different levels of clustering inside the sites.
+The final flattening might be interpreted as the algorithm running out of features to add to the clusters.
+We thereby find the edges of settlements and can define their size.
+
+to do: maps!!
+
+```{r}
+# Idee: wenn n+1 - n > 10 oder so --> großer step
+
+trial_points_sNL <-  c(1,1+which(diff(sNL1$max_normalized) > 0.1))
+trial_points_fBZ <-  c(1,1+which(diff(fBZ1$max_normalized) > 0.1))
+trial_points_sBZ <-  c(1,1+which(diff(sBZ1$max_normalized) > 0.1))
+trial_points_aeEZ<-  c(1,1+which(diff(aeEZ1$max_normalized) > 0.1))
+
+```
 
@@
 
+## Idee: points aufsteigend sortieren... also die Abstände zwischen zwei aufeinanderfolgenden max_normalized sotieren. die größten Abstände raussuchen, die als Knackpunkte definieren?
+points <- order(points)
+
 sNL1points<- as.data.frame(cbind(sNL1$radius[points], sNL1$max_normalized[points]))
@@
 pointssBZ <-  c(1,1+which(diff(sBZ1$max_normalized)!=0))
-
 sBZ1points<- as.data.frame(cbind(sBZ1$radius[pointssBZ], sBZ1$max_normalized[pointssBZ]))

### 2019-07-15 paper.Rmd
Interpretationsbeginn. Idee: nur sBZ ?

@@
 To the naked eye it is visible that there are different turning points at which the distribution flattens.
-This is a sign of different levels of clustering inside the sites.
-The final flattening might be interpreted as the algorithm running out of features to add to the clusters.
+This is a sign of different settlement strategies.
+Also we can find several levels of clustering.
+Especially features of the late Bronze Age and early Iron Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
+Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
 We thereby find the edges of settlements and can define their size.
+The step-wise rises at higher percolation radii needs explanation as well.
+To provide these, the results will be compared to large scale excavations of settlements in middle Germany.
+For interpretation I will now discuss the time slices seperately:
+
+#### Late Neolithic
+
+#### Early Bronze Age
+
+#### Late Bronze Age
+
+#### Early Iron Age
 

### 2019-07-15 paper.Rmd
sBZ: alles andere raus. nochmal alle cluster berechnet. wieder problem with maps. weird. -.-

@@
 Along the ca.
-13 km long and mostly 40 m broad part of the street over 6000 features were uncovered (Fahr in prep.), but I will focus on features from four different time periods: The late Neolithic (represented by Corded Ware Culture), early Bronze Age (Unetice culture), later Bronze Age (group “Saalemündungsgruppe”) and early Iron Age (group “Hausurnenkultur”).
-For these periods the aim is to find the clusters which delineate a site with the help of percolation analysis.
+13 km long and mostly 40 m broad part of the street over 6000 features were uncovered (Fahr in prep.), but I will focus on features from the later Bronze Age (group “Saalemündungsgruppe”).
+For this periods the aim is to find the clusters which delineate a site with the help of percolation analysis.
 The radius will estimate the distance between features that belong together into one site.
@@
 #Subset the settlement features for relevant cultures
-# there are 389 features dated as late bronze age and early iron age, that are being analysed in both epochs
-siedlung_SnK_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
-siedlung_SnK_Bef <-siedlung_SnK_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_SnK_Bef, "source_data/BefundesNL-minimal.csv", row.names = FALSE)
-
-siedlung_fBZ_Bef <- subset(siedlung_BefSchnitt,
-                           siedlung_BefSchnitt$epoche=='Bronzezeit' &
-                             siedlung_BefSchnitt$abschnitt=='frueh')
-siedlung_fBZ_Bef <- siedlung_fBZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_fBZ_Bef, "source_data/BefundefBZ-minimal.csv", row.names = FALSE)
-
+# there are 389 features dated as late bronze age and early iron age, that are being analysed in sBZ as well
 siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
@@
 
-siedlung_sBZ_aeEZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Eisenzeit' & siedlung_BefSchnitt$abschnitt=='aelter')
-siedlung_sBZ_aeEZ_Bef <- siedlung_sBZ_aeEZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_sBZ_aeEZ_Bef, "source_data/BefundesBZ_aeEZ-minimal.csv")
-
 ```
 
-There are 1595 features cataloged as belonging to these periods (specific number of features belonging to the periods cf table x).
-
-Epoch               |	Culture                              |	n settlement  features
-Neolithic	          |Schnurkeramik (Corded Ware Culture)             |	34
-Bronze Age          |	Aunjetitz (Unetice Culture)	                    | 25
-Bronze Age          |	Saalemündungsgruppe (River Saale Outfall Group) |	1005
-Bronze Age/Iron Age |	Late Bronze Age / early Iron Age                |	389
-Iron Age            |	Hausurnenkultur (House Urn Culture)	            | 129
-Iron Age            |	NA                                              |	13
-sum	                |                                                 |	1595
+There are 1005 settlement features cataloged as belonging to this period.
 
@@
 Consequently many features have been dated in both periods.
-I deal with this by adding the uncertainly dated features to the late bronze age analysis as well as to the early iron age analysis.
+I deal with this by adding the uncertainly dated features to the late bronze age analysis as well.
 
@@
 ### input in source _file.txt
-source_file,map_name,shape_file_name,DTM_file_name
-BefundesNL-minimal.csv, late neolithic features, alle_Schnitt-Fundstellen.shp,
-
-source_file,map_name,shape_file_name,DTM_file_name
-BefundefBZ-minimal.csv, early bronze age features, alle_Schnitt-Fundstellen.shp,
 
@@
 BefundesBZ-minimal.csv, late bronze age features, alle_Schnitt-Fundstellen.shp,
-
-source_file,map_name,shape_file_name,DTM_file_name
-BefundesBZ_aeEZ-minimal.csv, late bronze age to early iron age features, alle_Schnitt-Fundstellen.shp,
 
@@
 
-Außer bei der fBZ: da muss der minimale Radius 4 sein.
-## run code (each time new after changing source_file.txt and saving results somewhere)
-
 source("create_nodes_list_d.v4.7.R")
 source("clustering_script.v3.6.R")
-#source("mapping_clusters.v4.12.R")# Fehler in ogrInfo(dsn = dsn, layer = layer, encoding = encoding, use_iconv = use_iconv, : Cannot open data source...
+source("mapping_clusters.v4.12.R")# Fehler in ogrInfo(dsn = dsn, layer = layer, encoding = encoding, use_iconv = use_iconv, : Cannot open data source...
 weeiiiiird...
@@
 
-```{r combine all tables}
-#Jeweils die Daten in die vorgesehenen Ordnern verschieben.
-
-## für vergleichende plots:
-
-library(utils)
-
-sNL1 <- read.csv("analysis_results/sNL/1m_sNL/analysis_by_radius.csv")
-fBZ1  <- read.csv("analysis_results/fBZ/analysis_by_radius.csv")
-sBZ1  <- read.csv("analysis_results/sBZ/sBZ_1m/analysis_by_radius.csv")
-aeEZ1  <- read.csv("analysis_results/aeEZ/analysis_by_radius.csv")
-
-sNL1$period  <- "Spätneolithikum"
-fBZ1$period  <- "Frühbronzezeit"
-sBZ1$period  <-  "Spätbronzezeit"
-aeEZ1$period <- "ältere Eisenzeit"
-
-radius1 <- rbind(sNL1,sBZ1, fBZ1, aeEZ1)
-
-```
-
 As this analysis is concerned with a very fine level of detail, the starting point and the step size of the percolation algorithm was chosen to be 1m.
@@
 The size of a prehistoric village in middle Germany can’t be assumed to be larger than a kilometer in diameter, therefore the largest radius used was 500m.
-For the four different time periods different patterns of cluster development could be detected, which conforms to an assumption of differing settlement strategies through the times.
-They are visualised together in figure xyz
 
@@
   labs(x ="percolation radius", y = "normalized maximum cluster size",
-       title = "Comparison of different time periods")+
-  scale_color_discrete(breaks = c("Spätneolithikum", "Frühbronzezeit", "Spätbronzezeit", "ältere Eisenzeit"),
-                       labels = c("late Neolithic", "early Bronze Age", "late Bronze Age", "early Iron Age"))
+       title = "Cluster sizes in respect to percolation radius")
 
-ggsave("normalized_max_clusters.png", height = 10, width =  20, units = "cm", dpi = 300  )
+ggsave("normalized_max_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 300  )
 
@@
 
-To the naked eye it is visible that there are different turning points at which the distribution flattens.
-This is a sign of different settlement strategies.
-Also we can find several levels of clustering.
-Especially features of the late Bronze Age and early Iron Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
+There are several levels of clustering.
+Features of the late Bronze Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
 Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
@@
 To provide these, the results will be compared to large scale excavations of settlements in middle Germany.
-For interpretation I will now discuss the time slices seperately:
-
-#### Late Neolithic
-
-#### Early Bronze Age
-
-#### Late Bronze Age
-
-#### Early Iron Age
-
-to do: maps!!
 
@@
 
-trial_points_sNL <-  c(1,1+which(diff(sNL1$max_normalized) > 0.1))
-trial_points_fBZ <-  c(1,1+which(diff(fBZ1$max_normalized) > 0.1))
 trial_points_sBZ <-  c(1,1+which(diff(sBZ1$max_normalized) > 0.1))
-trial_points_aeEZ<-  c(1,1+which(diff(aeEZ1$max_normalized) > 0.1))
 
@@
 
-sNL1points<- as.data.frame(cbind(sNL1$radius[points], sNL1$max_normalized[points]))
-
-pointssBZ <-  c(1,1+which(diff(sBZ1$max_normalized)!=0))
-sBZ1points<- as.data.frame(cbind(sBZ1$radius[pointssBZ], sBZ1$max_normalized[pointssBZ]))
-
 pointssBZ <-  c(1,1+which(diff(sBZ1$max_normalized)!=0))
@@
 
-pointsaeEZ <-c(1,1+which(diff(aeEZ1$max_normalized)!=0))
-aeEZpoints <-as.data.frame(cbind(aeEZ1$radius[pointsaeEZ],
-aeEZ1$max_normalized[pointsaeEZ]))
-
 ggplot()+
   geom_line(data = radius1, aes(x = radius, y = max_normalized, col = period))+
-  geom_point(data = sNL1points, aes(x = sNL1points$V1,  y =sNL1points$V2), alpha = 0.5)+
-  geom_point(data = sBZ1points, aes(x=sBZ1points$V1, y=sBZ1points$V2), alpha = 0.5)+
   geom_point(data = aeEZpoints, aes(x=aeEZpoints$V1, y=aeEZpoints$V2))
@@
 
-turn_sNL <- e.divisive(as.matrix(diff(sNL1$max_normalized)), k = 1, min.size = nrow(sNL1)/10) #looks for change points, needs matrix, k number of changepoints estimated, min.size = minimum number of observations between change points -> decided to be a tenth of the number of observations so it's not every small change that's documented
-
-sNL_turn_r <-sNL1$radius[turn_sNL$estimates]
-
 # same late bronze age
@@
 sBZ_turn_r <-sBZ1$radius[turn_sBZ$estimates]
-
-# same early iron age
-aeEZ_turn  <- e.divisive(as.matrix(diff(aeEZ1$max_normalized)), k = 1, min.size = nrow(aeEZ1)/10)
-
-aeEZ_turn_r <- aeEZ1$radius[aeEZ_turn$estimates]
 
@@
 ```{r}
-sNL_turn_r[2]
 sBZ_turn_r[2]
-aeEZ_turn_r[2]
-```
-
-# next point: Vergleich mit meinen density daten?
-
-# Idee: Daten einladen, teilen, etc, run source,
-
-copied from old:
-```{r eval=FALSE, message=FALSE, cache=FALSE, include=FALSE}
-
-#load data
-BefSchnitt <- read.csv2('../data/Schnittbefunde4.csv')
-
-# order dating
-BefSchnitt$epoche <- ordered(BefSchnitt$epoche, levels = c("Neolithikum", "Bronzezeit", "Eisenzeit", "undat."))
-BefSchnitt$abschnitt <- ordered(BefSchnitt$abschnitt, levels =c('aelter', 'frueh','mittel', 'spaet'))
-BefSchnitt$kultur <- ordered(BefSchnitt$kultur, levels=c("Baalberge", "Bernburg", "Kugelamphorenkultur", "Trichterbecher", "Salzmuende", "Schnurkeramik", "Glockenbecher", "Aunjetitz", "Saalemuendungsgruppe", "sBZ/aeEZ", "Hausurnenkultur"))
-
-library(maptools)
-library(spatstat)
-library(rgdal)
-library(ggplot2)
-library(pastecs)
-
-# subset settlement features
-
-siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
-
-#Subset for cultures
-siedlung_SnK_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
-siedlung_fBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='frueh')
-siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
-siedlung_aeEZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Eisenzeit' & siedlung_BefSchnitt$abschnitt=='aelter')
-siedlung_sBZaeEZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='sBZ/aeEZ')
-
-siedlung_sBZ_aeEZ <- rbind(siedlung_sBZaeEZ_Bef, siedlung_aeEZ_Bef)
-
-###2. create spatstat-Objects (> ppp(x.coordinates, y.coordinates, x.range, y.range bzw window))
-
-window <- readOGR(dsn='../data', layer='win_Schnitt')
-win <- as(window, "SpatialPolygons")
-W <-as(win, "owin")
-
-siedlung_SnK_Bef_pp <- ppp(siedlung_SnK_Bef$X, 
- siedlung_SnK_Bef$Y, 
- W)
-siedlung_fBZ_Bef_pp <- ppp(siedlung_fBZ_Bef$X, 
- siedlung_fBZ_Bef$Y, 
- W)
-siedlung_sBZ_Bef_pp <- ppp(siedlung_sBZ_Bef$X, 
- siedlung_sBZ_Bef$Y, 
- W)
-siedlung_aeEZ_Bef_pp <- ppp(siedlung_aeEZ_Bef$X, 
-  siedlung_aeEZ_Bef$Y, 
-  W)
-siedlung_sBZ_aeEZ_pp <-ppp(siedlung_sBZ_aeEZ$X,
- siedlung_sBZ_aeEZ$Y,
- W)
-
-# Warnung: dublicated points in sBZ und aeEZ.
-siedlung_sBZ_Bef_pp <- unique(siedlung_sBZ_Bef_pp) # dopplungen raus
-siedlung_aeEZ_Bef_pp <- unique(siedlung_aeEZ_Bef_pp) # dopplungen raus
-siedlung_sBZ_aeEZ_pp <- unique(siedlung_sBZ_aeEZ_pp) # dopplungen raus
-
-# calculate distance matrix and create vector and dataframe
-siedlSnK_dist_v <- sort(as.vector(pairdist.ppp(siedlung_SnK_Bef_pp)))# Entfernung aller SnK-Punkte zueinander
-siedlSnK_dist_v <-subset(siedlSnK_dist_v, siedlSnK_dist_v > 0) # 0-Werte raus
-siedlSnK_dist_df <- as.data.frame(siedlSnK_dist_v)
-
-siedlfBZ_dist_v <- sort(as.vector(pairdist.ppp(siedlung_fBZ_Bef_pp)))# Entfernung aller fBZ-Punkte zueinander
-siedlfBZ_dist_v <-subset(siedlfBZ_dist_v, siedlfBZ_dist_v > 0) # 0-Werte raus
-siedlfBZ_dist_df <- as.data.frame(siedlfBZ_dist_v)
-
-siedlsBZ_dist_v <- sort(as.vector(pairdist.ppp(siedlung_sBZ_Bef_pp)))# Entfernung aller sBZ-Punkte zueinander
-siedlsBZ_dist_v <-subset(siedlsBZ_dist_v, siedlsBZ_dist_v > 0) # 0-Werte raus
-siedlsBZ_dist_df <- as.data.frame(siedlsBZ_dist_v)
-
-siedlaeEZ_dist_v <-sort(as.vector(pairdist.ppp(siedlung_aeEZ_Bef_pp)))# Entfernung aller aeEZ-Punkte zueinander
-siedlaeEZ_dist_v <-subset(siedlaeEZ_dist_v, siedlaeEZ_dist_v > 0) # 0-Werte raus
-siedlaeEZ_dist_df <- as.data.frame(siedlaeEZ_dist_v)
-
-siedlsBZ_aeEZ_dist_v <- sort(as.vector(pairdist.ppp(siedlung_sBZ_aeEZ_pp )))# Entfernung aller sBZ/aeEZ-Punkte zueinander
-siedlsBZ_aeEZ_dist_v <-subset(siedlsBZ_aeEZ_dist_v, siedlsBZ_aeEZ_dist_v > 0) # 0-Werte raus
-siedlsBZ_aeEZ_dist_df <- as.data.frame(siedlsBZ_aeEZ_dist_v)
-
-# subset to only 1000m
-
-siedlSnK_dist_df_1000 <-subset(siedlSnK_dist_df, siedlSnK_dist_df > 0 & siedlSnK_dist_df < 1000 )
-
-siedlfBZ_dist_df_1000 <-subset(siedlfBZ_dist_df, siedlfBZ_dist_df > 0 & siedlfBZ_dist_df < 1000 )
-
-siedlsBZ_dist_df_1000 <-subset(siedlsBZ_dist_df, siedlsBZ_dist_df > 0 & siedlsBZ_dist_df < 1000 )
-
-siedlsBZ_aeEZ_dist_df_1000 <-subset(siedlsBZ_aeEZ_dist_df, siedlsBZ_aeEZ_dist_df > 0 & siedlsBZ_aeEZ_dist_df < 1000 )
-
-siedlsBZ_aeEZ_dist_df_1000 <-subset(siedlsBZ_aeEZ_dist_df, siedlsBZ_aeEZ_dist_df > 0 & siedlsBZ_aeEZ_dist_df < 1000 )
-
-# create cumulative sums and percentage of those
-
-siedlSnK_dist_df_1000$n <-c(1:nrow(siedlSnK_dist_df_1000)) # sagt, wie viele so oder kleiner (weil vorher nach Größe sortiert)
-siedlSnK_dist_df_1000$prozent <-c(siedlSnK_dist_df_1000$n/nrow(siedlSnK_dist_df_1000)) # macht aus der Anzahl eine Prozentanzahl zur Vergleichbarkeit
-
-siedlfBZ_dist_df_1000$n <-c(1:nrow(siedlfBZ_dist_df_1000))
-siedlfBZ_dist_df_1000$prozent <-c(siedlfBZ_dist_df_1000$n/nrow(siedlfBZ_dist_df_1000))
-
-siedlsBZ_dist_df_1000$n <-c(1:nrow(siedlsBZ_dist_df_1000))
-siedlsBZ_dist_df_1000$prozent <-c(siedlsBZ_dist_df_1000$n/nrow(siedlsBZ_dist_df_1000))
-
-siedlsBZ_aeEZ_dist_df_1000$n <-c(1:nrow(siedlsBZ_aeEZ_dist_df_1000))
-siedlsBZ_aeEZ_dist_df_1000$prozent <-c(siedlsBZ_aeEZ_dist_df_1000$n/nrow(siedlsBZ_aeEZ_dist_df_1000))
-
-siedlsBZ_aeEZ_dist_df_1000$n <-c(1:nrow(siedlsBZ_aeEZ_dist_df_1000))
-siedlsBZ_aeEZ_dist_df_1000$prozent <-c(siedlsBZ_aeEZ_dist_df_1000$n/nrow(siedlsBZ_aeEZ_dist_df_1000))
-
 ```

### 2019-07-16 paper.Rmd
commit before ich den max cluster size aus meiner berechnung rausschmeiße.

@@
   echo = FALSE,
+  cache = TRUE,
   comment = "#>",
@@
 source_file,map_name,shape_file_name,DTM_file_name
-BefundesBZ-minimal.csv, late bronze age features, alle_Schnitt-Fundstellen.shp,
+BefundesBZ-minimal.csv, late bronze age features,alle_Schnitt-Fundstellen.shp,
 
@@
 
-source("cluster_frequency_script.v2.16.R")
+source("cluster_frequency_script.v2.17.R")
 
@@
 As this analysis is concerned with a very fine level of detail, the starting point and the step size of the percolation algorithm was chosen to be 1m.
-Only in case of the Unetice Culture a larger starting radius of 4m was chosen, because the smallest distance of features to each other in this time period is 4 m.
 The size of a prehistoric village in middle Germany can’t be assumed to be larger than a kilometer in diameter, therefore the largest radius used was 500m.
@@
 library(ggplot2)
+library(ggrepel)
 # not included because the mean cluster size ist too different because of hugely different sample sizes
-ggplot( data = radius1)+
-  geom_line(aes(x = radius, y = mean_clust_size, col = period))
-```
 
-```{r anzahl cluster}
-library(ggplot2)
-ggplot( data = radius1)+
-  geom_line(aes(x = radius, y = max_normalized, col = period))+
-  theme_light()+
-  labs(x ="percolation radius", y = "normalized maximum cluster size",
-       title = "Cluster sizes in respect to percolation radius")
+mean_steps <- c(1,1+which(diff(analysis_by_radius$mean_clust_size)!=0))
 
-ggsave("normalized_max_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 300  )
+sBZ_meansteps <- as.data.frame(cbind(analysis_by_radius$radius[mean_steps], analysis_by_radius$mean_clust_size[mean_steps]))
 
+sBZ_meansteps <- subset(sBZ_meansteps, sBZ_meansteps$V1 == 46 | sBZ_meansteps$V1 == 68 | sBZ_meansteps$V1 == 88 |  sBZ_meansteps$V1 == 140 | sBZ_meansteps$V1 == 175 | sBZ_meansteps$V1 == 221 | sBZ_meansteps$V1 == 297 |sBZ_meansteps$V1 == 374)
+
+ggplot()+
+  geom_line(data = analysis_by_radius, aes(x = radius, y = mean_clust_size))+
+  geom_point(data = sBZ_meansteps, aes(x = sBZ_meansteps$V1, y = sBZ_meansteps$V2))+
+  geom_label_repel(aes(x = sBZ_meansteps$V1, y = sBZ_meansteps$V2, label = sBZ_meansteps$V1),
+                     box.padding   = 0.35, 
+                   point.padding = 0.5,
+                   nudge_y = 50,
+                  segment.color = "grey50",
+                  color = "grey50")+
+  labs(title = "Sizes of clusters increasing with percolation radius",
+         x = "Percolation radius",
+       y = "Mean Cluster size")
+
+ggsave("mean_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 300  )
+
+# calculate turning points of distance measure vectors
+
+#install.packages("ecp")
+library("ecp")
+
+# same late bronze age
+turn_sBZ_mean <- e.divisive(as.matrix(diff(analysis_by_radius$mean_clust_size)), k = 1, min.size = nrow(analysis_by_radius)/10)
+
+sBZ_turn_rmean <-analysis_by_radius$radius[turn_sBZ_mean$estimates]
+
+sBZ_turn_rmean[2]
 ```
@@
 
-```{r}
-# Idee: wenn n+1 - n > 10 oder so --> großer step
-
-trial_points_sBZ <-  c(1,1+which(diff(sBZ1$max_normalized) > 0.1))
-
-```
-
 ```{r }
@@
 
-points <-  c(1,1+which(diff(sNL1$max_normalized)!=0))
+points <-  c(1,1+which(diff(analysis_by_radius$max_normalized)!=0))
 
@@
 
-pointssBZ <-  c(1,1+which(diff(sBZ1$max_normalized)!=0))
+sBZ1points<- as.data.frame(cbind(analysis_by_radius$radius[points], analysis_by_radius$max_normalized[points]))
 
-sBZ1points<- as.data.frame(cbind(sBZ1$radius[pointssBZ], sBZ1$max_normalized[pointssBZ]))
+sBZ_labels <- subset(sBZ1points, sBZ1points$V1 == 16 | sBZ1points$V1 == 65 | sBZ1points$V1 == 88 | sBZ1points$V1 == 144 | sBZ1points$V1 == 374)
 
 ggplot()+
-  geom_line(data = radius1, aes(x = radius, y = max_normalized, col = period))+
-  geom_point(data = aeEZpoints, aes(x=aeEZpoints$V1, y=aeEZpoints$V2))
+  geom_line(data = analysis_by_radius, aes(x = radius, y = max_normalized))+
+  geom_point(data = sBZ1points, aes(x=sBZ1points$V1, y=sBZ1points$V2))+
+   geom_label_repel(aes(x=sBZ_labels$V1, y=sBZ_labels$V2, label = sBZ_labels$V1),
+                  box.padding   = 0.35, 
+                  point.padding = 0.5,
+                  segment.color = "grey50",
+                  color = "grey50")+
+    theme_light()+
+  labs(x ="percolation radius", y = "normalized maximum cluster size",
+       title = "Cluster sizes in respect to percolation radius")
+
+ggsave("normalized_max_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 300  )
 
 ```
-Die Points sind bereits wichtige Radii-Angaben, weil der URsprungsdatensatz ja auch einfach bei 1 = 1m anfängt.
-
-Welcher Knickpunkt ist wichtig? Wendepunkte berechnen:
+I highlighted those points that mark the most distinctive steps in the distribution.
+We can see the radii after which the algorithm doesn't change the cluster size for some time, showing that here stretches of space between features exist.
+If the dataset is forced to split into two groups the step at 88m radius turns out to be the turning point if the maximum normalized cluster size is used, and 86m if the mean cluster size is calculated.
 
@@
 
-#install.packages("ecp")
-library("ecp")
+# same late bronze age
+turn_sBZ <- e.divisive(as.matrix(diff(analysis_by_radius$max_normalized)), k = 1, min.size = nrow(analysis_by_radius)/10)
 
-# same late bronze age
-turn_sBZ <- e.divisive(as.matrix(diff(sBZ1$max_normalized)), k = 1, min.size = nrow(sBZ1)/10)
+sBZ_turn_r <-analysis_by_radius$radius[turn_sBZ$estimates]
 
-sBZ_turn_r <-sBZ1$radius[turn_sBZ$estimates]
-
-```
-
-##Tabelle anschauen
-
-```{r}
 sBZ_turn_r[2]
@@
 
-new:
+## interpretation
 
-```{r anzahl cluster2, eval=FALSE, include=FALSE}
-ggplot( data = radius1)+
-  geom_line(aes(x = radius, y = max_normalized, col = period))+
-  geom_density()
-```
+The late bronze age features are mostly concentrated in the western half and on the eastern-most part of the transsect.
+As can be seen by the rapidly rising graphs describing the maximum cluster size as well as the mean cluster size in relation to the percolation radius, the features cluster closely by each other.
+First steps in the distribution can be seen at
+
+The largest excavation site of the late bronze age in middle Germany is to be found in Zwenkau(-Eythra), which was excavated in advance of coal extraction proceses.
+The excavation area in Zwenkau is at the largest dimensions 1100 x 825 m [@huth_1998, 194].
+
+Da die Saalemündungsgruppe größtenteils im Flachland vertreten ist, ist bisher nur eine Höhensiedlung bekannt^[Die Hünenburg (@heske_2010).] Nach K.
+Wagner unterscheidet sich die Saalemündungsgruppe von den südlicher gelegenen Gruppen unter anderem durch die Anlage von Siedlungen in Auen und an Hängen.
+Die zehn untersuchten Siedlungen ihrer Arbeit lagen zwischen 55 und 130 m üNN und die Höhe über den Auen bei 1 bis 25 m^[@wagner_1983, 38.].
+Berthold Schmidt geht von landwirtschaftlich günstigen Lagen der Siedlungen neben Gewässern und in offenem Gelände aus^[@schmidt_1978, 127.].
+Rosemarie Müller spricht davon, dass sich die Siedlungen an den ackerbaulich besseren Böden in der Kontaktzone zwischen Schwarzerde und Kiesuntergrund orientieren^[@muller_1992, 259.].
+
+Die Werte der spätbronze-/ältereisenzeitlich datierten Befunde unterscheiden sich merklich: Sie zeigen in der Dichteverteilung ein Maximum bei 92 m.
+Das Minimum befindet sich bei 346 m und ist damit der kleinste Wert im Vergleich aller Perioden.
+Die Kurve ist teilweise recht unruhig, was für ein lokal differenziertes Bild spricht^[Ein Grund hierfür könnte sein, dass sich unter den spätbronzezeitlich bestimmten Funden noch einige ältereisenzeitliche befinden.].
+Der Anstieg der kumulativen Werte verändert sich bei 285 m.
+
+Als großflächig ergrabenen Vergleich kann die Siedlung der jüngeren Bronzezeit und älteren Eisenzeit in Zwenkau^[Bei Döhlert-Albani Zwenkau-Eythra genannt (@dohlert-albani_2016).] in Sachsen herangezogen werden, wo mehrere Einzelhöfe über ein Areal 1100 x 825 m verstreut liegen.
+Diese Einzelhöfe haben unterschiedliche Ausmaße, die etwa 50 bis 85 m an der längsten Seite betragen (2000 - 2500 m²^[@huth_1998, 213.]).
+Sie überlagern sich nicht^[@huth_1998, 214.].
+Die Abstände zwischen den Höfen sind auch sehr unterschiedlich und können nur grob abgeschätzt werden.
+Jedoch scheint ein Abstand von ca.
+65 - 75 m recht häufig^[Vgl.
+@huth_1998, 211, Abb.
+6.].
+Damit liegen sie recht nahe beieinander, was, würde hier eine ähnliche Untersuchung durchgeführt werden wie in der vorliegenden Arbeit, zu schlechten Abgrenzungsmöglichkeiten von Siedlungsstätten führen könnte.
+Auf dem zitierten Plan sind jedoch nur Hausgrundrisse und Zaungräbchen eingezeichnet, was eine Vergleichbarkeit erschwert.
+Zudem gehen die Bearbeiter davon aus, dass die einzelnen Gehöfte nicht zeitgleich waren, sondern eine Wechselsiedlung bestand, in der stets mehrere Gehöfte in Streulage zueinander standen^[@huth_1998, 214.].
+
+Im Arbeitsgebiet entlang der B6n ist innerhalb der Spätbronzezeit ebenfalls mit einer zeitlichen Tiefe der Befunde zu rechnen^[Belegt durch Befundüberschneidungen z.
+B.
+zwischen einem Pfostenbau (Befundnummer 11333) und einer Grube (Befundnummer 11028)].
+Im Westen der Trasse (zw.
+Fpl.
+4 und 11) sind zudem vier Gräben aufgedeckt worden.
+Gräben werden häufig als Siedlungsgrenzen interpretiert.
+Die Abstände zueinander (720 m, 370 m, 440 m) sowie die Ausrichtungen des westlichsten und östlichsten der Gräben, die beide gegen Osten abzugrenzen scheinen, lassen jedoch vermuten, dass sie nicht gleichzeitig bestanden, sondern ein Zeichen kleinräumiger Verlagerungen darstellen.
+Die hohe Dichte der Befunde der Spätbronzezeit ist damit sicherlich zum Teil Ergebnis einer ortskonstanten Siedlungsweise^[Wie z.B.
+der Wechselsiedlung, wie sie für Zwenkau vorgeschlagen wurde (@huth_1998, 208).].
+Nichtsdestotrotz zeichnen sich Befundcluster mit einem Radius von 33 m ab, deren Dopplung, 66 m, innerhalb des Bereichs der Größe der Einzelhöfe in Zwenkau liegt.
+Zwischen Fpl.
+4 und 11 liegen neben sehr dichten Clustern sowohl fundleere Bereiche als auch Stellen mit geringerer Befundkonzentration.
+
+Das Maximum der spätbronze-/ältereisenzeitlichen Befunde von 92 m scheint zu groß zu sein, um den Zwenkauer Hofplätzen zu entsprechen.
+Der Dichtewerte am Minimum von 346 m ist wie bei der Spätbronzezeit ein relativ hoher Wert, was wiederum für eine nicht so klare Trennung unterschiedlicher Siedlungsstellen spricht.
+Dass das Minimum über einhundert Meter "eher" auftritt als bei der Spätbronzezeit ist ein Hinweis auf enger zusammenliegende Cluster von Befunden, was dem Zwenkauer Beispiel etwas näher kommt.
+Der "Wendepunkt" der kumulativen Kurve bei 285 m macht dabei ebenfalls größere Räume für zusammengehörige Befunde auf als bei den spätbronzezeitlich datierten.
+
+Nach diesen Ergebnissen liegen spätbronzezeitliche Befunde in kleineren Radien (in Analogie zu Zwenkau in Einzelhöfen) eng beieinander, während in der älteren Eisenzeit in größeren Abständen und größeren Zusammenhängen gebaut wurde.
+In beiden Fällen ist jedoch mit zeitlicher Tiefe zu rechnen und einer schlechten Abgrenzbarkeit von Siedlungsstätten zueinander.
+
+Es ist jedoch auch vorher schon festgestellt worden „Man hat es [..] in der Jungbronze- und Früheisenzeit mit vielfältigen Besiedlungsformen
+zu tun“^[@huth_1998, 216.].
+Erschwerend kommt hinzu, dass durch die ungenauen Datierungsmöglichkeiten hier eine sehr tiefe Zeitspanne vorliegt, bei der in jeder Analyse eventuelle chronologische Unterschiede verwischt werden.
+
+Interessant bleibt es festzuhalten, dass sich durchaus Unterschiede zwischen der Spätbronzezeit und den auch ältereisenzeitlich datierten Befunden fassen lassen.
+Ob dies ein zufälliger Effekt oder ein Hinweis für Veränderungen im Siedlungsverhalten ist, können nur weitere Untersuchungen klären.
 

### 2019-07-16 cluster_frequency_script.v2.17.R

@@ -1,0 +1,246 @@
+# CLUSTER FREQENCY PLOTTING SCRIPT
+# Simon Maddison, 10th May 2015
+# Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs # of clusters
+# Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
+# Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
+# Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
+# 	(currently max size). Changed outputs to multi-page pdf files
+# Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
+# Version 2.5: 23/4/16 -
+#	Added in computations for clusters of single nodes
+# 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
+#	Table of max, mean and median exported
+# Version 2.6: 26/4/16 -
+# 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
+# 	Exclude clusters with less than a certain threshold of nodes (parameter)
+# 	Also exclude largest cluster from mean
+# 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
+# Version 2.7: 29/4/16 -
+#	As per Elsa's published paper, plot max cluster size vs. radius as well
+# 	Page format improved to generate pdf A4 format
+# 	Bug fixed when adding clusters of size 1 (if null value)
+# Version 2.8: 4/5/16 -
+#	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
+# Version 2.9: 6/5/16 -
+#	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
+# Version 2.10: 8/5/16 - source text file format changed to include map information
+# Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
+#	File is member_cluster_by_radius.csv
+# Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
+#	Make the image square or else it distorts the plot (note that this does not happen in pdf)
+# 	Remove simple cluster rank plots, no longer useful
[…]

### 2019-07-16 mapping_clusters.v4.12.R

@@ -69,7 +69,7 @@ print(map_name)
 map_outline <- readOGR(dsn=file_name,layer=layer_name)
 
 # Read in nodes and grid coordinates
-xy_data <- read.csv(source_file, as.is = FALSE, sep = "\t") #added tab-seperation
+xy_data <- read.csv(source_file, as.is = FALSE, sep = ",") #added tab-seperation
 # as.is is redundant as far as I can see as just confirms default behaviour of read.csv
 # fields of interest:
 # PlcIndex Easting Northing
@@ -140,7 +140,7 @@ points(xy_data$Easting, xy_data$Northing, col='red', pch=20, cex=point_dia)
 number_of_sites <- paste("Number of sites: ",nrow(xy_data))
 mtext(number_of_sites)
 plot_title <- str_to_title(map_name,locale="")
-title(paste("Iron Age Hillforts in ", plot_title), sub=paste("Sources: ",source_file_name,"; ",shape_file_name))
+title(paste("Clusters of ", plot_title), sub=paste("Sources: ",source_file_name,"; ",shape_file_name))
 dev.off()
 
 # Generates maps for each of percolation radii in range of radius values

### 2019-07-16 paper.Rmd
interpretation sBZ begonnen. aus altem paper text eingefügt.

@@
                   color = "grey50")+
+  theme_light()+
   labs(title = "Sizes of clusters increasing with percolation radius",
@@
 
-ggsave("mean_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 300  )
+ggsave("mean_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 600  )
+
+```
+
+There are several levels of clustering.
+Features of the late Bronze Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
+Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
+We thereby find the edges of settlements and can define their size.
+The step-wise rises at higher percolation radii needs explanation as well.
+To provide these, the results will be compared to large scale excavations of settlements in middle Germany.
+
+I highlighted those points that mark the most distinctive steps in the distribution.
+We can see the radii after which the algorithm doesn't change the cluster size for some time, showing that here stretches of space between features exist.
+If the dataset is forced to split into two groups the step at  `r sBZ_turn_rmean[2]` radius turns out to be the splitting point of the mean cluster sizes calculated.
+
+```{r mean cluster size turning points, include=FALSE}
 
 # calculate turning points of distance measure vectors
+# google terms: knee of curve, "trade off point"
+#https://dataplatform.cloud.ibm.com/analytics/notebooks/54d79c2a-f155-40ec-93ec-ed05b58afa39/view?access_token=6d8ec910cf2a1b3901c721fcb94638563cd646fe14400fecbb76cea6aaae2fb1
+
+#https://www.rdocumentation.org/packages/SamSPECTRAL/versions/1.26.0/topics/kneepointDetection
 
@@
 
-sBZ_turn_rmean[2]
-```
-
-There are several levels of clustering.
-Features of the late Bronze Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
-Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
-We thereby find the edges of settlements and can define their size.
-The step-wise rises at higher percolation radii needs explanation as well.
-To provide these, the results will be compared to large scale excavations of settlements in middle Germany.
-
-```{r }
-## not happy with results here. esp. for EZ.
-# google terms: knee of curve, "trade off point"
-#https://dataplatform.cloud.ibm.com/analytics/notebooks/54d79c2a-f155-40ec-93ec-ed05b58afa39/view?access_token=6d8ec910cf2a1b3901c721fcb94638563cd646fe14400fecbb76cea6aaae2fb1
-
-#https://www.rdocumentation.org/packages/SamSPECTRAL/versions/1.26.0/topics/kneepointDetection
-
-points <-  c(1,1+which(diff(analysis_by_radius$max_normalized)!=0))
-
-## Idee: points aufsteigend sortieren... also die Abstände zwischen zwei aufeinanderfolgenden max_normalized sotieren. die größten Abstände raussuchen, die als Knackpunkte definieren?
-points <- order(points)
-
-sBZ1points<- as.data.frame(cbind(analysis_by_radius$radius[points], analysis_by_radius$max_normalized[points]))
-
-sBZ_labels <- subset(sBZ1points, sBZ1points$V1 == 16 | sBZ1points$V1 == 65 | sBZ1points$V1 == 88 | sBZ1points$V1 == 144 | sBZ1points$V1 == 374)
-
-ggplot()+
-  geom_line(data = analysis_by_radius, aes(x = radius, y = max_normalized))+
-  geom_point(data = sBZ1points, aes(x=sBZ1points$V1, y=sBZ1points$V2))+
-   geom_label_repel(aes(x=sBZ_labels$V1, y=sBZ_labels$V2, label = sBZ_labels$V1),
-                  box.padding   = 0.35, 
-                  point.padding = 0.5,
-                  segment.color = "grey50",
-                  color = "grey50")+
-    theme_light()+
-  labs(x ="percolation radius", y = "normalized maximum cluster size",
-       title = "Cluster sizes in respect to percolation radius")
-
-ggsave("normalized_max_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 300  )
-
-```
-I highlighted those points that mark the most distinctive steps in the distribution.
-We can see the radii after which the algorithm doesn't change the cluster size for some time, showing that here stretches of space between features exist.
-If the dataset is forced to split into two groups the step at 88m radius turns out to be the turning point if the maximum normalized cluster size is used, and 86m if the mean cluster size is calculated.
-
-```{r}
-
-# calculate turning points of distance measure vectors
-
-# same late bronze age
-turn_sBZ <- e.divisive(as.matrix(diff(analysis_by_radius$max_normalized)), k = 1, min.size = nrow(analysis_by_radius)/10)
-
-sBZ_turn_r <-analysis_by_radius$radius[turn_sBZ$estimates]
-
-sBZ_turn_r[2]
 ```
@@
 The late bronze age features are mostly concentrated in the western half and on the eastern-most part of the transsect.
-As can be seen by the rapidly rising graphs describing the maximum cluster size as well as the mean cluster size in relation to the percolation radius, the features cluster closely by each other.
-First steps in the distribution can be seen at
+As can be seen by the rapidly rising graph describing the mean cluster size in relation to the percolation radius, the features cluster closely by each other.
+First steps in the distribution can be seen at 46 m, 68 m and 88 m.
+These are the distances, at which the clusters "stabilise" and don't grow with growing percolation radii.
 
-The largest excavation site of the late bronze age in middle Germany is to be found in Zwenkau(-Eythra), which was excavated in advance of coal extraction proceses.
-The excavation area in Zwenkau is at the largest dimensions 1100 x 825 m [@huth_1998, 194].
+The largest excavation site of the late bronze age in middle Germany is to be found in Zwenkau(-Eythra) in Saxony, which was excavated in advance of coal mining.
+At Zwenkau several single farmsteads delimited by houses and fences spread over the whole excavation area, which measures at its greatest dimensions 1100 x 825 m [@huth_1998, 194.213].
+The farmsteads in Zwenkau don't overlap [@huth_1998, 214] and the distances to each other are quite diverse.
+Nonetheless a number of them seem to scatter at at an intervall of ca.
+65-75 m.
+[cf.
+@huth_1998, 211, fig.
+6].
+The farmsteads themselves are not all the same size, but the longest sides show to about 50 - 85m long (cumulating to sizes of 2000 - 2500 m²) [@huth_1998, 213.].
+It is assumed not all of them existed at the same time, but that there were always several isolated farmsteads in a scattered distribution to each other [@huth_1998, 214].
 
-Da die Saalemündungsgruppe größtenteils im Flachland vertreten ist, ist bisher nur eine Höhensiedlung bekannt^[Die Hünenburg (@heske_2010).] Nach K.
-Wagner unterscheidet sich die Saalemündungsgruppe von den südlicher gelegenen Gruppen unter anderem durch die Anlage von Siedlungen in Auen und an Hängen.
-Die zehn untersuchten Siedlungen ihrer Arbeit lagen zwischen 55 und 130 m üNN und die Höhe über den Auen bei 1 bis 25 m^[@wagner_1983, 38.].
-Berthold Schmidt geht von landwirtschaftlich günstigen Lagen der Siedlungen neben Gewässern und in offenem Gelände aus^[@schmidt_1978, 127.].
-Rosemarie Müller spricht davon, dass sich die Siedlungen an den ackerbaulich besseren Böden in der Kontaktzone zwischen Schwarzerde und Kiesuntergrund orientieren^[@muller_1992, 259.].
+At the analysed transect excavation we also deal with a depth in time, as there are overlapping features and several ditches, which most probably did not exist at the same time, but can be interpreted as indices of small-scale settlement shifts.
 
-Die Werte der spätbronze-/ältereisenzeitlich datierten Befunde unterscheiden sich merklich: Sie zeigen in der Dichteverteilung ein Maximum bei 92 m.
-Das Minimum befindet sich bei 346 m und ist damit der kleinste Wert im Vergleich aller Perioden.
-Die Kurve ist teilweise recht unruhig, was für ein lokal differenziertes Bild spricht^[Ein Grund hierfür könnte sein, dass sich unter den spätbronzezeitlich bestimmten Funden noch einige ältereisenzeitliche befinden.].
-Der Anstieg der kumulativen Werte verändert sich bei 285 m.
-
-Als großflächig ergrabenen Vergleich kann die Siedlung der jüngeren Bronzezeit und älteren Eisenzeit in Zwenkau^[Bei Döhlert-Albani Zwenkau-Eythra genannt (@dohlert-albani_2016).] in Sachsen herangezogen werden, wo mehrere Einzelhöfe über ein Areal 1100 x 825 m verstreut liegen.
-Diese Einzelhöfe haben unterschiedliche Ausmaße, die etwa 50 bis 85 m an der längsten Seite betragen (2000 - 2500 m²^[@huth_1998, 213.]).
-Sie überlagern sich nicht^[@huth_1998, 214.].
-Die Abstände zwischen den Höfen sind auch sehr unterschiedlich und können nur grob abgeschätzt werden.
-Jedoch scheint ein Abstand von ca.
-65 - 75 m recht häufig^[Vgl.
-@huth_1998, 211, Abb.
-6.].
 Damit liegen sie recht nahe beieinander, was, würde hier eine ähnliche Untersuchung durchgeführt werden wie in der vorliegenden Arbeit, zu schlechten Abgrenzungsmöglichkeiten von Siedlungsstätten führen könnte.
@@
 
-Das Maximum der spätbronze-/ältereisenzeitlichen Befunde von 92 m scheint zu groß zu sein, um den Zwenkauer Hofplätzen zu entsprechen.
-Der Dichtewerte am Minimum von 346 m ist wie bei der Spätbronzezeit ein relativ hoher Wert, was wiederum für eine nicht so klare Trennung unterschiedlicher Siedlungsstellen spricht.
-Dass das Minimum über einhundert Meter "eher" auftritt als bei der Spätbronzezeit ist ein Hinweis auf enger zusammenliegende Cluster von Befunden, was dem Zwenkauer Beispiel etwas näher kommt.
-Der "Wendepunkt" der kumulativen Kurve bei 285 m macht dabei ebenfalls größere Räume für zusammengehörige Befunde auf als bei den spätbronzezeitlich datierten.
-
 Nach diesen Ergebnissen liegen spätbronzezeitliche Befunde in kleineren Radien (in Analogie zu Zwenkau in Einzelhöfen) eng beieinander, während in der älteren Eisenzeit in größeren Abständen und größeren Zusammenhängen gebaut wurde.
@@
 Ob dies ein zufälliger Effekt oder ein Hinweis für Veränderungen im Siedlungsverhalten ist, können nur weitere Untersuchungen klären.
+
+IDee:
+Abgleich mit den vom LDA abgegrenzten sites bei welchem cluster-radius??
 

### 2019-07-17 paper.Rmd
made functions built package

@@
 ---
-title: "Percolation analysis of transect data"
+title: "Percolation analysis"
 author:
+  -Maddison, Simon
+
   -Schmidt, Sophie C.
-  - Author Two
+
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
       fig_caption: yes
-      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
-
+csl: RGK_archaeology_DGUF.csl
+bibliography: sitedefinition.bib
 abstract: |
-  Text of abstract
+  Percolation Analysis has been recently applied in Archaeology for identifying clusters and groupings at a national scale, for example investigating the distribution of Hillforts in Britain and Ireland, and Domesday sites in England.
+The technique, originally developed in physics and more recently adopted in Geography, is a way of identifying groupings or clusters, purely based on spatial separation using Euclidian distance.
+The investigations for British Hillforts and Domesday sites have shown this to be a fruitful starting point for investigating possible socio-political entities, and patterns of deep history.
+The technique has now also been applied to features at a sub-regional level, in Saxony-Anhalt, middle Germany, with the different objective of identifying settlement sites along a 13km strip excavation.
+Aim here was to arrive at estimates of settlement sizes, which in turn can inform landscape archaeological surveys on the decision on attributing single finds to an already known site or registering a new site.
+This paper provides a summary of the Percolation Analysis method, and then provides two detailed case studies where the technique is applied at significantly different geographical scales.
+This will demonstrate not only the potential for the technique within archaeology, but also how it can be applied at different spatial scales with different objectives appropriate to the specific problem in question.
 keywords: |
-  keyword 1; keyword 2; keyword 3
-highlights: |
-  These are the highlights. 
+  spatial analysis; percolation; settlement archaeology
 ---
@@
 
-#library(percolatransect) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
+library(percolation) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
 ```
+
+### Background
+This proposal outline covers a paper for submission to the Journal of the CAA, and a presentation at the German Chapter of the CAA to be held in Wilhelmshaven in September 2019.
+
+#Percolation Analysis – Archaeological applications at widely different spatial scales
+
+##Introduction
+Percolation Analysis has been recently applied in Archaeology for identifying clusters and groupings at a national scale, for example investigating the distribution of Hillforts in Britain and Ireland, and Domesday sites in England (references to papers at CAA 2018/2019, book chapter, paper in Atlas Conference etc.).
+The technique, originally developed in physics and more recently adopted in Geography (references), is a way of identifying groupings or clusters, purely based on spatial separation using Euclidian distance.
+The above investigations for British Hillforts and Domesday sites have shown this to be a fruitful starting point for investigating possible socio-political entities, and patterns of deep history.
+The technique has now also been applied to features at a sub-regional level, in Saxony-Anhalt, middle Germany, with the different objective of identifying settlement sites along a 13km strip excavation.
+Aim here was to arrive at estimates of settlement sizes, which in turn can inform landscape archaeological surveys on the decision on attributing single finds to an already known site or registering a new site.
+This paper provides a summary of the Percolation Analysis method, and then provides two detailed case studies where the technique is applied at significantly different geographical scales.
+This will demonstrate not only the potential for the technique within archaeology, but also how it can be applied at different spatial scales with different objectives appropriate to the specific problem in question.
+
+##Methodology
+Percolation Analysis is a technique for identifying clusters within a set of spatially arranged points.
+The computation is based on the Euclidian distance between those points.
+Percolation analysis is as a way of mathematically describing clusters of spatially arranged points and analysing their related behaviour.
+A ready example is the propagation of fire through a forest, where fire will spread from tree to tree within a cluster, when the trees are close enough together, but at a critical density when all the trees form a single cluster it can spread to the forest limits (reference).
+A cluster is based on a defined distance threshold, so that for any given point all neighbouring points falling within this threshold are part of the cluster.
+The test is then re-applied for each of these neighbours in turn, and any further points meeting this criterion are also part of the cluster.
+This technique can be applied at any scale, from the molecular to the geographical and beyond.
+Originally developed for describing the physical properties of materials, Percolation Analysis has recently been used in geography to identify metropolitan areas, based on population density.
+The City Clustering Algorithm (CCA) has been developed out of percolation theory by Rozenfeld et al.
+(2008) based on distance within a cellular lattice and further developed by Rozenfeld,  et al.
+(2011) to use the Euclidean distance between points.
+The technique is illustrated in Figure tba, where an arbitrary point is selected as a start and any point falling within a defined threshold distance  ‘l’  becomes part of the cluster and the process is then re-applied to each of these points in turn, until the cluster can extend no further.
+This threshold distance is also known as the ‘percolation radius’ and this term is generally used below.
+Arcaute et al.
+(2016) have adopted this technique for defining urban areas, using the density of street interconnections rather than population.
+They have also developed analytical techniques for identifying transition points in cluster growth as the distance threshold is progressively increased, as discussed further below.
+Note that the method has evolved from statistical techniques in materials science, where it is applied to sets of spatially distributed points which are identical and where there is no interest in distinguishing between the points.
+However when used in archaeology there is potentially a very great interest in the individual points, reflecting as they do distinct archaeological entities, as will be shown later.
+
+###Comparison to other clustering algorithms 
+A number of spatial clustering algorithms are known in spatial data mining (Neethu - Surendran 2013, Varghese et al 2014), used in archaeology has been mostly the k-means non-hierarchical clustering algorithm, developed by Kintight and Ammermann in 1982 (Baxter 1994 [2015a], 148).
+This algorithm has been applied widely in the last 40 years in archaeology (to do: many examples see Baxter 2015b), probably because of its ease in use and understanding: At the beginning the whole data set is considered as one cluster and the centre of this cluster is determined.
+The point furthest from this centre is then used as a centroid for a new cluster and attracts those points to its cluster that are nearer to it than to the original cluster (Baxter 1994, [2015a], 149).
+Step by step the algorithm determines new cluster centers and allocates each point into one of k clusters in such a way, that the sum-squared error (SSE) is minimized.
+The SSE is the sum of the squared distances from each point to the center of the cluster to which it is assigned (Kintight 1990, 185).
+By minimizing global sum-squared errors the algorithm tends to create circular clusters (Kintight 1990, 190).
+Another point of critique has been the need to define the number of clusters (k) that are being created beforehand.
+To navigate some problems of k-means and associated algorithms, which have been highlighted in the years from Kintight (1990) to Ducke (2015) and in parts mitigated by Baxter (2015b), Caspari and Jendryke developed Achsphere as an archaeological cluster algorithm (Caspari – Jendryke 2017).
+They integrate structural parameters, which were recorded together with the spatial information of the studied features.
+Because they analysed mostly round structures, the features were weighted using the diameter, though other parameters might be used.
+(Caspari – Jendryke 2017, 182).
+This weighing of the influence of the features after archaeological pre-consideration was implemented to mitigate the effect of different densities in the same data set (Caspari – Jendryke 2017, 182).
+Around each feature  a sphere is constructed, which size is based on the weighing factor.
+Two features will belong to the same cluster, if their spheres touch or overlap.
+The clustering algorithm starts at an arbitrary node, checks all neighbours (touching spheres) and stops only, when no new neighbours are found.
+Inputs needed for the algorithm are a minimum number of points for a cluster and the the weight (Caspari – Jendryke 2017, 184).
+It is considered by the authors not to be a “generic cluster algorithm but a specific method to divide landscape archaeological datasets into sub-entities for further analysis assuming that spherical structuring dominates the data.” (Caspari – Jendryke 2017, 186).
+
+Maybe some words on DBSCAN here? I need to read up on it still…
+
+Other algorithms, such as Nearest Neighbour, Ripley’s K-function, the F- and G-functions are clustering detection algorithms, that tell about whether the point distribution is spatially clustered but don’t directly give an attribution of points to a certain cluster.
+We believe percolation analysis to be a worthy contribution to the toolkit of clustering algorithms for archaeologists, because it is easily understandable and applicable.
+Available in the free and open source scripting language R it is easily replicable for any researcher, who might want to implement it.
+
+Ducke formulated the following parameters for an useful spatial cluster detector:
+Its mathematical core should be simple, so that archaeologists can understand why a certain input leads to a certain output,
+it should assume as little as possible about the clustering structure (i.e., the number, sizes and locations of clusters),
+it should be robust against noise, i.e., it should just ignore the odd scattering of sherds around the actual clusters, and it should not assume that every point is indeed part of a cluster, 
+it should either assign each point to a cluster or classify it as noise, 
+and finally, it should always produce the same result when given the same input data.
+(Ducke 2015, 357-358).
+
+We think percolation analysis fits well these desiderata, as its mathematical core is simple; size, number and location of clusters is explored not predetermined, it will include outliers only at very late stages of the clustering process (which is easily detected and may be excluded from analysis results if so chosen) and… well… do we always get the very same results?
+Hm, I think as the first seed is always chosen randomly, we may not get the very same results every time. What are your experiences here?
+
+##Case Studies
+
+###Hillforts in Britain 
+Working with data from the ‘Atlas of Hillforts’ (reference) it was decided to use Percolation Analysis to establish any ‘natural’ or intrinsic groupings of hillforts that might exist in Britain and Ireland.
+Once identified, these groupings could then be compared with topography and geographical regions, as well as other historical data sets, and further analysed with data from the Atlas.
+The Atlas dataset comprises 3xxx confirmed sites in Britain and xxx in all of Ireland.
+Percolation Analysis was applied in radius increments of 1km.
+The cluster transitions for Britain are shown in Figure xxx, which plots the normalized maximum cluster size (with a normalized size range of between 0 and 1.0) against percolation radius.
+For large radius values all sites will form a single cluster while for progressively smaller radii, the clusters start to break up, and this transition diagram is an indicator of where potentially interesting clusters become visible.
+For small radius values no clusters form at all with the most notably obvious transition occurring at 34 km, as discussed below.
+Geographical plots of clusters are shown in Figures xxx.
+Clusters are ranked by size and allocated a colour, with red being the largest cluster and blue the next, below rank 15 all sites are plotted as grey.
+Above 35km all sites form a single large cluster, except for the Hebrides, Shetland Islands, Isle of Man and Scillies.
+Apart from south-east Scotland, the most interesting transitions occur in the 6-13km range.
+At 34km (Figure xxx) the predominantly Scottish cluster includes sites in England as far south as a line roughly between Morecambe and Flamborough Head.
+Within England as the radius values reduce, sites in the Pennines and the east progressively break out of the bigger cluster, and at 14km, the south-west peninsula forms its own cluster in Cornwall and part of Devon, and other clusters appear in the south-east.
+The plot for 12km (Figure xxx) shows for example Cornwall and Devon/part of Somerset as individual clusters, and a cluster along the Chilterns.
+The plot for 9km (Figure xxx) shows clusters in north-west Wales, the Clwydian Range, south-west Wales, the Gower, central Wales and the Marches and two clusters on the north-west and the south-east of the Severn Valley, the latter being the Cotswolds group.
+Some of these clusters have been the subject of more detailed analysis and three of them are discussed below.
+An important point is that there is nothing necessarily special about particular values of the percolation radius, so that transitions will not necessarily occur for the same values in different regions or countries.
+There are various possible explanations for this, such as the variability in regional and local topography.
+In areas of high density such as south-west Wales and south-east Scotland, then a finer grained analysis with radius increments of 0.1km reveals more localised cluster patterns in the range 3-7km radius values.
+Further study is required to establish what significance these might have.
+(add figure??)
 
@@
 
-There are 1005 settlement features cataloged as belonging to this period.
+There are 1006 settlement features cataloged as belonging to this period.
 
@@
 Machine trenching has been shown to be the most effective way to find sites [@hey_2006].
-Admittedly even then not all sites are discovered, especially Neolithic ones have the least probability to be found, which may be one reason for the small number of Neolithic features in the transect.
 The late Bronze age and the early iron age are not easily seperable in the settlements, because the ceramics are very similar.
@@
 This approach understands the archaeological record  as a continual distribution in space, with spots of higher densities, the so-called “sites”, and areas of lower density [@wobst_1983, 39].
+
 At this point the continuously excavated data set of the street and the clustering analysis percolation can be fruitfully connected: As percolation works with radii around points it may assist in quantitatively assessing which distances between features are common.
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r include=FALSE}
 
@@
 
-source_file,map_name,shape_file_name,DTM_file_name
-BefundesBZ-minimal.csv, late bronze age features,alle_Schnitt-Fundstellen.shp,
+#source_file,map_name,shape_file_name,DTM_file_name
+#BefundesBZ-minimal.csv, late bronze age features,alle_Schnitt-Fundstellen.shp,
 
@@
 
-upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
-500,2,1, 1000,0,0,1
+#upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
+#500,2,1, 1000,0,0,1
 
-source("create_nodes_list_d.v4.7.R")
-source("clustering_script.v3.6.R")
-source("mapping_clusters.v4.12.R")# Fehler in ogrInfo(dsn = dsn, layer = layer, encoding = encoding, use_iconv = use_iconv, : Cannot open data source...
-weeiiiiird...
-nochmal auf anderer Maschine testen.
+library(maptools)
+library(rgdal)
+library(stringr)
+library(igraph)
 
-source("cluster_frequency_script.v2.17.R")
+source("R/create_nodes_list_d.v4.7.R")
+percolateNodes()
+
+source("R/clustering_script.v3.6.R")
+percolate()
+
+#source("R/mapping_clusters.v4.12.R")
+#mapClusters()
+
+library(calibrate)
+library(Hmisc)
+
+source("R/cluster_frequency_script.v2.17.R")
+clusterFrequency()
 
@@
 
-ggsave("mean_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 600  )
-
 ```
-
-There are several levels of clustering.
-Features of the late Bronze Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
-Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
-We thereby find the edges of settlements and can define their size.
-The step-wise rises at higher percolation radii needs explanation as well.
-To provide these, the results will be compared to large scale excavations of settlements in middle Germany.
-
-I highlighted those points that mark the most distinctive steps in the distribution.
-We can see the radii after which the algorithm doesn't change the cluster size for some time, showing that here stretches of space between features exist.
-If the dataset is forced to split into two groups the step at  `r sBZ_turn_rmean[2]` radius turns out to be the splitting point of the mean cluster sizes calculated.
 
@@
 
-## interpretation
+There are several levels of clustering.
+Features of the late Bronze Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
+Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
+We thereby find the edges of settlements and can define their size.
+The step-wise rises at higher percolation radii needs explanation as well.
+To provide these, the results will be compared to a large scale excavation of a late bronze age site in middle Germany.
+
+I highlighted those points that mark the most distinctive steps in the distribution.
+We can see the radii after which the algorithm doesn't change the cluster size for some time, showing that here stretches of space between features exist.
+The turning point of the mean cluster sizes is at the radius of `r sBZ_turn_rmean[2]`m.
+
+### Interpretation
 
 The late bronze age features are mostly concentrated in the western half and on the eastern-most part of the transsect.
-As can be seen by the rapidly rising graph describing the mean cluster size in relation to the percolation radius, the features cluster closely by each other.
+As can be seen by the rapidly rising graph describing the mean cluster size in relation to the percolation radius, the features cluster closely to each other.
 First steps in the distribution can be seen at 46 m, 68 m and 88 m.
@@
 6].
-The farmsteads themselves are not all the same size, but the longest sides show to about 50 - 85m long (cumulating to sizes of 2000 - 2500 m²) [@huth_1998, 213.].
+The farmsteads themselves are not all the same size, but the longest sides show to be about 50 - 85m long (cumulating to sizes of 2000 - 2500 m²) [@huth_1998, 213.].
 It is assumed not all of them existed at the same time, but that there were always several isolated farmsteads in a scattered distribution to each other [@huth_1998, 214].
 
-At the analysed transect excavation we also deal with a depth in time, as there are overlapping features and several ditches, which most probably did not exist at the same time, but can be interpreted as indices of small-scale settlement shifts.
+At the analysed transect excavation we also deal with a depth in time, as there are overlapping features and several ditches, which most probably did not exist at the same time, but can be interpreted as evidence of small-scale settlement shifts.
+We can therefore assume that at least partly the high density of settlement features belonging to the late bronze age might be interpreted as evidence of several phases or local re-settlement.
+Nonetheless we can notice that the two smaller radii detected as possible site delimiter by the percolation algorithm fall well into the range of the farmstead sizes of Zwenkau-Eythra.
 
-Damit liegen sie recht nahe beieinander, was, würde hier eine ähnliche Untersuchung durchgeführt werden wie in der vorliegenden Arbeit, zu schlechten Abgrenzungsmöglichkeiten von Siedlungsstätten führen könnte.
-Auf dem zitierten Plan sind jedoch nur Hausgrundrisse und Zaungräbchen eingezeichnet, was eine Vergleichbarkeit erschwert.
-Zudem gehen die Bearbeiter davon aus, dass die einzelnen Gehöfte nicht zeitgleich waren, sondern eine Wechselsiedlung bestand, in der stets mehrere Gehöfte in Streulage zueinander standen^[@huth_1998, 214.].
-
-Im Arbeitsgebiet entlang der B6n ist innerhalb der Spätbronzezeit ebenfalls mit einer zeitlichen Tiefe der Befunde zu rechnen^[Belegt durch Befundüberschneidungen z.
-B.
-zwischen einem Pfostenbau (Befundnummer 11333) und einer Grube (Befundnummer 11028)].
-Im Westen der Trasse (zw.
-Fpl.
-4 und 11) sind zudem vier Gräben aufgedeckt worden.
-Gräben werden häufig als Siedlungsgrenzen interpretiert.
-Die Abstände zueinander (720 m, 370 m, 440 m) sowie die Ausrichtungen des westlichsten und östlichsten der Gräben, die beide gegen Osten abzugrenzen scheinen, lassen jedoch vermuten, dass sie nicht gleichzeitig bestanden, sondern ein Zeichen kleinräumiger Verlagerungen darstellen.
-Die hohe Dichte der Befunde der Spätbronzezeit ist damit sicherlich zum Teil Ergebnis einer ortskonstanten Siedlungsweise^[Wie z.B.
-der Wechselsiedlung, wie sie für Zwenkau vorgeschlagen wurde (@huth_1998, 208).].
-Nichtsdestotrotz zeichnen sich Befundcluster mit einem Radius von 33 m ab, deren Dopplung, 66 m, innerhalb des Bereichs der Größe der Einzelhöfe in Zwenkau liegt.
-Zwischen Fpl.
-4 und 11 liegen neben sehr dichten Clustern sowohl fundleere Bereiche als auch Stellen mit geringerer Befundkonzentration.
-
-Nach diesen Ergebnissen liegen spätbronzezeitliche Befunde in kleineren Radien (in Analogie zu Zwenkau in Einzelhöfen) eng beieinander, während in der älteren Eisenzeit in größeren Abständen und größeren Zusammenhängen gebaut wurde.
-In beiden Fällen ist jedoch mit zeitlicher Tiefe zu rechnen und einer schlechten Abgrenzbarkeit von Siedlungsstätten zueinander.
-
-Es ist jedoch auch vorher schon festgestellt worden „Man hat es [..] in der Jungbronze- und Früheisenzeit mit vielfältigen Besiedlungsformen
-zu tun“^[@huth_1998, 216.].
-Erschwerend kommt hinzu, dass durch die ungenauen Datierungsmöglichkeiten hier eine sehr tiefe Zeitspanne vorliegt, bei der in jeder Analyse eventuelle chronologische Unterschiede verwischt werden.
-
-Interessant bleibt es festzuhalten, dass sich durchaus Unterschiede zwischen der Spätbronzezeit und den auch ältereisenzeitlich datierten Befunden fassen lassen.
-Ob dies ein zufälliger Effekt oder ein Hinweis für Veränderungen im Siedlungsverhalten ist, können nur weitere Untersuchungen klären.
+Mapping the clusters, though, reveals a different picture.
+As the percolation algorithm moves from node to node, the cluster groups are much larger than the radii.
+Here now it seems sensible to determine at what point the clusters detected by percolation show the best overlap to the site definitions by the Heritage Management.
 

### 2019-07-17 R/cluster_frequency_script.v2.17.R

@@ -1,0 +1,187 @@
+#' CLUSTER FREQENCY PLOTTING SCRIPT
+#' Simon Maddison, 10th May 2015
+#' Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs #' of clusters
+#' Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
+#' Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
+#' Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
+#' 	(currently max size). Changed outputs to multi-page pdf files
+#' Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
+#' Version 2.5: 23/4/16 -
+#'	Added in computations for clusters of single nodes
+#' 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
+#'	Table of max, mean and median exported
+#' Version 2.6: 26/4/16 -
+#' 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
+#' 	Exclude clusters with less than a certain threshold of nodes (parameter)
+#' 	Also exclude largest cluster from mean
+#' 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
+#' Version 2.7: 29/4/16 -
+#'	As per Elsa's published paper, plot max cluster size vs. radius as well
+#' 	Page format improved to generate pdf A4 format
+#' 	Bug fixed when adding clusters of size 1 (if null value)
+#' Version 2.8: 4/5/16 -
+#'	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
+#' Version 2.9: 6/5/16 -
+#'	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
+#' Version 2.10: 8/5/16 - source text file format changed to include map information
+#' Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
+#'	File is member_cluster_by_radius.csv
+#' Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
+#'	Make the image square or else it distorts the plot (note that this does not happen in pdf)
+#' 	Remove simple cluster rank plots, no longer useful
+#' Version 2.13: 7/11/17	- amended working directory path for new pc
[…]

### 2019-07-17 R/clustering_script.v3.6.R

@@ -1,0 +1,123 @@
+#' CLUSTERING SCRIPT, RUNS AFTER NODES LIST SCRIPT
+#' Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+#' Cite as:	arXiv:1504.08318 [physics.soc-ph]
+#' Version 3
+#' This is version 3, incorporating adjustments and enhancements to code 10/5/15 & 2/10/15
+#' This code computes the clusters, based on matrix of inter-nodal distances computed in script
+#'  	create_nodes_list_d.vxxx.R
+#' Note that the list of nodes and internodal distances is not a complete matrix, but only includes
+#' 	distances below a certain threshold. This keeps the data sizes manageable.
+#' Note that the original used library bigmemory but this is not available for windows so all refs removed.
+#' Note that when nodes are individual, they are no longer in a cluster. (31/1/16)
+#' Version 3.1: 20/04/16 - Note that this intrinsically cannot generate clusters with only one node.
+#'   	Need to post process means in the analysis script
+#' Version 3.2: 6/5/16 - Changed Index name to fit within 8 chars -> PlcIndex
+#' Version 3.3: 18/5/16 - output data into a single file, indexed on PlcIndex and radius instead of separate
+#'	files. Read in PlcIndex.csv generated by create_nodes_list_d....R
+#' Version 3.4: 7/11/17 - path of working directory amended for new PC
+#' Version 3.6: 04/12/18 - changes in Version 3.5 omitted
+#' 	Add in unit parameter to select km or m, in "radius_values.txt"
+#'	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
+#'	so that a unit value of 1 shows through as metres, and a value of 1000 as km. Other values accomodated.
+#' 	NOTE: no modification necessary to work for fractional values of radius, e.g. step size of 0.1km???????????????
+
+
+percolate <- function(x) {
+#setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
+# paths
+path_source <- paste(getwd(),"/source_data",sep="")
+path_results <- paste(getwd(),"/working_data",sep="")
+data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
+
+# Read in list of site Indices; file created by create_nodes_list_d.R
[…]

### 2019-07-17 R/create_nodes_list_d.v4.7.R

@@ -1,0 +1,139 @@
+#' CREATE NODES LIST SCRIPT
+#' Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+#' Cite as:	arXiv:1504.08318 [physics.soc-ph]
+#' This is now version 3, incorporating corrections, performance and style improvements 10/5/15
+#' This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
+#' that is to say a partial matrix of distances between nodes.
+#' Distances are computed for each node with each successive node, working through the list.
+#' For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
+#' This uses an approach that creates file with only distances below a limit, e.g. 100km.
+#' This will then not be a fully interconnected network;
+#' 	need to ensure that this does not adversely affect clustering computation.
+#' Note original used the bigmemory library but this is not available for windows, so all refs removed.
+#' Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
+#' 	This data written out to text files.
+#' Version 4.1: 4/4/2016 -
+#' NOTE: problems with a matrix with #'REF entries in .csv -
+#'	No check for this, and caused problems with matrix manipulation
+#' Removed conversions to and from matrix data format for data, from original source. Not necessary
+#' Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
+#'     that input data now has additional Lat Long fields added, which are not used here
+#' Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
+#' Version 4.4: 8/5/16 - Change of source text file format to include map data
+#' Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
+#' Version 4.6: 07/11/17 - Change working directory for updated machine
+#' Version 4.7: 03/12/18 - add in unit parameter to select km or m, in "radius_values.txt"
+#'	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
[…]

### 2019-07-17 R/mapping_clusters.v4.12.R

@@ -1,0 +1,245 @@
+#' CLUSTER MAPPING SCRIPT
+#' Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+#' Cite as:	arXiv:1504.08318 [physics.soc-ph]
+#' Version 3a: 10/5/15 & 2/10/15 - with additions to include county boundary outlines,
+#' This code maps the clusters overlaid on an outline of the British Isles or Ireland including county outlines
+#' England and Wales shape files added from Portsmouth University files 31/1/16
+#' Version 4: 24/3/16. Changes to plots made to:
+#' 	Include identity of clusters (i.e.cluster index) in legend - done
+#' 	Plot the source of the original data (e.g. Atlas, Hogg etc.) (taken from source file name)- done
+#' 	Parameterise the shape file to be used for plotting ...
+#'	Take out graded grey colours for clusters > 15
+#' Version 4.1: 29/3/16 changed outputs to be multi-page pdf
+#'	NOTE: Ireland not plotting points TO BE RESOLVED
+#' Version 4.2: 6/4/16 - error in plot of all site corrected; removed 'xy'; all refs now to xy_data
+#' Version 4.3: 10/4/16 - output shape file with all data points, with same projection as input map
+#'     NOTE: esri shape file driver truncates names to 10 characters but this should not be a
+#'     problem at the moment. Prob of e.g. PlacesIndex, ClusterNumber etc.
+#' 	shape file name is name of source file without .csv etc. extension
+#' Version 4.4: 29/4/16 - paging upgraded to export to A4 and use the full page
+#' Version 4.5: 6/5/16 - changed Index name to fit within 8 chars -> PlcIndex
+#' Version 4.6: 8/5/16 - working on Ireland plot to fix. Problem seemed to be an old Ireland map with
+#'	an obsolete coordinate system
+#'	Add in external input to country and shape file for source,
+#'	file is added to source_file.txt - map name and shape file name, headers also added
+#'	source_file, map_name, shape_file
+#'	REQUIRES CHANGE TO ALL OTHER PROGRAMS (done)
+#' Version 4.7: 18/5/16 -  Cluster data now comes in a single file (member_cluster_by_radius.csv)
+#'   	output cluster ranks as new file site_cluster_rank_by_radius, lists by PlcIndex the cluster rank
+#'	indexed by radius
[…]

### 2019-07-19 paper.Rmd
überarbeitetes paper usw usf

@@
 ---
-title: "Percolation analysis"
+title: "Percolation Analysis – Archaeological applications at widely different spatial scales"
 author:
@@
 abstract: |
-  Percolation Analysis has been recently applied in Archaeology for identifying clusters and groupings at a national scale, for example investigating the distribution of Hillforts in Britain and Ireland, and Domesday sites in England.
+  This paper provides a summary of the Percolation Analysis method, and then provides two detailed case studies where the technique is applied at significantly different geographical scales.
+This will demonstrate not only the potential for the technique within archaeology, but also how it can be applied at different spatial scales with different objectives appropriate to the specific problem in question.
 The technique, originally developed in physics and more recently adopted in Geography, is a way of identifying groupings or clusters, purely based on spatial separation using Euclidian distance.
+In this paper, percolation Analysis is being applied for investigating the distribution of Hillforts in Britain and Ireland, and Domesday sites in England, identifying clusters and groupings at a national scale.
 The investigations for British Hillforts and Domesday sites have shown this to be a fruitful starting point for investigating possible socio-political entities, and patterns of deep history.
@@
 Aim here was to arrive at estimates of settlement sizes, which in turn can inform landscape archaeological surveys on the decision on attributing single finds to an already known site or registering a new site.
-This paper provides a summary of the Percolation Analysis method, and then provides two detailed case studies where the technique is applied at significantly different geographical scales.
-This will demonstrate not only the potential for the technique within archaeology, but also how it can be applied at different spatial scales with different objectives appropriate to the specific problem in question.
 keywords: |
-  spatial analysis; percolation; settlement archaeology
+  spatial analysis; percolation; settlement archaeology; clustering algorithm
 ---
@@
 This proposal outline covers a paper for submission to the Journal of the CAA, and a presentation at the German Chapter of the CAA to be held in Wilhelmshaven in September 2019.
-
-#Percolation Analysis – Archaeological applications at widely different spatial scales
 
@@
 Along the ca.
-13 km long and mostly 40 m broad part of the street over 6000 features were uncovered (Fahr in prep.), but I will focus on features from the later Bronze Age (group “Saalemündungsgruppe”).
+13 km long and mostly 40 m broad part of the street over 6000 features were uncovered (Fahr in prep.), but this paper will focus on features from the later Bronze Age (group “Saalemündungsgruppe”).
 For this periods the aim is to find the clusters which delineate a site with the help of percolation analysis.
 The radius will estimate the distance between features that belong together into one site.
-
-#### Data set
 
@@
 Machine trenching has been shown to be the most effective way to find sites [@hey_2006].
-The late Bronze age and the early iron age are not easily seperable in the settlements, because the ceramics are very similar.
-Researchers agree [@wagner_2004, 8 ; @heske_2005, 95] that there seems to be a settlement continuation between the two phases, while the burial practices change.
-Consequently many features have been dated in both periods.
-I deal with this by adding the uncertainly dated features to the late bronze age analysis as well.
 
-#### Theoretical Issues
 The term “site” has been at the center of a lively debate in survey archaeology over the last 40 years.
 Until the 70’s it has mostly been defined as a place [@dunnell_1992, 23-24] - a find spot, which is similar to German archaeology, where the term used, “Fundplatz”, means exactly that.
-In the German archaeological inventories, though, a site may contain several culturally distinct loci “Fundstellen” [@dauber_1950, 96], which are usually cataloged as a settlement, a burial ground, a hoard or as a single find spot of a period [@eggert_2005, 56].
+In the German archaeological inventories, though, a site may contain several culturally distinct loci, “Fundstellen” [@dauber_1950, 96], which are usually cataloged as a settlement, a burial ground, a hoard or as a single find spot of a period [@eggert_2005, 56].
 Two questions arise, when deciding how to classify a site as a settlement: Qualitatively, what kind of finds or features define a settlement [@linke_1976, 8], and quantitatively, of how far apart two “find spots” are supposed to be.
 If two sherds of the same time period are found 50 m apart - are these two sites or belong they to one site?
-In every larger settlement or landscape archaeological study this topic is being discussed and in the end a decision felled, which the authors agree, is kind of arbitrary and should actually rely on empiric studies [@malmer_1962; @mischka_2007].
+In every larger settlement or landscape archaeological study this topic is being discussed and in the end a decision felled, which the authors agree, is kind of arbitrary and should actually rely on empiric studies [@malmer_1962, 258; @mischka_2007, 49-50].
 Since the middle of the 1970s there has been the discussion of a non- or off-site approach to anglophone archaeology.
@@
 
-At this point the continuously excavated data set of the street and the clustering analysis percolation can be fruitfully connected: As percolation works with radii around points it may assist in quantitatively assessing which distances between features are common.
+At this point the continuously excavated data set of the street and the clustering analysis percolation can be fruitfully connected: As percolation works with radii around points it may assist in quantitatively assessing which distances between features are common and what distance features don't seem to belong to each other anymore.
+This question needs to be answered for each archaeological culture seperately as we cannot assume similar settlement distributions through time[@schirren_1997, 30].
+
 Assuming a connection between underground features and surface finds enables us to transfer the distances of the features to those of finds and may inform landscape archaeological surveys on the decision on attributing single finds to an already known site or registering a new site.
@@
 These are the distances, at which the clusters "stabilise" and don't grow with growing percolation radii.
+As mentioned above, the mean width of the excavated strip was 40m.
+Therefore it is assumed, that the first "stabilisation" is due to the lack of features beyond the edges of the excavation area.
 
@@
 The farmsteads in Zwenkau don't overlap [@huth_1998, 214] and the distances to each other are quite diverse.
-Nonetheless a number of them seem to scatter at at an intervall of ca.
+Nonetheless a number of them seem to scatter at at intervalls of ca.
 65-75 m.
@@
 We can therefore assume that at least partly the high density of settlement features belonging to the late bronze age might be interpreted as evidence of several phases or local re-settlement.
-Nonetheless we can notice that the two smaller radii detected as possible site delimiter by the percolation algorithm fall well into the range of the farmstead sizes of Zwenkau-Eythra.
+Nonetheless we can notice that the turning points of the radius vector by `r sBZ_turn_rmean[2]`m falls well into the range of the farmstead sizes of Zwenkau-Eythra and might be a possible farmstead site delimiter by the percolation algorithm.
 
-Mapping the clusters, though, reveals a different picture.
-As the percolation algorithm moves from node to node, the cluster groups are much larger than the radii.
-Here now it seems sensible to determine at what point the clusters detected by percolation show the best overlap to the site definitions by the Heritage Management.
+We note: As long as the next feature is `r sBZ_turn_rmean[2]`m away, features seem to belong to the same cluster.
+We can therefore assume, late bronze age finds at a distance of `r sBZ_turn_rmean[2]`m to each other to belong to the same site.
 
-IDee:
-Abgleich mit den vom LDA abgegrenzten sites bei welchem cluster-radius??
+Mapping the clusters reveals a more complete picture: As the percolation algorithm moves from node to node, the cluster groups are much larger than the radii.
+Should "in-between" finds be missing, still two findspots belonging to the same site might not identified as to belong to the same site.
+
+Nonetheless the question posed by Malmer and Mischka [@malmer_1962; @mischka_2007] on how to define the distance between to findspots before delimiting a new site has been answered in an empirical fashion as demanded.
 
 # Conclusion
+
+Percolation analysis offers...
+
+- great at different scales
+
+- different research questions might be answered:
+
+- cluster sizes, density of points inside a cluster
+
+- ...
 

### 2019-07-31 README.Rmd
setup.

@@
 
-The goal of percolatransect is to try the percolation analysis as given by Simon Maddison with my own data.
+The goal of percopackage is to create functions for the percolation analysis from Simon Maddison's scripts.
 
@@
 # install.packages("devtools")
-devtools::install_github("SCSchmidt/percolatransect")
+devtools::install_github("SCSchmidt/percopackage")
 ```

### 2019-07-31 paper.Rmd
setup.

--- 2019-07-16 paper.Rmd
@@
 ---
-title: "Percolation analysis of transect data"
+title: "Percolation Analysis – Building a Package"
 author:
+  -Maddison, Simon
+
   -Schmidt, Sophie C.
-  - Author Two
+
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
       fig_caption: yes
-      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
-
+csl: RGK_archaeology_DGUF.csl
+bibliography: sitedefinition.bib
 abstract: |
-  Text of abstract
+  The aim here is to create functions for percolation in R.
 keywords: |
-  keyword 1; keyword 2; keyword 3
-highlights: |
-  These are the highlights. 
+  spatial analysis; percolation; clustering algorithm
 ---
@@
 
-#library(percolatransect) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
+library(percopackage) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
 ```
 
-### Strip excavation in Germany
-The second case study is located in Saxony-Anhalt, middle Germany.
-During the early 2000s the street “Bundesstraße 6” was built near the town of Köthen.
-The area of the street, approach roads, exits and retention reservoirs were machine test trenched by the Heritage Management to find archaeological sites.
-Along the ca.
-13 km long and mostly 40 m broad part of the street over 6000 features were uncovered (Fahr in prep.), but I will focus on features from the later Bronze Age (group “Saalemündungsgruppe”).
-For this periods the aim is to find the clusters which delineate a site with the help of percolation analysis.
-The radius will estimate the distance between features that belong together into one site.
+# Data is in source_data
 
-#### Data set
+Bsp Datensatz hier sei sNL
 
-```{r}
-#Data cleaning and prep for Sophie
-
-# load data
-BefSchnitt <- read.csv2('source_data/Schnittbefunde4.csv', sep = "\t", dec = ",")
-
-# bringing the periods in the right order
-BefSchnitt$epoche <- ordered(BefSchnitt$epoche, levels = c("Neolithikum", "Bronzezeit", "Eisenzeit", "undat."))
-BefSchnitt$abschnitt <- ordered(BefSchnitt$abschnitt, levels =c('aelter', 'frueh','mittel', 'spaet'))
-BefSchnitt$kultur <- ordered(BefSchnitt$kultur, levels=c("Baalberge", "Bernburg", "Kugelamphorenkultur", "Trichterbecher", "Salzmuende", "Schnurkeramik", "Glockenbecher", "Aunjetitz", "Saalemuendungsgruppe", "sBZ/aeEZ", "Hausurnenkultur"))
-
-# subset settlement features
-siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
-
-#Subset the settlement features for relevant cultures
-# there are 389 features dated as late bronze age and early iron age, that are being analysed in sBZ as well
-siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
-siedlung_sBZ_Bef <-siedlung_sBZ_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_sBZ_Bef, "source_data/BefundesBZ-minimal.csv")
-
-```
-
-There are 1005 settlement features cataloged as belonging to this period.
-
-Because of the test trenching it is assumed, that all features and sites along the transect have been found, even though there are gaps between the actual excavation areas and many features remain undated.
-Machine trenching has been shown to be the most effective way to find sites [@hey_2006].
-Admittedly even then not all sites are discovered, especially Neolithic ones have the least probability to be found, which may be one reason for the small number of Neolithic features in the transect.
-The late Bronze age and the early iron age are not easily seperable in the settlements, because the ceramics are very similar.
-Researchers agree [@wagner_2004, 8 ; @heske_2005, 95] that there seems to be a settlement continuation between the two phases, while the burial practices change.
-Consequently many features have been dated in both periods.
-I deal with this by adding the uncertainly dated features to the late bronze age analysis as well.
-
-#### Theoretical Issues
-The term “site” has been at the center of a lively debate in survey archaeology over the last 40 years.
-Until the 70’s it has mostly been defined as a place [@dunnell_1992, 23-24] - a find spot, which is similar to German archaeology, where the term used, “Fundplatz”, means exactly that.
-In the German archaeological inventories, though, a site may contain several culturally distinct loci “Fundstellen” [@dauber_1950, 96], which are usually cataloged as a settlement, a burial ground, a hoard or as a single find spot of a period [@eggert_2005, 56].
-Two questions arise, when deciding how to classify a site as a settlement: Qualitatively, what kind of finds or features define a settlement [@linke_1976, 8], and quantitatively, of how far apart two “find spots” are supposed to be.
-If two sherds of the same time period are found 50 m apart - are these two sites or belong they to one site?
-In every larger settlement or landscape archaeological study this topic is being discussed and in the end a decision felled, which the authors agree, is kind of arbitrary and should actually rely on empiric studies [@malmer_1962; @mischka_2007].
-Since the middle of the 1970s there has been the discussion of a non- or off-site approach to anglophone archaeology.
-The terms were introduced by Thomas [-@thomas_1975] and Foley [-@foley_1981] and describe the analysis of finds "between sites".
-This approach understands the archaeological record  as a continual distribution in space, with spots of higher densities, the so-called “sites”, and areas of lower density [@wobst_1983, 39].
-At this point the continuously excavated data set of the street and the clustering analysis percolation can be fruitfully connected: As percolation works with radii around points it may assist in quantitatively assessing which distances between features are common.
-Assuming a connection between underground features and surface finds enables us to transfer the distances of the features to those of finds and may inform landscape archaeological surveys on the decision on attributing single finds to an already known site or registering a new site.
-Of course, settlement features only comprise the “build space” of a settlement.
-Though features in-between sites may exist, like traps or temporary storage facilities, places like working areas or fields which may be detected by off-site surface find distributions, won’t be included.
-
-### Percolation
-
-```{r eval=FALSE, include=FALSE}
+```{r include=FALSE}
 
@@
 
-upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
-500,2,1, 1000,0,0,1
+#upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
+#500,2,1, 1000,0,0,1
 
-source("create_nodes_list_d.v4.7.R")
-source("clustering_script.v3.6.R")
-source("mapping_clusters.v4.12.R")# Fehler in ogrInfo(dsn = dsn, layer = layer, encoding = encoding, use_iconv = use_iconv, : Cannot open data source...
-weeiiiiird...
-nochmal auf anderer Maschine testen.
+library(maptools)
+library(rgdal)
+library(stringr)
+library(igraph)
 
-source("cluster_frequency_script.v2.17.R")
+source("R/create_nodes_list_d.v4.7.R")
+percolateNodes()
+
+source("R/clustering_script.v3.6.R")
+percolate()
+
+#source("R/mapping_clusters.v4.12.R")
+#mapClusters()
+
+library(calibrate)
+library(Hmisc)
+
+source("R/cluster_frequency_script.v2.17.R")
+clusterFrequency()
 
 ```
-
-As this analysis is concerned with a very fine level of detail, the starting point and the step size of the percolation algorithm was chosen to be 1m.
-The size of a prehistoric village in middle Germany can’t be assumed to be larger than a kilometer in diameter, therefore the largest radius used was 500m.
-
-```{r mean cluster size, eval=FALSE, include=FALSE}
-library(ggplot2)
-library(ggrepel)
-# not included because the mean cluster size ist too different because of hugely different sample sizes
-
-mean_steps <- c(1,1+which(diff(analysis_by_radius$mean_clust_size)!=0))
-
-sBZ_meansteps <- as.data.frame(cbind(analysis_by_radius$radius[mean_steps], analysis_by_radius$mean_clust_size[mean_steps]))
-
-sBZ_meansteps <- subset(sBZ_meansteps, sBZ_meansteps$V1 == 46 | sBZ_meansteps$V1 == 68 | sBZ_meansteps$V1 == 88 |  sBZ_meansteps$V1 == 140 | sBZ_meansteps$V1 == 175 | sBZ_meansteps$V1 == 221 | sBZ_meansteps$V1 == 297 |sBZ_meansteps$V1 == 374)
-
-ggplot()+
-  geom_line(data = analysis_by_radius, aes(x = radius, y = mean_clust_size))+
-  geom_point(data = sBZ_meansteps, aes(x = sBZ_meansteps$V1, y = sBZ_meansteps$V2))+
-  geom_label_repel(aes(x = sBZ_meansteps$V1, y = sBZ_meansteps$V2, label = sBZ_meansteps$V1),
-                     box.padding   = 0.35, 
-                   point.padding = 0.5,
-                   nudge_y = 50,
-                  segment.color = "grey50",
-                  color = "grey50")+
-  theme_light()+
-  labs(title = "Sizes of clusters increasing with percolation radius",
-         x = "Percolation radius",
-       y = "Mean Cluster size")
-
-ggsave("mean_clusters_sBZ.png", height = 10, width =  20, units = "cm", dpi = 600  )
-
-```
-
-There are several levels of clustering.
-Features of the late Bronze Age create a steep curve in the beginning, which shows a close clustering at low percolation radii.
-Longer stretches of flattening might be interpreted as the algorithm running out of features to add to the clusters.
-We thereby find the edges of settlements and can define their size.
-The step-wise rises at higher percolation radii needs explanation as well.
-To provide these, the results will be compared to large scale excavations of settlements in middle Germany.
-
-I highlighted those points that mark the most distinctive steps in the distribution.
-We can see the radii after which the algorithm doesn't change the cluster size for some time, showing that here stretches of space between features exist.
-If the dataset is forced to split into two groups the step at  `r sBZ_turn_rmean[2]` radius turns out to be the splitting point of the mean cluster sizes calculated.
-
-```{r mean cluster size turning points, include=FALSE}
-
-# calculate turning points of distance measure vectors
-# google terms: knee of curve, "trade off point"
-#https://dataplatform.cloud.ibm.com/analytics/notebooks/54d79c2a-f155-40ec-93ec-ed05b58afa39/view?access_token=6d8ec910cf2a1b3901c721fcb94638563cd646fe14400fecbb76cea6aaae2fb1
-
-#https://www.rdocumentation.org/packages/SamSPECTRAL/versions/1.26.0/topics/kneepointDetection
-
-#install.packages("ecp")
-library("ecp")
-
-# same late bronze age
-turn_sBZ_mean <- e.divisive(as.matrix(diff(analysis_by_radius$mean_clust_size)), k = 1, min.size = nrow(analysis_by_radius)/10)
-
-sBZ_turn_rmean <-analysis_by_radius$radius[turn_sBZ_mean$estimates]
-
-```
-
-## interpretation
-
-The late bronze age features are mostly concentrated in the western half and on the eastern-most part of the transsect.
-As can be seen by the rapidly rising graph describing the mean cluster size in relation to the percolation radius, the features cluster closely by each other.
-First steps in the distribution can be seen at 46 m, 68 m and 88 m.
-These are the distances, at which the clusters "stabilise" and don't grow with growing percolation radii.
-
-The largest excavation site of the late bronze age in middle Germany is to be found in Zwenkau(-Eythra) in Saxony, which was excavated in advance of coal mining.
-At Zwenkau several single farmsteads delimited by houses and fences spread over the whole excavation area, which measures at its greatest dimensions 1100 x 825 m [@huth_1998, 194.213].
-The farmsteads in Zwenkau don't overlap [@huth_1998, 214] and the distances to each other are quite diverse.
-Nonetheless a number of them seem to scatter at at an intervall of ca.
-65-75 m.
-[cf.
-@huth_1998, 211, fig.
-6].
-The farmsteads themselves are not all the same size, but the longest sides show to about 50 - 85m long (cumulating to sizes of 2000 - 2500 m²) [@huth_1998, 213.].
-It is assumed not all of them existed at the same time, but that there were always several isolated farmsteads in a scattered distribution to each other [@huth_1998, 214].
-
-At the analysed transect excavation we also deal with a depth in time, as there are overlapping features and several ditches, which most probably did not exist at the same time, but can be interpreted as indices of small-scale settlement shifts.
-
-Damit liegen sie recht nahe beieinander, was, würde hier eine ähnliche Untersuchung durchgeführt werden wie in der vorliegenden Arbeit, zu schlechten Abgrenzungsmöglichkeiten von Siedlungsstätten führen könnte.
-Auf dem zitierten Plan sind jedoch nur Hausgrundrisse und Zaungräbchen eingezeichnet, was eine Vergleichbarkeit erschwert.
-Zudem gehen die Bearbeiter davon aus, dass die einzelnen Gehöfte nicht zeitgleich waren, sondern eine Wechselsiedlung bestand, in der stets mehrere Gehöfte in Streulage zueinander standen^[@huth_1998, 214.].
-
-Im Arbeitsgebiet entlang der B6n ist innerhalb der Spätbronzezeit ebenfalls mit einer zeitlichen Tiefe der Befunde zu rechnen^[Belegt durch Befundüberschneidungen z.
-B.
-zwischen einem Pfostenbau (Befundnummer 11333) und einer Grube (Befundnummer 11028)].
-Im Westen der Trasse (zw.
-Fpl.
-4 und 11) sind zudem vier Gräben aufgedeckt worden.
-Gräben werden häufig als Siedlungsgrenzen interpretiert.
-Die Abstände zueinander (720 m, 370 m, 440 m) sowie die Ausrichtungen des westlichsten und östlichsten der Gräben, die beide gegen Osten abzugrenzen scheinen, lassen jedoch vermuten, dass sie nicht gleichzeitig bestanden, sondern ein Zeichen kleinräumiger Verlagerungen darstellen.
-Die hohe Dichte der Befunde der Spätbronzezeit ist damit sicherlich zum Teil Ergebnis einer ortskonstanten Siedlungsweise^[Wie z.B.
-der Wechselsiedlung, wie sie für Zwenkau vorgeschlagen wurde (@huth_1998, 208).].
-Nichtsdestotrotz zeichnen sich Befundcluster mit einem Radius von 33 m ab, deren Dopplung, 66 m, innerhalb des Bereichs der Größe der Einzelhöfe in Zwenkau liegt.
-Zwischen Fpl.
-4 und 11 liegen neben sehr dichten Clustern sowohl fundleere Bereiche als auch Stellen mit geringerer Befundkonzentration.
-
-Nach diesen Ergebnissen liegen spätbronzezeitliche Befunde in kleineren Radien (in Analogie zu Zwenkau in Einzelhöfen) eng beieinander, während in der älteren Eisenzeit in größeren Abständen und größeren Zusammenhängen gebaut wurde.
-In beiden Fällen ist jedoch mit zeitlicher Tiefe zu rechnen und einer schlechten Abgrenzbarkeit von Siedlungsstätten zueinander.
-
-Es ist jedoch auch vorher schon festgestellt worden „Man hat es [..] in der Jungbronze- und Früheisenzeit mit vielfältigen Besiedlungsformen
-zu tun“^[@huth_1998, 216.].
-Erschwerend kommt hinzu, dass durch die ungenauen Datierungsmöglichkeiten hier eine sehr tiefe Zeitspanne vorliegt, bei der in jeder Analyse eventuelle chronologische Unterschiede verwischt werden.
-
-Interessant bleibt es festzuhalten, dass sich durchaus Unterschiede zwischen der Spätbronzezeit und den auch ältereisenzeitlich datierten Befunden fassen lassen.
-Ob dies ein zufälliger Effekt oder ein Hinweis für Veränderungen im Siedlungsverhalten ist, können nur weitere Untersuchungen klären.
-
-IDee:
-Abgleich mit den vom LDA abgegrenzten sites bei welchem cluster-radius??
-
-# Conclusion
 

### 2019-07-31 cluster_frequency_script.v2.16.R

@@ -1,212 +1,0 @@
-# CLUSTER FREQENCY PLOTTING SCRIPT
-# Simon Maddison, 10th May 2015
-# Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs # of clusters
-# Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
-# Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
-# Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
-# 	(currently max size). Changed outputs to multi-page pdf files
-# Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
-# Version 2.5: 23/4/16 -
-#	Added in computations for clusters of single nodes
-# 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
-#	Table of max, mean and median exported
-# Version 2.6: 26/4/16 -
-# 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
-# 	Exclude clusters with less than a certain threshold of nodes (parameter)
-# 	Also exclude largest cluster from mean
-# 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
-# Version 2.7: 29/4/16 -
-#	As per Elsa's published paper, plot max cluster size vs. radius as well
-# 	Page format improved to generate pdf A4 format
-# 	Bug fixed when adding clusters of size 1 (if null value)
-# Version 2.8: 4/5/16 -
-#	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
-# Version 2.9: 6/5/16 -
-#	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
-# Version 2.10: 8/5/16 - source text file format changed to include map information
-# Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
-#	File is member_cluster_by_radius.csv
-# Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
-#	Make the image square or else it distorts the plot (note that this does not happen in pdf)
-# 	Remove simple cluster rank plots, no longer useful
-# Version 2.13: 7/11/17	- amended working directory path for new pc
[…]

### 2019-07-31 cluster_frequency_script.v2.17.R

@@ -1,246 +1,0 @@
-# CLUSTER FREQENCY PLOTTING SCRIPT
-# Simon Maddison, 10th May 2015
-# Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs # of clusters
-# Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
-# Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
-# Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
-# 	(currently max size). Changed outputs to multi-page pdf files
-# Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
-# Version 2.5: 23/4/16 -
-#	Added in computations for clusters of single nodes
-# 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
-#	Table of max, mean and median exported
-# Version 2.6: 26/4/16 -
-# 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
-# 	Exclude clusters with less than a certain threshold of nodes (parameter)
-# 	Also exclude largest cluster from mean
-# 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
-# Version 2.7: 29/4/16 -
-#	As per Elsa's published paper, plot max cluster size vs. radius as well
-# 	Page format improved to generate pdf A4 format
-# 	Bug fixed when adding clusters of size 1 (if null value)
-# Version 2.8: 4/5/16 -
-#	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
-# Version 2.9: 6/5/16 -
-#	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
-# Version 2.10: 8/5/16 - source text file format changed to include map information
-# Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
-#	File is member_cluster_by_radius.csv
-# Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
-#	Make the image square or else it distorts the plot (note that this does not happen in pdf)
-# 	Remove simple cluster rank plots, no longer useful
[…]

### 2019-07-31 clustering_script.v3.6.R

@@ -1,122 +1,0 @@
-# CLUSTERING SCRIPT, RUNS AFTER NODES LIST SCRIPT
-# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-# Cite as:	arXiv:1504.08318 [physics.soc-ph]
-# Version 3
-# This is version 3, incorporating adjustments and enhancements to code 10/5/15 & 2/10/15
-# This code computes the clusters, based on matrix of inter-nodal distances computed in script
-#  	create_nodes_list_d.vxxx.R
-# Note that the list of nodes and internodal distances is not a complete matrix, but only includes
-# 	distances below a certain threshold. This keeps the data sizes manageable.
-# Note that the original used library bigmemory but this is not available for windows so all refs removed.
-# Note that when nodes are individual, they are no longer in a cluster. (31/1/16)
-# Version 3.1: 20/04/16 - Note that this intrinsically cannot generate clusters with only one node.
-#   	Need to post process means in the analysis script
-# Version 3.2: 6/5/16 - Changed Index name to fit within 8 chars -> PlcIndex
-# Version 3.3: 18/5/16 - output data into a single file, indexed on PlcIndex and radius instead of separate
-#	files. Read in PlcIndex.csv generated by create_nodes_list_d....R
-# Version 3.4: 7/11/17 - path of working directory amended for new PC
-# Version 3.6: 04/12/18 - changes in Version 3.5 omitted
-# 	Add in unit parameter to select km or m, in "radius_values.txt"
-#	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
-#	so that a unit value of 1 shows through as metres, and a value of 1000 as km. Other values accomodated.
-# 	NOTE: no modification necessary to work for fractional values of radius, e.g. step size of 0.1km???????????????
-
-library(igraph)
-#setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #path on laptop
-# paths
-path_source <- paste(getwd(),"/source_data",sep="")
-path_results <- paste(getwd(),"/working_data",sep="")
-data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
-
-# Read in list of site Indices; file created by create_nodes_list_d.R
-file_name <- paste(path_results,"/","PlcIndex.csv",sep="")
[…]

### 2019-07-31 create_nodes_list_d.v4.7.R

@@ -1,136 +1,0 @@
-# CREATE NODES LIST SCRIPT
-# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-# Cite as:	arXiv:1504.08318 [physics.soc-ph]
-# This is now version 3, incorporating corrections, performance and style improvements 10/5/15
-# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
-# that is to say a partial matrix of distances between nodes.
-# Distances are computed for each node with each successive node, working through the list.
-# For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
-# This uses an approach that creates file with only distances below a limit, e.g. 100km.
-# This will then not be a fully interconnected network;
-# 	need to ensure that this does not adversely affect clustering computation.
-# Note original used the bigmemory library but this is not available for windows, so all refs removed.
-# Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
-# 	This data written out to text files.
-# Version 4.1: 4/4/2016 -
-# NOTE: problems with a matrix with #REF entries in .csv -
-#	No check for this, and caused problems with matrix manipulation
-# Removed conversions to and from matrix data format for data, from original source. Not necessary
-# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
-#     that input data now has additional Lat Long fields added, which are not used here
-# Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
-# Version 4.4: 8/5/16 - Change of source text file format to include map data
-# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
-# Version 4.6: 07/11/17 - Change working directory for updated machine
-# Version 4.7: 03/12/18 - add in unit parameter to select km or m, in "radius_values.txt"
-#	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
-#	so that a unit value of 1 shows through as metres, and a value of 1000 as km. Other values accomodated
-
[…]

### 2019-07-31 data_prep.R

@@ -1,32 +1,0 @@
-#Data cleaning and prep for Sophie
-
-# load data
-BefSchnitt <- read.csv2('source_data/Schnittbefunde4.csv', sep = "\t", dec = ",")
-
-# bringing the periods in the right order
-BefSchnitt$epoche <- ordered(BefSchnitt$epoche, levels = c("Neolithikum", "Bronzezeit", "Eisenzeit", "undat."))
-BefSchnitt$abschnitt <- ordered(BefSchnitt$abschnitt, levels =c('aelter', 'frueh','mittel', 'spaet'))
-BefSchnitt$kultur <- ordered(BefSchnitt$kultur, levels=c("Baalberge", "Bernburg", "Kugelamphorenkultur", "Trichterbecher", "Salzmuende", "Schnurkeramik", "Glockenbecher", "Aunjetitz", "Saalemuendungsgruppe", "sBZ/aeEZ", "Hausurnenkultur"))
-
-# subset settlement features
-siedlung_BefSchnitt <- subset(BefSchnitt, BefSchnitt$befundart=='Siedlung')
-
-#Subset the settlement features for relevant cultures
-# there are 389 features dated as late bronze age and early iron age, that are being analysed in both epochs
-siedlung_SnK_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$kultur=='Schnurkeramik')
-siedlung_SnK_Bef <-siedlung_SnK_Bef[c('PlcIndex', 'Easting', 'Northing')]
-write.csv(siedlung_SnK_Bef, "source_data/BefundesNL-minimal.csv", row.names = FALSE)
-
-siedlung_fBZ_Bef <- subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='frueh')
-siedlung_fBZ_Bef <-siedlung_fBZ_Bef[c("PlcIndex", 'Easting', 'Northing')]
-write.csv(siedlung_fBZ_Bef, "source_data/BefundefBZ-minimal.csv")
-
-siedlung_sBZ_Bef <-subset(siedlung_BefSchnitt, siedlung_BefSchnitt$epoche=='Bronzezeit' & siedlung_BefSchnitt$abschnitt=='spaet')
[…]

### 2019-07-31 old_scripts/cluster_frequency_script.v2.15.R

@@ -1,244 +1,0 @@
-# CLUSTER FREQENCY PLOTTING SCRIPT
-# Simon Maddison, 10th May 2015
-# Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs # of clusters
-# Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
-# Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
-# Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
-# 	(currently max size). Changed outputs to multi-page pdf files
-# Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
-# Version 2.5: 23/4/16 -
-#	Added in computations for clusters of single nodes
-# 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
-#	Table of max, mean and median exported
-# Version 2.6: 26/4/16 -
-# 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
-# 	Exclude clusters with less than a certain threshold of nodes (parameter)
-# 	Also exclude largest cluster from mean
-# 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
-# Version 2.7: 29/4/16 -
-#	As per Elsa's published paper, plot max cluster size vs. radius as well
-# 	Page format improved to generate pdf A4 format
-# 	Bug fixed when adding clusters of size 1 (if null value)
-# Version 2.8: 4/5/16 -
-#	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
-# Version 2.9: 6/5/16 -
-#	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
-# Version 2.10: 8/5/16 - source text file format changed to include map information
-# Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
-#	File is member_cluster_by_radius.csv
-# Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
-#	Make the image square or else it distorts the plot (note that this does not happen in pdf)
-# 	Remove simple cluster rank plots, no longer useful
[…]

### 2019-07-31 old_scripts/clustering_script.v3.4.R

@@ -1,103 +1,0 @@
-# CLUSTERING SCRIPT, RUNS AFTER NODES LIST SCRIPT
-# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-# Cite as:	arXiv:1504.08318 [physics.soc-ph]
-# Version 3
-# This is version 3, incorporating adjustments and enhancements to code 10/5/15 & 2/10/15
-# This code computes the clusters, based on matrix of inter-nodal distances computed in script
-#  	create_nodes_list_d.vxxx.R
-# Note that the list of nodes and internodal distances is not a complete matrix, but only includes
-# 	distances below a certain threshold. This keeps the data sizes manageable.
-# Note that the original used library bigmemory but this is not available for windows so all refs removed.
-# Note that when nodes are individual, they are no longer in a cluster. (31/1/16)
-# Version 3.1: 20/04/16 - Note that this intrinsically cannot generate clusters with only one node.
-#   	Need to post process means in the analysis script
-# Version 3.2: 6/5/16 - Changed Index name to fit within 8 chars -> PlcIndex
-# Version 3.3: 18/5/16 - output data into a single file, indexed on PlcIndex and radius instead of separate
-#	files. Read in PlcIndex.csv generated by create_nodes_list_d....R
-# Version 3.4: 7/11/17 - path of working directory amended for new PC
-
-library(igraph)
-setwd("E:/MA_Erweiterung/percolatransect") # changed for me (SCS)
-# paths
-path_source <- paste(getwd(),"/source_data",sep="")
-path_results <- paste(getwd(),"/working_data",sep="")
-data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
-
-# Read in list of site Indices; file created by create_nodes_list_d.R
-file_name <- paste(path_results,"/","PlcIndex.csv",sep="")
-# This is used as the basis for the output file
-mem_clust_by_r <- read.csv(file_name,header=TRUE)
-
-# Read in distance thresholds - this ensures same values used in all scripts
-# Edit the  file radius_values.txt to change these.
-file_name <- paste(path_results,"/","radius_values.txt",sep="")
-radius_values <- read.csv(file_name,header=TRUE)
-upper_radius <- radius_values$upper_radius
-lower_radius <- radius_values$lower_radius
[…]

### 2019-07-31 old_scripts/create_nodes_list_d.v4.6.R

@@ -1,135 +1,0 @@
-# CREATE NODES LIST SCRIPT
-# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-# Cite as:	arXiv:1504.08318 [physics.soc-ph]
-# This is now version 3, incorporating corrections, performance and style improvements 10/5/15
-# This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
-# that is to say a partial matrix of distances between nodes.
-# Distances are computed for each node with each successive node, working through the list.
-# For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
-# This uses an approach that creates file with only distances below a limit, e.g. 100km.
-# This will then not be a fully interconnected network;
-# 	need to ensure that this does not adversely affect clustering computation.
-# Note original used the bigmemory library but this is not available for windows, so all refs removed.
-# Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
-# 	This data written out to text files.
-# Version 4.1: 4/4/2016 -
-# NOTE: problems with a matrix with #REF entries in .csv -
-#	No check for this, and caused problems with matrix manipulation
-# Removed conversions to and from matrix data format for data, from original source. Not necessary
-# Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
-#     that input data now has additional Lat Long fields added, which are not used here
-# Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
-# Version 4.4: 8/5/16 - Change of source text file format to include map data
-# Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
-# Version 4.6: 07/11/17 - Change working directory for updated machine
-
-setwd("E:/MA_Erweiterung/percolatransect") # changed for me (SCS)
-# paths
-path_source <- paste(getwd(),"/source_data",sep="")
-path_results <- paste(getwd(),"/working_data",sep="")
-
-# Read in source file name defined in file source_file.txt
-file_name <- paste(path_results,"/","source_file.txt",sep="")
[…]

### 2019-07-31 old_scripts/mapping_clusters.v4.10.R

@@ -1,227 +1,0 @@
-# CLUSTER MAPPING SCRIPT
-# Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-# Cite as:	arXiv:1504.08318 [physics.soc-ph]
-# Version 3a: 10/5/15 & 2/10/15 - with additions to include county boundary outlines,
-# This code maps the clusters overlaid on an outline of the British Isles or Ireland including county outlines
-# England and Wales shape files added from Portsmouth University files 31/1/16
-# Version 4: 24/3/16. Changes to plots made to:
-# 	Include identity of clusters (i.e.cluster index) in legend - done
-# 	Plot the source of the original data (e.g. Atlas, Hogg etc.) (taken from source file name)- done
-# 	Parameterise the shape file to be used for plotting ...
-#	Take out graded grey colours for clusters > 15
-# Version 4.1: 29/3/16 changed outputs to be multi-page pdf
-#	NOTE: Ireland not plotting points TO BE RESOLVED
-# Version 4.2: 6/4/16 - error in plot of all site corrected; removed 'xy'; all refs now to xy_data
-# Version 4.3: 10/4/16 - output shape file with all data points, with same projection as input map
-#     NOTE: esri shape file driver truncates names to 10 characters but this should not be a
-#     problem at the moment. Prob of e.g. PlacesIndex, ClusterNumber etc.
-# 	shape file name is name of source file without .csv etc. extension
-# Version 4.4: 29/4/16 - paging upgraded to export to A4 and use the full page
-# Version 4.5: 6/5/16 - changed Index name to fit within 8 chars -> PlcIndex
-# Version 4.6: 8/5/16 - working on Ireland plot to fix. Problem seemed to be an old Ireland map with
-#	an obsolete coordinate system
-#	Add in external input to country and shape file for source,
-#	file is added to source_file.txt - map name and shape file name, headers also added
-#	source_file, map_name, shape_file
-#	REQUIRES CHANGE TO ALL OTHER PROGRAMS (done)
-# Version 4.7: 18/5/16 -  Cluster data now comes in a single file (member_cluster_by_radius.csv)
-#   	output cluster ranks as new file site_cluster_rank_by_radius, lists by PlcIndex the cluster rank
-#	indexed by radius
[…]

### 2019-07-31 paper.Rmd
changed create_nodes to take input in function

@@
 
+# create df from input data set
+data <- read.csv("source_data/BefundesNL-minimal.csv", sep = ",") #' crazy mistakes happen if this is wrong...
+#' This file needs three columns: PlcIndex, Easting, Northing in this order.
+#' Additional fields Lat Long not used for this program.
+#' Note that the Easting and Northing need to be UK grid references with the Alphabetic
+#'  grid square converted to a numeric prefix for each
+#' List any entries with null values and write to file
+
 ## run analysis and save results of every run.
@@
 source("R/create_nodes_list_d.v4.7.R")
-percolateNodes()
+percolateNodes(data = data, radius_values = 10, limit = 500, radius_unit = 1)
 

### 2019-07-31 R/create_nodes_list_d.v4.7.R

@@ -26,39 +26,15 @@
 #'	NOTE: values are assumed to be in metres, unit will factor this in calculations and charts by the unit value
 #'	so that a unit value of 1 shows through as metres, and a value of 1000 as km. Other values accomodated
 
+## Sophie's trial to make functions here.
 
-#'setwd("/home/sophie/Dokumente/Konferenzen/percolatransect/") #'path on laptop
-percolateNodes <- function(x) {
+percolateNodes <- function(data, radius_values, limit, radius_unit) {
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")
-
-#' Read in source file name defined in file source_file.txt
-file_name <- paste(path_results,"/","source_file.txt",sep="")
-source_files <- read.csv(file_name,header=TRUE,stringsAsFactors=FALSE)
-source_file_name <- source_files$source_file
-#' Edit this file for different input file name
-
-#' Original file has been generated from Hogg Index spreadsheet
-#' Irish file was derived from material from the Atlas, ca. 14 May 2015
-#' Later analyses run in the same way on Atlas data March 2016 and on published data November 2017
-
-source_file <- paste(path_source,"/",source_file_name,sep="")
-
-#' Read in limit value from source file
-#' Edit the source file radius_values.txt to change this.
-file_name <- paste(path_results,"/","radius_values.txt",sep="")
-radius_values <- read.csv(file_name,header=TRUE)
-limit <- radius_values$limit
-radius_unit <- radius_values$radius_unit
 
 ptm <- proc.time()
 #' For computation time
 
-data <- read.csv(source_file, sep = ",") #' crazy mistakes happen if this is wrong...
-#' This file needs three columns: PlcIndex, Easting, Northing in this order.
-#' Additional fields Lat Long not used for this program.
-#' Note that the Easting and Northing need to be UK grid references with the Alphabetic
-#'  grid square converted to a numeric prefix for each
 #' List any entries with null values and write to file
 data_NA <- data[rowSums(is.na(data)) > 0,]
 print(paste("Entries in source file with one or more null values: "))

### 2019-07-31 paper.Rmd
work on mapping - function.

@@
 
-## run analysis and save results of every run.
-
-### input in source _file.txt
-
-#source_file,map_name,shape_file_name,DTM_file_name
-#BefundesBZ-minimal.csv, late bronze age features,alle_Schnitt-Fundstellen.shp,
-
-### input in radius_values.txt (stays)
-
-#upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
-#500,2,1, 1000,0,0,1
+sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp"
 
@@
 
-#source("R/mapping_clusters.v4.12.R")
-#mapClusters()
+percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1)
+
+source("R/mapping_clusters.v4.12.R")
+mapClusters(data = data, shape = sNL_shape)
 

### 2019-07-31 R/mapping_clusters.v4.12.R

@@ -1,76 +1,15 @@
-#' CLUSTER MAPPING SCRIPT
-#' Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-#' Cite as:	arXiv:1504.08318 [physics.soc-ph]
-#' Version 3a: 10/5/15 & 2/10/15 - with additions to include county boundary outlines,
-#' This code maps the clusters overlaid on an outline of the British Isles or Ireland including county outlines
-#' England and Wales shape files added from Portsmouth University files 31/1/16
-#' Version 4: 24/3/16. Changes to plots made to:
-#' 	Include identity of clusters (i.e.cluster index) in legend - done
-#' 	Plot the source of the original data (e.g. Atlas, Hogg etc.) (taken from source file name)- done
-#' 	Parameterise the shape file to be used for plotting ...
-#'	Take out graded grey colours for clusters > 15
-#' Version 4.1: 29/3/16 changed outputs to be multi-page pdf
-#'	NOTE: Ireland not plotting points TO BE RESOLVED
-#' Version 4.2: 6/4/16 - error in plot of all site corrected; removed 'xy'; all refs now to xy_data
-#' Version 4.3: 10/4/16 - output shape file with all data points, with same projection as input map
-#'     NOTE: esri shape file driver truncates names to 10 characters but this should not be a
-#'     problem at the moment. Prob of e.g. PlacesIndex, ClusterNumber etc.
-#' 	shape file name is name of source file without .csv etc. extension
-#' Version 4.4: 29/4/16 - paging upgraded to export to A4 and use the full page
-#' Version 4.5: 6/5/16 - changed Index name to fit within 8 chars -> PlcIndex
-#' Version 4.6: 8/5/16 - working on Ireland plot to fix. Problem seemed to be an old Ireland map with
-#'	an obsolete coordinate system
-#'	Add in external input to country and shape file for source,
-#'	file is added to source_file.txt - map name and shape file name, headers also added
-#'	source_file, map_name, shape_file
-#'	REQUIRES CHANGE TO ALL OTHER PROGRAMS (done)
-#' Version 4.7: 18/5/16 -  Cluster data now comes in a single file (member_cluster_by_radius.csv)
-#'   	output cluster ranks as new file site_cluster_rank_by_radius, lists by PlcIndex the cluster rank
-#'	indexed by radius
-#' Version 4.8: 30/7/16 - Plot as png file output. Earlier issues with resolution resolved.
[…]

### 2019-07-31 R/nodes_clust.R

@@ -1,0 +1,193 @@
+#' CREATE NODES LIST SCRIPT
+#' Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
+#' Cite as:	arXiv:1504.08318 [physics.soc-ph]
+#' This is now version 3, incorporating corrections, performance and style improvements 10/5/15
+#' This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
+#' that is to say a partial matrix of distances between nodes.
+#' Distances are computed for each node with each successive node, working through the list.
+#' For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
+#' This uses an approach that creates file with only distances below a limit, e.g. 100km.
+#' This will then not be a fully interconnected network;
+#' 	need to ensure that this does not adversely affect clustering computation.
+#' Note original used the bigmemory library but this is not available for windows, so all refs removed.
+#' Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
+#' 	This data written out to text files.
+#' Version 4.1: 4/4/2016 -
+#' NOTE: problems with a matrix with #'REF entries in .csv -
+#'	No check for this, and caused problems with matrix manipulation
+#' Removed conversions to and from matrix data format for data, from original source. Not necessary
+#' Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
+#'     that input data now has additional Lat Long fields added, which are not used here
+#' Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
+#' Version 4.4: 8/5/16 - Change of source text file format to include map data
+#' Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
+#' Version 4.6: 07/11/17 - Change working directory for updated machine
+#' Version 4.7: 03/12/18 - add in unit parameter to select km or m, in "radius_values.txt"
[…]

### 2019-07-31 paper.Rmd
fixed mem_clust_by_r not found
-> wird als csv exportiert, dann wieder importiert. sinnig???

@@
 
-sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp"
+sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp")
 
@@
 source("R/mapping_clusters.v4.12.R")
-mapClusters(data = data, shape = sNL_shape)
+mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape)
 

### 2019-07-31 R/map_clust.R

@@ -1,8 +1,11 @@
 
-mapClusters <- function(data, shape) {
+mapClusters <- function(data, radius_values, limit, radius_unit, shape, upper_radius, lower_radius, step_value) {
 
+percolate2(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value)
+  
 path_results <- paste(getwd(),"/working_data",sep="")
 path_maps <- paste(getwd(),"/maps",sep="")
+data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
 
 # Truncate shape file name to remove extension
 layer_name <- substr(shape,1,(nchar(shape)-4))
@@ -23,12 +26,6 @@ proj4string(xy_data) <- crs_projection
 file_name <- paste(path_results,"/","member_cluster_by_radius.csv",sep="")
 ranked_mem_clust_by_r <- read.csv(file_name, header=TRUE)
 
-# Read in distance thresholds - this ensures same values used as in clustering script
-file_name <- paste(path_results,"/","radius_values.txt",sep="")
-radius_values <- read.csv(file_name,header=TRUE)
-upper_radius <- radius_values$upper_radius
-lower_radius <- radius_values$lower_radius
-step_value <- radius_values$step_value
 
 #check on decimal places if step_value non integer
 dec_places <- if ((step_value %% 1) != 0)
@@ -36,7 +33,6 @@ dec_places <- if ((step_value %% 1) != 0)
 	} else {
 	0}
 
-radius_unit <- radius_values$radius_unit
 
 if (radius_unit == 1)
 {unit_text <- "m"

### 2019-07-31 R/nodes_clust.R

@@ -28,7 +28,7 @@
 
 ## Sophie's trial to make functions here.
 
-percolate2 <- function(data, radius_values, limit, radius_unit) {
+percolate2 <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value) {
 path_source <- paste(getwd(),"/source_data",sep="")
 path_results <- paste(getwd(),"/working_data",sep="")
 
@@ -113,6 +113,11 @@ t2 <- proc.time() - ptm
 print('matrix copied')
 print(t2)
 
+## ab hier clustering_script
+
+mem_clust_by_r <- paste(path_results,"/","PlcIndex.csv",sep="")
+
+
 if (radius_unit == 1)
 {unit_text <- "m"
 } else if (radius_unit == 1000)
@@ -125,6 +130,8 @@ print(paste("Radii used for cluster analysis, ",unit_text,": upper ",upper_radiu
 
 # To compute and display computational time
 ptm <- proc.time()
+
+data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
 
 # The data table of nodes and internode distances is a Text file, with headers
 matrix_IDs_distance <- read.table(data_file,header=TRUE)

### 2019-07-31 paper.Rmd
nodes_clust und map_clust funktionieren. hänge bei cluster_freq

@@
 
-percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1)
+percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
 
 source("R/mapping_clusters.v4.12.R")
-mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape)
+mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape, map_name = "sNL-Karte")
 

### 2019-07-31 R/cluster_freq.R

@@ -1,0 +1,180 @@
+#' CLUSTER FREQENCY PLOTTING SCRIPT
+#' Simon Maddison, 10th May 2015
+#' Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs #' of clusters
+#' Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
+#' Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
+#' Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
+#' 	(currently max size). Changed outputs to multi-page pdf files
+#' Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
+#' Version 2.5: 23/4/16 -
+#'	Added in computations for clusters of single nodes
+#' 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
+#'	Table of max, mean and median exported
+#' Version 2.6: 26/4/16 -
+#' 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
+#' 	Exclude clusters with less than a certain threshold of nodes (parameter)
+#' 	Also exclude largest cluster from mean
+#' 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
+#' Version 2.7: 29/4/16 -
+#'	As per Elsa's published paper, plot max cluster size vs. radius as well
+#' 	Page format improved to generate pdf A4 format
+#' 	Bug fixed when adding clusters of size 1 (if null value)
+#' Version 2.8: 4/5/16 -
+#'	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
+#' Version 2.9: 6/5/16 -
+#'	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
+#' Version 2.10: 8/5/16 - source text file format changed to include map information
+#' Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
+#'	File is member_cluster_by_radius.csv
+#' Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
+#'	Make the image square or else it distorts the plot (note that this does not happen in pdf)
+#' 	Remove simple cluster rank plots, no longer useful
[…]

### 2019-07-31 R/map_clust.R

@@ -1,5 +1,5 @@
 
-mapClusters <- function(data, radius_values, limit, radius_unit, shape, upper_radius, lower_radius, step_value) {
+mapClusters <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value, shape, map_name) {
 
 percolate2(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value)
   
@@ -7,9 +7,10 @@ path_results <- paste(getwd(),"/working_data",sep="")
 path_maps <- paste(getwd(),"/maps",sep="")
 data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
 
+map_outline <- shape
 # Truncate shape file name to remove extension
-layer_name <- substr(shape,1,(nchar(shape)-4))
-print(map_name)
+#layer_name <- substr(shape,1,(nchar(shape)-4))
+#print(map_name)
 
 # Read in nodes and grid coordinates
 xy_data <- data
@@ -73,8 +74,9 @@ points(xy_data$Easting, xy_data$Northing, col='red', pch=20, cex=point_dia)
 number_of_sites <- paste("Number of sites: ",nrow(xy_data))
 mtext(number_of_sites)
 plot_title <- str_to_title(map_name,locale="")
-title(paste("Clusters of ", plot_title), sub=paste("Sources: ",source_file_name,"; ",shape_file_name))
+title(paste("Clusters of ", plot_title), sub=paste("Sources: ",data,"; ",map_name))
 dev.off()
+
 
 # Generates maps for each of percolation radii in range of radius values
 for(i in loop_count)
@@ -139,8 +141,8 @@ for(i in loop_count)
 		legend_size <- 0.8}
 	legend(legend_loc, inset= .01, title="Rank Cluster#",legend=ranked_clusters$cluster[1:number_colours], cex=legend_size,
 		fill=ranked_clusters$col[1:number_colours])
-
-	title(main=plot_title, sub=paste("Source File: ",source_file_name, "; percolation distance:",radius_name," ",unit_text))
+	
+	title(main=plot_title, sub=paste("; percolation distance:",radius_name," ",unit_text))
 
 	# Create data for output in csv file
 	# create ranking index for cluster numbers
@@ -166,6 +168,7 @@ file_name <- paste(path_results,"/","site_cluster_rank_by_radius.csv",sep="")
 # need to write this WITHOUT the row number
[…]

### 2019-07-31 R/nodes_clust.R

@@ -113,9 +113,15 @@ t2 <- proc.time() - ptm
 print('matrix copied')
 print(t2)
 
+
+
 ## ab hier clustering_script
 
-mem_clust_by_r <- paste(path_results,"/","PlcIndex.csv",sep="")
+
+
+mem_clust_by_r <- as.data.frame(data_unique$PlcIndex)
+names(mem_clust_by_r)[1] <- "PlcIndex"
+
 
 
 if (radius_unit == 1)

### 2019-07-31 paper.Rmd
skriptnamen

--- 2019-07-31 paper.Rmd
@@
 
-sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp"
-
 library(maptools)
@@
 library(igraph)
+sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp")
 
-source("R/create_nodes_list_d.v4.7.R")
-percolateNodes(data = data, radius_values = 10, limit = 500, radius_unit = 1)
+source("R/nodes_clust.R")
+percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
 
-source("R/clustering_script.v3.6.R")
-percolate()
-
-percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1)
-
-source("R/mapping_clusters.v4.12.R")
-mapClusters(data = data, shape = sNL_shape)
+source("R/map_clust.R")
+mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape, map_name = "sNL-Karte")
 

### 2019-08-01 paper.Rmd
alle scripte bis auf mapping in eine funktion

@@
 # create df from input data set
-data <- read.csv("source_data/BefundesNL-minimal.csv", sep = ",") #' crazy mistakes happen if this is wrong...
+data <- read.csv("raw_data/BefundesNL-minimal.csv", sep = ",") #' crazy mistakes happen if this is wrong...
 #' This file needs three columns: PlcIndex, Easting, Northing in this order.
@@
 source("R/cluster_frequency_script.v2.17.R")
-clusterFrequency()
+clusterFrequency(radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
 

### 2019-08-01 R/cluster_freq.R

@@ -73,39 +73,15 @@ if (radius_unit == 1)
 unit_text <- paste(radius_unit, "m", sep="")}
 
 
-# no idea where upper_cluster_min und _lower_cluster_minimum are comin from.
-
-#upper_cluster_minimum <- radius_values$upper_cluster_minimum
-#lower_cluster_minimum <- radius_values$lower_cluster_minimum
-
-# If one or both of these are Null, then set minimum to 1
-# assume percolation and not dbscan
-#percolation <- FALSE
-#if(is.null(upper_cluster_minimum)|is.null(lower_cluster_minimum))
-#{
-#	percolation <- TRUE
-#	upper_cluster_minimum <- 1
-#	lower_cluster_minimum <- 1
-#	print("Minimum cluster size set to 1, as one or both values read are Null; assume percolation and not dbscan")
-#}
-
 radius_values <- seq(upper_radius,lower_radius,by=-step_value)
 # Changes to accomodate non-integer radius values
 radii_count <- length(radius_values)
 loop_count <- seq(radii_count,1,by=-1)
 
-cluster_min_values <- seq(upper_cluster_minimum,lower_cluster_minimum,by=-1)
 
-for(cluster_min in cluster_min_values)
-	{
-	# Reads in file of data giving cluster ids indexed by radius, for each node
-	if(percolation== TRUE)
-	{
-		file_name <- paste(path_working,"/","member_cluster_by_radius.csv",sep="")
-	} else {
-		file_name <- paste(path_working,"/","member_cluster_by_radius_k",cluster_min,".csv",sep="")
-	}
-	mem_clust_by_r <- read.csv(file_name, header = TRUE)
+file_name <- paste(path_working,"/","member_cluster_by_radius.csv",sep="")
+
+mem_clust_by_r <- read.csv(file_name, header = TRUE)
 
 	# Create matrix of number of clusters and number of nodes (max, mean, median), for each radius
 	# Columns:  Radius, number of clusters, max cluster size, mean cluster size, median cluster size
@@ -138,21 +114,6 @@ for(cluster_min in cluster_min_values)
 		ranked_clusters$cluster <- as.numeric(as.character(ranked_clusters$cluster))
 		number_of_clusters <- nrow(ranked_clusters)
 
-		# add in clusters of size 1; compute number of these clusters
-		# TAKE THIS OUT
-		#add_row_total <- total_nodes - total_clustered_nodes
[…]

### 2019-08-01 R/nodes_clust_freq.R

@@ -1,0 +1,258 @@
+## Sophie's trial to make functions here.
+
+percolate_alles <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value) {
+path_source <- paste(getwd(),"/raw_data",sep="")
+path_working <- paste(getwd(),"/working_data",sep="")
+path_results <- paste(getwd(),"/analysis_results",sep="")
+
+
+ptm <- proc.time()
+#' For computation time
+
+#' List any entries with null values and write to file
+data_NA <- data[rowSums(is.na(data)) > 0,]
+print(paste("Entries in source file with one or more null values: "))
+data_NA
+file_name <- paste(path_working,"/","null_entries.txt",sep="")
+write.table(data_NA, file_name, row.names=FALSE)
+#' Remove rows with null values from data
+data <- na.omit(data)
+
+#' Remove points that are superimposed and keep only the first ID
+#' - This removes one of two sites that are very close to each other
+#' Determined on basis of x y coordinates
+#' Write list to file
+duplicate_xy <- data[duplicated(data[,2:3]),]
+data_unique <- data[!duplicated(data[,2:3]),]
+print(paste("Number of removed superimposed points: ",(nrow(data)-nrow(data_unique))))
+duplicate_xy
+file_name <- paste(path_working,"/","duplicate_entries.txt",sep="")
+write.table(duplicate_xy, file_name, row.names=FALSE)
+
+x_vec <- data_unique$Easting
+y_vec <- data_unique$Northing
+ID <- data_unique$PlcIndex
+
+#' Write file with list of PlcIndex used
+PlcIndex_list <- matrix(ID,ncol=1)
+file_name <- paste(path_working,"/","PlcIndex.csv",sep="")
+write.table(data_unique$PlcIndex, file_name, row.names=FALSE, col.names="PlcIndex")
+
+#' Number of points/nodes in file with no duplicates
+n <- length(ID)
+print(paste('number of points: ',n))
+
+#' Create matrix of internodal distances
+#' Columns: NodeId1, NodeId2, distance 1-2
+col_list <- cbind('ID1','ID2','d12')
+ni <- n-1
+nj <- n
+n_rows <- n*(n-1)/2
+nodes_list <- matrix(, nrow = n_rows, ncol = 3)
+colnames(nodes_list) <- col_list
+
+row <- 0
+i <- 1
+for (i in 1:ni)
+{
+	j1 <- i+1
+	for (j in j1:nj)
+	{
[…]

### 2019-08-01 R/map_clust.R
eine funktion für perlocation, eine für maps kreiert. erfolgreich den datentransfer eingebaut.

@@ -1,11 +1,19 @@
 
-mapClusters <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value, shape, map_name) {
+mapClusters <- function(data, shape, map_name) {
 
-percolate2(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value)
-  
-path_results <- paste(getwd(),"/working_data",sep="")
+  # changed path results and path_working to better seperate working data and analysis results data  
+path_results <- paste(getwd(),"/analysis_results",sep="")
+path_working <- paste(getwd(),"/working_data",sep="")
 path_maps <- paste(getwd(),"/maps",sep="")
-data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
+data_file <- paste(path_working,"/","nodes_list_d.txt",sep="")
+
+# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
+file_name <- paste(path_working,"/","working_data.csv",sep="")
+radius_values <- read.csv(file_name,header=TRUE, sep = ",")
+upper_radius <- radius_values$upper_radius
+lower_radius <- radius_values$lower_radius
+step_value <- radius_values$step_value
+radius_unit <- radius_values$radius_unit
 
 map_outline <- shape
 # Truncate shape file name to remove extension
@@ -24,7 +32,7 @@ coordinates(xy_data) <- c("Easting", "Northing")
 proj4string(xy_data) <- crs_projection
 
 # Read in data file with cluster id for each site and radius
-file_name <- paste(path_results,"/","member_cluster_by_radius.csv",sep="")
+file_name <- paste(path_working,"/","member_cluster_by_radius.csv",sep="")
 ranked_mem_clust_by_r <- read.csv(file_name, header=TRUE)
 
 
@@ -175,7 +183,7 @@ write.csv(ranked_mem_clust_by_r[order(ranked_mem_clust_by_r$PlcIndex),], file_na
 projection_string <- proj4string(map_outline)
 crs_projection <- CRS(projection_string)
 
-# name of output shapefile
+# name of output shapefile (renamed by Sophie)
 # Truncate source file name to remove extension
 output_shape_file <- paste(path_maps,"/analysis_results.shp",sep="")
 layer_name <- "percolation"

### 2019-08-01 R/nodes_clust_freq.R

@@ -5,6 +5,13 @@ path_source <- paste(getwd(),"/raw_data",sep="")
 path_working <- paste(getwd(),"/working_data",sep="")
 path_results <- paste(getwd(),"/analysis_results",sep="")
 
+# this will save the input values in a txt and as w_data in the environment to look up
+w_data_colnames <- c("radius_values", "limit", "radius_unit", "upper_radius", "lower_radius", "step_value")
+w_data_values <- c(radius_values, limit, radius_unit, upper_radius, lower_radius, step_value)
+w_data <<- rbind(w_data_colnames,w_data_values)
+
+file_name <- paste(path_working,"/","working_data.csv",sep="")
+write.table(w_data, file_name, row.names=FALSE, col.names = FALSE, sep = ",")
 
 ptm <- proc.time()
 #' For computation time
@@ -111,7 +118,7 @@ print(paste("Radii used for cluster analysis, ",unit_text,": upper ",upper_radiu
 # To compute and display computational time
 ptm <- proc.time()
 
-data_file <- paste(path_results,"/","nodes_list_d.txt",sep="")
+data_file <- paste(path_working,"/","nodes_list_d.txt",sep="")
 
 # The data table of nodes and internode distances is a Text file, with headers
 matrix_IDs_distance <- read.table(data_file,header=TRUE)

### 2019-08-01 paper.Rmd
eine funktion für perlocation, eine für maps kreiert. erfolgreich den datentransfer eingebaut.
prob im moment bei dem cluster plotten kram

@@
 
-source("R/nodes_clust.R")
-percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
+percolate_all(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
 
 source("R/map_clust.R")
-mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape, map_name = "sNL-Karte")
+mapClusters(data = data, shape = sNL_shape, map_name = "sNL-Karte")
 
@@
 source("R/cluster_frequency_script.v2.17.R")
-clusterFrequency(radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
+plot_clust_freq(source_file_name = "late neolithic features")
 

### 2019-08-01 R/cluster_freq.R

@@ -54,83 +54,70 @@
 #setwd("D:/Iron_Age_Hillforts/Percolation")
 
 # paths
-clusterFrequency <- function(upper_radius, lower_radius, step_value, radius_unit) {
-path_working <- paste(getwd(),"/working_data",sep="")
-path_results <- paste(getwd(),"/analysis_results",sep="")
+plot_clust_freq <- function(source_file_name) {
+ 
+  path_working <- paste(getwd(),"/working_data",sep="")
+  path_results <- paste(getwd(),"/analysis_results",sep="")
 
 
+file_name <- paste(path_results,"/","analysis_by_radius.csv",sep="")
+analysis_by_radius <- read.csv2(file_name,sep=",")
 
-# Read source file to establish number of nodes (entries in the file)
-# subtract 1 for header line
-total_nodes <- nrow(data) -1
-
-
+# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
+file_name <- paste(path_working,"/","working_data.csv",sep="")
+radius_values <- read.csv2(file_name,header=TRUE, sep = ",")
+upper_radius <- radius_values$upper_radius
+lower_radius <- radius_values$lower_radius
+step_value <- radius_values$step_value
+radius_unit <- radius_values$radius_unit
+	
 if (radius_unit == 1)
 {unit_text <- "m"
 } else if (radius_unit == 1000)
 {unit_text <- "km"
 } else {
-unit_text <- paste(radius_unit, "m", sep="")}
+  unit_text <- paste(radius_unit, "m", sep="")}	
+	
+	# output as png files
 
-
-radius_values <- seq(upper_radius,lower_radius,by=-step_value)
-# Changes to accomodate non-integer radius values
-radii_count <- length(radius_values)
-loop_count <- seq(radii_count,1,by=-1)
-
-
-file_name <- paste(path_working,"/","member_cluster_by_radius.csv",sep="")
-
-mem_clust_by_r <- read.csv(file_name, header = TRUE)
-
-	# Create matrix of number of clusters and number of nodes (max, mean, median), for each radius
-	# Columns:  Radius, number of clusters, max cluster size, mean cluster size, median cluster size
-	col_list <- cbind('radius','num_clust','max_clust_size','max_normalized','mean_clust_size','median_clust_size')
-	n_cols <- length(col_list)
-
-	n_rows <- length(radius_values)
[…]

### 2019-08-01 R/map_clust.R

@@ -5,6 +5,10 @@ mapClusters <- function(data, shape, map_name) {
 path_results <- paste(getwd(),"/analysis_results",sep="")
 path_working <- paste(getwd(),"/working_data",sep="")
 path_maps <- paste(getwd(),"/maps",sep="")
+
+dir.create(path_maps, showWarnings = FALSE)
+
+# read in nodes list
 data_file <- paste(path_working,"/","nodes_list_d.txt",sep="")
 
 # Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
@@ -32,7 +36,7 @@ coordinates(xy_data) <- c("Easting", "Northing")
 proj4string(xy_data) <- crs_projection
 
 # Read in data file with cluster id for each site and radius
-file_name <- paste(path_working,"/","member_cluster_by_radius.csv",sep="")
+file_name <- paste(path_results,"/","member_cluster_by_radius.csv",sep="")
 ranked_mem_clust_by_r <- read.csv(file_name, header=TRUE)
 
 
@@ -166,7 +170,7 @@ for(i in loop_count)
 	ranked_mem_clust_by_r[,ClstRad_col] <- NULL
 	dev.off()
 }
-dev.off()
+#dev.off()
 
 # convert NA's in ranked_mem_clust_by_r to zero
 ranked_mem_clust_by_r[is.na(ranked_mem_clust_by_r)] <- 0

### 2019-08-01 R/nodes_clust_freq.R

@@ -1,11 +1,22 @@
-## Sophie's trial to make functions here.
+##' created 2019-08-01 by Sophie Schmidt
+##' 
+##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and cluster_frequency_script.v2.17 
+##' by Simon Maddison
+##' it creates a file structure in which working data and analysis results are saved
+##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header
+##' input of radius values needed
+##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
+##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
+##' both output-folders will be used by following functions
 
-percolate_alles <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value) {
-path_source <- paste(getwd(),"/raw_data",sep="")
+percolate_all <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value) {
 path_working <- paste(getwd(),"/working_data",sep="")
 path_results <- paste(getwd(),"/analysis_results",sep="")
 
-# this will save the input values in a txt and as w_data in the environment to look up
+dir.create(path_working, showWarnings = FALSE)
+dir.create(path_results, showWarnings = FALSE)
+
+# this will save the input values in a csv and as w_data in the environment to look up
 w_data_colnames <- c("radius_values", "limit", "radius_unit", "upper_radius", "lower_radius", "step_value")
 w_data_values <- c(radius_values, limit, radius_unit, upper_radius, lower_radius, step_value)
 w_data <<- rbind(w_data_colnames,w_data_values)
@@ -207,7 +218,7 @@ radii_count <- length(radius_values)
 loop_count <- seq(radii_count,1,by=-1)
 
 
-file_name <- paste(path_working,"/","member_cluster_by_radius.csv",sep="")
+file_name <- paste(path_results,"/","member_cluster_by_radius.csv",sep="")
 
 mem_clust_by_r <- read.csv(file_name, header = TRUE)
 

### 2019-08-02 R/percopackage.R
started cleaning up old stuff and checking and building the package

@@ -1,0 +1,14 @@
+
+#' \code{percopackage} package
+#'
+#' percolation analysis in R
+#'
+#' copied from Jenny Brian
+#' \href{https://github.com/SCSchmidt/percopackage/README.html}{GitHub}
+#'
+#' @docType package
+#' @name percopackage
+
+
+## quiets concerns of R CMD check re: the .'s that appear in pipelines
+if(getRversion() >= "2.15.1")  utils::globalVariables(c("."))

### 2019-08-02 R/cluster_freq.R
down to only one warning when checking. mostly roxygen documentation added in scripts

@@ -1,65 +1,24 @@
-#' CLUSTER FREQENCY PLOTTING SCRIPT
-#' Simon Maddison, 10th May 2015
-#' Version 2.1: 2/10/15 - Tidied up, paths and added plot of radius vs #' of clusters
-#' Version 2.2: 31/1/16 -  Labels added to the second plot, requires the textxy function in calibrate package
-#' Note odd plot of radius 1 if included, due to clustering idiosyncracy that does not include clusters of 1.
-#' Version 2.3: 30/3/16 - Extended to include plots of average and median cluster sizes on the same plot
-#' 	(currently max size). Changed outputs to multi-page pdf files
-#' Version 2.4: 20/4/16 - Plot to log log added for median. Defined range plot removed
-#' Version 2.5: 23/4/16 -
-#'	Added in computations for clusters of single nodes
-#' 	Totals of nodes and number of clusters take account of single nodes as clusters of 1
-#'	Table of max, mean and median exported
-#' Version 2.6: 26/4/16 -
-#' 	As per Elsa's paper, plot 'S_mean' cluster size, vs radius,
-#' 	Exclude clusters with less than a certain threshold of nodes (parameter)
-#' 	Also exclude largest cluster from mean
-#' 	Thresholds for upper and lower calculations of S_mean read in from radius_values text file
-#' Version 2.7: 29/4/16 -
-#'	As per Elsa's published paper, plot max cluster size vs. radius as well
-#' 	Page format improved to generate pdf A4 format
-#' 	Bug fixed when adding clusters of size 1 (if null value)
-#' Version 2.8: 4/5/16 -
-#'	As per Elsa's published paper, max also plotted as normalized relative to total number of nodes
-#' Version 2.9: 6/5/16 -
-#'	Problem with S_mean if number of clusters becomes zero, resolved, and also corrected computation
-#' Version 2.10: 8/5/16 - source text file format changed to include map information
-#' Version 2.11: 18/5/16 - updated to read cluster data from combined file that is now generated by other programs
-#'	File is member_cluster_by_radius.csv
-#' Version 2.12: 30/7/16 - data output as png file, easier to incorporate in word doc
-#'	Make the image square or else it distorts the plot (note that this does not happen in pdf)
-#' 	Remove simple cluster rank plots, no longer useful
-#' Version 2.13: 7/11/17	- amended working directory path for new pc
-#' Version 2.14: 17/11/17 - amended to allow for multiple file versions based on additional 'k' factor
[…]

### 2019-08-02 R/map_clust.R

@@ -1,4 +1,15 @@
-
+##' created 2019-08-01 by Sophie Schmidt
+##' 
+##' This is a function built based on the script mapping_clusters.v4.12
+##' by Simon Maddison
+##' it creates a folder maps, where output is saved as png
+#
+#' @param data needs input of dataframe
+#' @param shape needs input of SpatialPolygonDataFrame from 'sp'
+#' @param map_name needs string for how the maps shall be named
+#' @return as many maps as png as step_values have been calculated
+#' @export
+#'
 mapClusters <- function(data, shape, map_name) {
 
   # changed path results and path_working to better seperate working data and analysis results data  

### 2019-08-02 R/nodes_clust_freq.R

@@ -8,8 +8,16 @@
 ##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
 ##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
 ##' both output-folders will be used by following functions
+#' @param data needs input of dataframe
+#' @param limit needs input of integer: is the value above which distances will not be calculated between sites
+#' @param radius_unit is either 1 for meter or 1000 for km for all input numbers
+#' @param upper_radius needs input of integer, is the upper value of the radius range to be used
+#' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
+#' @param step_value integer or numeric, is the step value to be used between these two values
+#' @return 3 plots of radius to maximum cluster size, radius to mean cluster size and radius to normalized max. cluster size
+#' @export
 
-percolate_all <- function(data, radius_values, limit, radius_unit, upper_radius, lower_radius, step_value) {
+percolate_all <- function(data, limit, radius_unit, upper_radius, lower_radius, step_value) {
 path_working <- paste(getwd(),"/working_data",sep="")
 path_results <- paste(getwd(),"/analysis_results",sep="")
 
@@ -17,8 +25,8 @@ dir.create(path_working, showWarnings = FALSE)
 dir.create(path_results, showWarnings = FALSE)
 
 # this will save the input values in a csv and as w_data in the environment to look up
-w_data_colnames <- c("radius_values", "limit", "radius_unit", "upper_radius", "lower_radius", "step_value")
-w_data_values <- c(radius_values, limit, radius_unit, upper_radius, lower_radius, step_value)
+w_data_colnames <- c("limit", "radius_unit", "upper_radius", "lower_radius", "step_value")
+w_data_values <- c(limit, radius_unit, upper_radius, lower_radius, step_value)
 w_data <<- rbind(w_data_colnames,w_data_values)
 
 file_name <- paste(path_working,"/","working_data.csv",sep="")

### 2019-08-02 R/mapClusters.R
runs. but, roxygen somehow doesn't do @export percolate. added manually to namespace. *shrug*

@@ -1,0 +1,218 @@
+##' created 2019-08-01 by Sophie Schmidt
+##' 
+##' This is a function built based on the script mapping_clusters.v4.12
+##' by Simon Maddison
+##' it creates a folder maps, where output is saved as png
+#' @author Simon Maddison
+#' @author Sophie C. Schmidt
+#' @import sp
+#' @import stats
+#' @import igraph
+#' @import maptools
+#' @import stringr
+#' @import grDevices
+#' @import graphics
+#' @import rgdal
+#' @import utils
+#' @param data needs input of dataframe
+#' @param shape needs input of SpatialPolygonDataFrame from 'sp' for background map (same ESPG!)
+#' @param map_name needs string for how the maps shall be named
+#' @param source_file_name string for the name of data set
+#' @return as many maps as png as step_values have been calculated
+#' 
+#' @export mapClusters
+#'
+mapClusters <- function(data, shape, map_name, source_file_name) {
+
+  # changed path results and path_working to better seperate working data and analysis results data  
+path_results <- paste(getwd(),"/analysis_results",sep="")
+path_working <- paste(getwd(),"/working_data",sep="")
+path_maps <- paste(getwd(),"/maps",sep="")
+
+dir.create(path_maps, showWarnings = FALSE)
+
+# read in nodes list
+data_file <- paste(path_working,"/","nodes_list_d.txt",sep="")
+
+# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
+file_name <- paste(path_working,"/","working_data.csv",sep="")
+radius_values <- read.csv(file_name,header=TRUE, sep = ",")
+upper_radius <- radius_values$upper_radius
+lower_radius <- radius_values$lower_radius
+step_value <- radius_values$step_value
+radius_unit <- radius_values$radius_unit
+
+map_outline <- shape
+# Truncate shape file name to remove extension
+#layer_name <- substr(shape,1,(nchar(shape)-4))
+#print(map_name)
+
+# Read in nodes and grid coordinates
+xy_data <- data
+
+# Convert data to SpatialPointsDataFrame, using project4string from selected map file
+# get projection string for current map
+projection_string <- proj4string(map_outline)
+crs_projection <- CRS(projection_string)
[…]

### 2019-08-02 R/percolate.R

@@ -1,0 +1,293 @@
+##' created 2019-08-01 by Sophie Schmidt
+##' 
+##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and cluster_frequency_script.v2.17 
+##' by Simon Maddison
+##' it creates a file structure in which working data and analysis results are saved
+##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header
+##' input of radius values needed
+##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
+##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
+##' both output-folders will be used by following functions
+#' @author Simon Maddison
+#' @author Sophie C. Schmidt
+#' 
+#' @import stats
+#' @import Hmisc
+#' @import utils
+
+#' @param data needs input of dataframe
+#' @param limit needs input of integer: is the value above which distances will not be calculated between sites
+#' @param radius_unit is either 1 for meter or 1000 for km for all input numbers
+#' @param upper_radius needs input of integer, is the upper value of the radius range to be used
+#' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
+#' @param step_value integer or numeric, is the step value to be used between these two values
+#' @return percolate 3 plots of radius to maximum cluster size, radius to mean cluster size and radius to normalized max. cluster size
+#' 
+#' @export percolate
+#'
+percolate <- function(data, limit, radius_unit, upper_radius, lower_radius, step_value) {
+  
+path_working <- paste(getwd(),"/working_data",sep="")
+path_results <- paste(getwd(),"/analysis_results",sep="")
+
+dir.create(path_working, showWarnings = FALSE)
+dir.create(path_results, showWarnings = FALSE)
+
+# this will save the input values in a csv and as w_data in the environment to look up
+w_data_colnames <- c("limit", "radius_unit", "upper_radius", "lower_radius", "step_value")
+w_data_values <- c(limit, radius_unit, upper_radius, lower_radius, step_value)
[…]

### 2019-08-02 R/plotClustFreq.R

@@ -1,0 +1,93 @@
+
+#' based on CLUSTER FREQENCY PLOTTING SCRIPTv2.17 by Simon Maddison, 10th May 2015
+#' This script extracts cluster frequency data and plots it for a range of percolation radii
+#' The data is in the analysis_results-directory in text files created by the nodes_clust_freq-function;
+#' 	each file is a list of Place indices, with the identity of each cluster
+#' 	which it is a member of.
+#' 	radius-values have been stored in the working_data-directory.
+#' 	output will be put into /analysis_results
+#' @author Simon Maddison
+#' @author Sophie C. Schmidt
+#' 
+#' @import stats
+#' @import calibrate
+#' @import Hmisc
+#' @import grDevices
+#' @import graphics
+#' @import utils
+#' @param source_file_name needs input of source file name for plotting
+#' @return plotClustFreq 3 plots of radius to maximum cluster size, radius to mean cluster size and radius to normalized max. cluster size
+#' 
+#' @export plotClustFreq
+#'
+
+
+
+# paths definition
+plotClustFreq <- function(source_file_name) {
+ 
+  path_working <- paste(getwd(),"/working_data",sep="")
+  path_results <- paste(getwd(),"/analysis_results",sep="")
+
+# load data generated by nodes_clust_freq-function
+file_name <- paste(path_results,"/","analysis_by_radius.csv",sep="")
+analysis_by_radius <- read.csv2(file_name,sep=",")
+
+# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
+file_name <- paste(path_working,"/","working_data.csv",sep="")
+radius_values <- read.csv2(file_name,header=TRUE, sep = ",")
+upper_radius <- radius_values$upper_radius
+lower_radius <- radius_values$lower_radius
+step_value <- radius_values$step_value
+radius_unit <- radius_values$radius_unit
+	
+if (radius_unit == 1)
+{unit_text <- "m"
+} else if (radius_unit == 1000)
+{unit_text <- "km"
+} else {
+  unit_text <- paste(radius_unit, "m", sep="")}	
+	
+	# output as png files
+
+#removed if-condition  about percolation
+	  output_file <- paste(path_results,"/cluster_plots_%02d.png",sep="")
+	  plot_suffix <- ""
+	
[…]

### 2019-11-13 R/percolate.R
added information on Elsa Arcaute

@@ -1,15 +1,19 @@
 ##' created 2019-08-01 by Sophie Schmidt
 ##' 
 ##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and cluster_frequency_script.v2.17 
-##' by Simon Maddison
-##' it creates a file structure in which working data and analysis results are saved
+##' by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under :  
+##' E. Arcaute, C. Molinero, E. Hatna, R. Murcio, C. Vargas-Ruiz, A.P. Masucci and M. Batty. Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. doi:10.1098/rsos.150691, 2016. 
+##' 
+##' It creates a file structure in which working data and analysis results are saved
 ##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header
 ##' input of radius values needed
 ##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
 ##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
 ##' both output-folders will be used by following functions
+
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt
+#' @author Elsa Arcaute
 #' 
 #' @import stats
 #' @import Hmisc

### 2019-11-13 R/percolate.R
added parameter to enable using a self-calculated distance matrix

@@ -5,7 +5,7 @@
 ##' E. Arcaute, C. Molinero, E. Hatna, R. Murcio, C. Vargas-Ruiz, A.P. Masucci and M. Batty. Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. doi:10.1098/rsos.150691, 2016. 
 ##' 
 ##' It creates a file structure in which working data and analysis results are saved
-##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header
+##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header OR a distance table with the headers 'ID1','ID2','d12'!
 ##' input of radius values needed
 ##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
 ##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
@@ -19,16 +19,16 @@
 #' @import Hmisc
 #' @import utils
 
-#' @param data needs input of dataframe
+#' @param data needs input of dataframe as specified above
+#' @param type specifies whether dataframe is points or a distance matrix. Default is "points". All other input will be treated as distance matrix
 #' @param limit needs input of integer: is the value above which distances will not be calculated between sites
 #' @param radius_unit is either 1 for meter or 1000 for km for all input numbers
 #' @param upper_radius needs input of integer, is the upper value of the radius range to be used
 #' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
 #' @param step_value integer or numeric, is the step value to be used between these two values
-#' @return 
-#' @export 
-#'
-percolate <- function(data, limit, radius_unit, upper_radius, lower_radius, step_value) {
+#' @return the function returns analysis_by_radius.csv and member_cluster_by_radius.csv
+#' @export
+percolate <- function(data, type = "points", limit, radius_unit, upper_radius, lower_radius, step_value) {
 
 # create directories
   # file.path creates paths according to platform used on user's computer
@@ -51,21 +51,25 @@ file_name <-paste(file.path(path_working,"data.csv"))
 write.table(data, file_name, row.names=FALSE, col.names = TRUE, sep = ",")
 
 ptm <- proc.time()
-#' For computation time
[…]

### 2020-01-16 R/cluster_freq.R
clean up

@@ -1,82 +1,0 @@
-#' based on CLUSTER FREQENCY PLOTTING SCRIPTv2.17 by Simon Maddison, 10th May 2015
-#' This script extracts cluster frequency data and plots it for a range of percolation radii
-#' The data is in the analysis_results-directory in text files created by the nodes_clust_freq-function;
-#' 	each file is a list of Place indices, with the identity of each cluster
-#' 	which it is a member of.
-#' 	radius-values have been stored in the working_data-directory.
-#' 	output will be put into /analysis_results
-#' @param source_file_name needs input of source file name for plotting
-#' @return 3 plots of radius to maximum cluster size, radius to mean cluster size and radius to normalized max. cluster size
-#' @export
-#'
-
-
-
-# paths definition
-plot_clust_freq <- function(source_file_name) {
- 
-  path_working <- paste(getwd(),"/working_data",sep="")
-  path_results <- paste(getwd(),"/analysis_results",sep="")
-
-# load data generated by nodes_clust_freq-function
-file_name <- paste(path_results,"/","analysis_by_radius.csv",sep="")
-analysis_by_radius <- read.csv2(file_name,sep=",")
-
-# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
-file_name <- paste(path_working,"/","working_data.csv",sep="")
-radius_values <- read.csv2(file_name,header=TRUE, sep = ",")
-upper_radius <- radius_values$upper_radius
-lower_radius <- radius_values$lower_radius
-step_value <- radius_values$step_value
-radius_unit <- radius_values$radius_unit
-	
-if (radius_unit == 1)
-{unit_text <- "m"
-} else if (radius_unit == 1000)
-{unit_text <- "km"
-} else {
-  unit_text <- paste(radius_unit, "m", sep="")}	
-	
-	# output as png files
-
-#removed if-condition  about percolation
-	  output_file <- paste(path_results,"/cluster_plots_%02d.png",sep="")
-	  plot_suffix <- ""
-	
-	png(file=output_file, units="cm", width=21, height=21, res=300)
-	
-	# Plot radius vs max_clust_size
-	plot(analysis_by_radius$radius,analysis_by_radius$max_clust_size,
-	     main=paste("Max cluster size vs radius ",plot_suffix),
-	     sub=paste("Source File: ",source_file_name),
[…]

### 2020-01-16 R/mapClusters.v.2.1.R

@@ -1,15 +1,62 @@
+##' created 2019-08-01 by Sophie Schmidt
+##' 
+##' This is a function built based on the script mapping_clusters.v4.12
+##' by Simon Maddison
+##' it creates a folder maps, where output is saved as png
+#' @author Simon Maddison
+#' @author Sophie C. Schmidt
+#' @import sp
+#' @import stats
+#' @import igraph
+#' @import maptools
+#' @import stringr
+#' @import grDevices
+#' @import graphics
+#' @import rgdal
+#' @import raster
+#' @import utils
+#' @param shape needs input of SpatialPolygonDataFrame from 'sp' for background map (same ESPG!)
+#' @param map_name needs string for how the maps shall be named
+#' @param source_file_name string for the name of data set
+#' @param dpi dots per inch for the images. set to 300 as standard
+#' @return as many maps as png as step_values have been calculated
+#' 
+#' @export mapClusters
+#'
+mapClusters <- function(shape, map_name, source_file_name, dpi = 300) {
 
-mapClusters <- function(data, shape) {
+  # changed path results and path_working to better seperate working data and analysis results data  
 
-path_results <- paste(getwd(),"/working_data",sep="")
-path_maps <- paste(getwd(),"/maps",sep="")
+  # file.path creates paths according to platform used on user's computer
+path_working <- file.path(getwd(), "working_data")
+path_results <- file.path(getwd(), "analysis_results")
 
+# create maps directory
+path_maps <- file.path(getwd(), "maps")
+dir.create(path_maps, showWarnings = FALSE)
+
+# read in nodes list
+data_file <- paste(file.path(path_working,"nodes_list_d.txt"))
+
+# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
+file_name <- paste(file.path(path_working,"working_data.csv"))
+radius_values <- read.csv(file_name,header=TRUE, sep = ",")
+upper_radius <- radius_values$upper_radius
+lower_radius <- radius_values$lower_radius
+step_value <- radius_values$step_value
+radius_unit <- radius_values$radius_unit
+
+map_outline <- shape
 # Truncate shape file name to remove extension
-layer_name <- substr(shape,1,(nchar(shape)-4))
[…]

### 2020-01-16 R/map_clust.R

@@ -1,210 +1,0 @@
-##' created 2019-08-01 by Sophie Schmidt
-##' 
-##' This is a function built based on the script mapping_clusters.v4.12
-##' by Simon Maddison
-##' it creates a folder maps, where output is saved as png
-#
-#' @param data needs input of dataframe
-#' @param shape needs input of SpatialPolygonDataFrame from 'sp'
-#' @param map_name needs string for how the maps shall be named
-#' @return as many maps as png as step_values have been calculated
-#' @export
-#'
-mapClusters <- function(data, shape, map_name) {
-
-  # changed path results and path_working to better seperate working data and analysis results data  
-path_results <- paste(getwd(),"/analysis_results",sep="")
-path_working <- paste(getwd(),"/working_data",sep="")
-path_maps <- paste(getwd(),"/maps",sep="")
-
-dir.create(path_maps, showWarnings = FALSE)
-
-# read in nodes list
-data_file <- paste(path_working,"/","nodes_list_d.txt",sep="")
-
-# Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
-file_name <- paste(path_working,"/","working_data.csv",sep="")
-radius_values <- read.csv(file_name,header=TRUE, sep = ",")
-upper_radius <- radius_values$upper_radius
-lower_radius <- radius_values$lower_radius
-step_value <- radius_values$step_value
-radius_unit <- radius_values$radius_unit
-
-map_outline <- shape
-# Truncate shape file name to remove extension
-#layer_name <- substr(shape,1,(nchar(shape)-4))
-#print(map_name)
-
-# Read in nodes and grid coordinates
-xy_data <- data
-
-# Convert data to SpatialPointsDataFrame, using project4string from selected map file
-# get projection string for current map
-projection_string <- proj4string(map_outline)
-crs_projection <- CRS(projection_string)
-# turn data into SpatialPointsDataFrame
-coordinates(xy_data) <- c("Easting", "Northing")
-proj4string(xy_data) <- crs_projection
-
-# Read in data file with cluster id for each site and radius
-file_name <- paste(path_results,"/","member_cluster_by_radius.csv",sep="")
-ranked_mem_clust_by_r <- read.csv(file_name, header=TRUE)
-
-
[…]

### 2020-01-16 R/nodes_clust.R

@@ -1,206 +1,0 @@
-#' CREATE NODES LIST SCRIPT
-#' Original code from Elsa Arcaute, CASA, UCL 28.2.15; extensively modified by Simon Maddison.
-#' Cite as:	arXiv:1504.08318 [physics.soc-ph]
-#' This is now version 3, incorporating corrections, performance and style improvements 10/5/15
-#' This code creates the file nodes_list_d.txt containing the list for all the distances between pairs,
-#' that is to say a partial matrix of distances between nodes.
-#' Distances are computed for each node with each successive node, working through the list.
-#' For ca. 3500 nodes this is no longer practicable, as computation become too long and files too big.
-#' This uses an approach that creates file with only distances below a limit, e.g. 100km.
-#' This will then not be a fully interconnected network;
-#' 	need to ensure that this does not adversely affect clustering computation.
-#' Note original used the bigmemory library but this is not available for windows, so all refs removed.
-#' Version 3.1: 29/3/16 - add check for null values, display and strip out, also update on duplicate coordinates.
-#' 	This data written out to text files.
-#' Version 4.1: 4/4/2016 -
-#' NOTE: problems with a matrix with #'REF entries in .csv -
-#'	No check for this, and caused problems with matrix manipulation
-#' Removed conversions to and from matrix data format for data, from original source. Not necessary
-#' Version 4.2: 10/4/16 - Minor error in duplicate computation corrected. Old ref to matrix_xy; note also
-#'     that input data now has additional Lat Long fields added, which are not used here
-#' Version 4.3: 6/5/16 - Change index name in source file to bring within character limit in ArcGIS -> PlcIndex
-#' Version 4.4: 8/5/16 - Change of source text file format to include map data
-#' Version 4.5: 18/5/16 - Change to include output PlcIndex as csv, cleaned up list with only those processed
-#' Version 4.6: 07/11/17 - Change working directory for updated machine
-#' Version 4.7: 03/12/18 - add in unit parameter to select km or m, in "radius_values.txt"
[…]

### 2020-01-16 R/nodes_clust_freq.R

@@ -1,284 +1,0 @@
-##' created 2019-08-01 by Sophie Schmidt
-##' 
-##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and cluster_frequency_script.v2.17 
-##' by Simon Maddison
-##' it creates a file structure in which working data and analysis results are saved
-##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header
-##' input of radius values needed
-##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
-##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
-##' both output-folders will be used by following functions
-#' @param data needs input of dataframe
-#' @param limit needs input of integer: is the value above which distances will not be calculated between sites
-#' @param radius_unit is either 1 for meter or 1000 for km for all input numbers
-#' @param upper_radius needs input of integer, is the upper value of the radius range to be used
-#' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
-#' @param step_value integer or numeric, is the step value to be used between these two values
-#' @return 3 plots of radius to maximum cluster size, radius to mean cluster size and radius to normalized max. cluster size
-#' @export
-
-percolate_all <- function(data, limit, radius_unit, upper_radius, lower_radius, step_value) {
-path_working <- paste(getwd(),"/working_data",sep="")
-path_results <- paste(getwd(),"/analysis_results",sep="")
-
-dir.create(path_working, showWarnings = FALSE)
-dir.create(path_results, showWarnings = FALSE)
-
-# this will save the input values in a csv and as w_data in the environment to look up
-w_data_colnames <- c("limit", "radius_unit", "upper_radius", "lower_radius", "step_value")
-w_data_values <- c(limit, radius_unit, upper_radius, lower_radius, step_value)
-w_data <<- rbind(w_data_colnames,w_data_values)
-
-file_name <- paste(path_working,"/","working_data.csv",sep="")
[…]

### 2020-01-16 R/percopackage.R

@@ -1,14 +1,0 @@
-
-#' \code{percopackage} package
-#'
-#' percolation analysis in R
-#'
-#' copied from Jenny Brian
-#' \href{https://github.com/SCSchmidt/percopackage/README.html}{GitHub}
-#'
-#' @docType package
-#' @name percopackage
-
-
-## quiets concerns of R CMD check re: the .'s that appear in pipelines
-if(getRversion() >= "2.15.1")  utils::globalVariables(c("."))

### 2020-01-16 R/percolate.v2.1.R
updated for a better description of distance table

@@ -23,7 +23,7 @@
 #' @import igraph
 
 #' @param data needs input of dataframe as specified above
-#' @param distance_table specifies whether dataframe is points or a distance matrix. Default is NULL, therfore points. All other input will be treated as distance matrix
+#' @param distance_table to give a distance matrix instead of calculating one. Default is NULL, and Euklidean distance will be used and calculated from the given data.
 #' @param limit needs input of integer: is the value above which distances will not be calculated between sites
 #' @param radius_unit is either 1 for meter or 1000 for km for all input numbers
 #' @param upper_radius needs input of integer, is the upper value of the radius range to be used

### 2020-01-17 R/plotClustFreq.v2.1.R
Simon solved problem with factors instead of numerics.

@@ -1,6 +1,4 @@
 
-#' plotting cluster frequency
-#' 
 #' based on CLUSTER FREQENCY PLOTTING SCRIPTv2.17 by Simon Maddison, 10th May 2015
 #' This script extracts cluster frequency data and plots it for a range of percolation radii
 #' The data is in the analysis_results-directory in text files created by the nodes_clust_freq-function;
@@ -73,26 +71,30 @@ if (radius_unit == 1)
 
   output_file <- paste(file.path(path_results,"radius_to_max_cluster_size.png"))
 	png(file=output_file, units="cm", width=21, height=21, res=300)
-	
-	plot(analysis_by_radius$radius,analysis_by_radius$max_clust_size,
+	radius_vals <- as.numeric(as.character(analysis_by_radius$radius))
+	plot(radius_vals,analysis_by_radius$max_clust_size,
 	     main=paste("Max cluster size vs radius "),
 	     sub=paste("Source File: ",source_file_name),
 	     xlab=paste("radius ", unit_text),
 	     ylab="max cluster size", type="b")
+#	textxy(analysis_by_radius$radius,analysis_by_radius$max_clust_size,analysis_by_radius$radius, col="red", cex=.8)
+	# at the moment some weird mistake here: Error in if (sum(posXposY) > 0) text(X[posXposY], Y[posXposY], labs[posXposY],  : 
+#	missing value where TRUE/FALSE needed
+	# there shouldn't be any values missing.
 	dev.off()	
-
-# Plot radius vs mean_clust_size
+	# Plot radius vs mean_clust_size
 	
 	output_file <- paste(file.path(path_results,"radius_to_mean_cluster_size.png"))
 	png(file=output_file, units="cm", width=21, height=21, res=300)
 	#SM: convert factor to numeric
 	mean_clust_size_values <- as.numeric(as.character(analysis_by_radius$mean_clust_size))
-	plot(analysis_by_radius$radius,mean_clust_size_values ,
+	plot(radius_vals,mean_clust_size_values ,
 	     main=paste("Mean cluster size vs radius "),
 	     sub=paste("Source File: ",source_file_name),
 	     xlab=paste("radius ", unit_text),
 	     ylab="mean cluster size", type="b")
-
+#	textxy(analysis_by_radius$radius,analysis_by_radius$mean_clust_size,analysis_by_radius$radius, col="red", cex=.8)
+	
 	dev.off()
[…]

### 2020-01-17 R/percolate.v2.1.R
finally understood roxygen headers

@@ -1,4 +1,4 @@
-##' created 2019-08-01 by Sophie Schmidt
+##' Percolation
 ##' 
 ##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and cluster_frequency_script.v2.17 
 ##' by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under :  

### 2020-01-20 R/mapClusters.v.2.1.R
Simons improvements

@@ -17,7 +17,7 @@
 #' @import utils
 #' @param shape needs input of SpatialPolygonDataFrame from 'sp' for background map (same ESPG!)
 #' @param map_name needs string for how the maps shall be named
-#' @param source_file_name string for the name of data set
+#' @param source_file_name string for the name of data set used, to include on maps
 #' @param dpi dots per inch for the images. set to 300 as standard
 #' @return as many maps as png as step_values have been calculated
 #' 
@@ -25,7 +25,7 @@
 #'
 mapClusters <- function(shape, map_name, source_file_name, dpi = 300) {
 
-  # changed path results and path_working to better seperate working data and analysis results data  
+  # set up path results and path_working to better seperate working data and analysis results data  
 
   # file.path creates paths according to platform used on user's computer
 path_working <- file.path(getwd(), "working_data")
@@ -47,9 +47,6 @@ step_value <- radius_values$step_value
 radius_unit <- radius_values$radius_unit
 
 map_outline <- shape
-# Truncate shape file name to remove extension
-#layer_name <- substr(shape,1,(nchar(shape)-4))
-#print(map_name)
 
 # Read in nodes and grid coordinates
 data_filename <- paste(file.path(path_working,"data.csv"))
@@ -90,24 +87,23 @@ radius_values <- seq(upper_radius,lower_radius,by=-step_value)
 radii_count <- length(radius_values)
 loop_count <- seq(radii_count,1,by=-1)
 
-# Define colours for clusters, top 15 and then gray for the rest
+# Define colours for clusters; top 15 and then gray for the rest
 top15_colours <- colors()[c(553,29,258,654,91,115,456,122,48,8,149,86,102,40,12)]
 the_rest_colour <- "#AEAEAE"
 
-# plot all sites as pdf
+# this code can be used to plot all sites as pdf as an alternative
 # Maps plotted on multipage pdf
 #file_map_pdf <- paste(path_maps,"/","percolation_plots_",map_name,".pdf",sep="")
 #pdf(file=file_map_pdf, paper="a4", width=21/2.54, height=29.7/2.54)
 
-# Plot as png, earlier issues with png now resolved
-
+# Plot as png, default. png is deemed a more practical solution
+# page format default is A4
[…]

### 2020-01-20 R/percolate.v2.1.R

@@ -5,10 +5,10 @@
 ##' E. Arcaute, C. Molinero, E. Hatna, R. Murcio, C. Vargas-Ruiz, A.P. Masucci and M. Batty. Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. doi:10.1098/rsos.150691, 2016. 
 ##' 
 ##' It creates a file structure in which working data and analysis results are saved
-##' input data needed, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header. A distance table with the headers 'ID1','ID2','d12' SM: may be used if a computation of the euclidean distance between points is not required. 
+##' input data required, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header. A distance table with the headers 'ID1','ID2','d12' SM: may be used if a computation of the euclidean distance between points is not required. 
 ##' input of radius values needed 
-#SM: NOTE that if the distance table option is used the Spatial dataframe MUST ALSO BE PROVIDED for the mapping!
-#SM: both file types need to be comma delimited!
+##' NOTE that if the distance table option is used the Spatial dataframe MUST ALSO BE PROVIDED for the mapping!
+##' both file types need to be comma delimited!
 ##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
 ##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
 ##' both output-folders will be used by following functions
@@ -23,13 +23,13 @@
 #' @import igraph
 
 #' @param data needs input of dataframe as specified above
-#' @param distance_table to give a distance matrix instead of calculating one. Default is NULL, and Euklidean distance will be used and calculated from the given data.
+#' @param distance_table to give a distance matrix instead of calculating one. Default is NULL, and Euclidean distance will be used and calculated from the given data.
 #' @param limit needs input of integer: is the value above which distances will not be calculated between sites
 #' @param radius_unit is either 1 for meter or 1000 for km for all input numbers
 #' @param upper_radius needs input of integer, is the upper value of the radius range to be used
 #' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
[…]

### 2020-01-20 R/plotClustFreq.v2.1.R

@@ -21,8 +21,6 @@
 #' 
 #' @export plotClustFreq
 #'
-## SM: problem with the mean and normalized values being stored as factors. Resolved.
-
 
 
 # paths definition
@@ -35,7 +33,7 @@ plotClustFreq <- function(source_file_name = source_file_name) {
 file_name <- paste(file.path(path_results,"analysis_by_radius.csv"))
 analysis_by_radius <- read.csv2(file_name,sep=",")
 
-# load source_file_name if put out by mapClusters, if it was saved there. otherwise use input
+# load source_file_name from mapClusters, if it was saved there. Otherwise use input
 
 
 if ( file.exists(file.path(path_working, "source_file_name_out.csv"))) {
@@ -64,9 +62,7 @@ if (radius_unit == 1)
 } else {
   unit_text <- paste(radius_unit, "m", sep="")}	
 	
-	# output as png files
-
-#removed if-condition  about percolation
+# output as png files
 
 # Plot radius vs max_clust_size
 
@@ -78,38 +74,35 @@ if (radius_unit == 1)
 	     sub=paste("Source File: ",source_file_name),
 	     xlab=paste("radius ", unit_text),
 	     ylab="max cluster size", type="b")
-#	textxy(analysis_by_radius$radius,analysis_by_radius$max_clust_size,analysis_by_radius$radius, col="red", cex=.8)
-	# at the moment some weird mistake here: Error in if (sum(posXposY) > 0) text(X[posXposY], Y[posXposY], labs[posXposY],  : 
-#	missing value where TRUE/FALSE needed
-	# there shouldn't be any values missing.
+
 	dev.off()	
+	
 	# Plot radius vs mean_clust_size
 	
 	output_file <- paste(file.path(path_results,"radius_to_mean_cluster_size.png"))
 	png(file=output_file, units="cm", width=21, height=21, res=300)
-	#SM: convert factor to numeric
+	# convert factor to numeric
 	mean_clust_size_values <- as.numeric(as.character(analysis_by_radius$mean_clust_size))
 	plot(radius_vals,mean_clust_size_values ,
 	     main=paste("Mean cluster size vs radius "),
 	     sub=paste("Source File: ",source_file_name),
 	     xlab=paste("radius ", unit_text),
 	     ylab="mean cluster size", type="b")
-#	textxy(analysis_by_radius$radius,analysis_by_radius$mean_clust_size,analysis_by_radius$radius, col="red", cex=.8)
[…]

### 2020-01-20 R/percolate.R
removed duplicate code

@@ -250,27 +250,6 @@ write.csv(mem_clust_by_r,file_name,quote=FALSE,row.names=FALSE)
 # subtract 1 for header line
 total_nodes <- nrow(data) -1
 
-#### SOPHIE I THINK THE CODE BELOW TO THE NEXT SUCH COMMENT IS REDUNDANT???
-if (radius_unit == 1)
-{unit_text <- "m"
-} else if (radius_unit == 1000)
-{unit_text <- "km"
-} else {
-  unit_text <- paste(radius_unit, "m", sep="")}
-
-
-radius_values <- seq(upper_radius,lower_radius,by=-step_value)
-# Changes to accomodate non-integer radius values
-radii_count <- length(radius_values)
-loop_count <- seq(radii_count,1,by=-1)
-
-
-file_name <- paste(file.path(path_results, "member_cluster_by_radius.csv"))
-
-mem_clust_by_r <- read.csv(file_name, header = TRUE)
-### IE DOWN TO THIS POINT. I THINK ALL THIS CODE FROM ABOVE IS DUPLICATE???
-
-
 # Create matrix of number of clusters and number of nodes (max, mean, median), for each radius
 # Columns:  Radius, number of clusters, max cluster size, mean cluster size, median cluster size
 col_list <- cbind('radius','num_clust','max_clust_size','max_normalized','mean_clust_size','median_clust_size')

### 2020-01-20 R/percolate.R
removed a SM

@@ -5,7 +5,7 @@
 ##' E. Arcaute, C. Molinero, E. Hatna, R. Murcio, C. Vargas-Ruiz, A.P. Masucci and M. Batty. Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. doi:10.1098/rsos.150691, 2016. 
 ##' 
 ##' It creates a file structure in which working data and analysis results are saved
-##' input data required, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header. A distance table with the headers 'ID1','ID2','d12' SM: may be used if a computation of the euclidean distance between points is not required. 
+##' input data required, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header. A distance table with the headers 'ID1','ID2','d12' may be used if a computation of the euclidean distance between points is not required. 
 ##' input of radius values needed 
 ##' NOTE that if the distance table option is used the Spatial dataframe MUST ALSO BE PROVIDED for the mapping!
 ##' both file types need to be comma delimited!

### 2020-04-21 R/mapClusters.v.2.2.R
new versions of functions

@@ -1,8 +1,14 @@
 ##' Map clusters
 ##' 
-##' This is a function built based on the script mapping_clusters.v4.12
-##' by Simon Maddison
-##' it creates a folder maps, where output is saved as png
+##' This function will map the clusters created by percolation. It needs the following input:
+##' *mapClusters(shape, map_name, source_file_name, dpi=300)*
+##' **shape** is a SpatialPolygonDataFrame (sp), which will be used for plotting as a background map, and determining the coordinate system.
+##' **map_name** is a string, which will be used to title the maps.
+##' **source_file_name** is a string, which will be used in a subtitle within the maps and should describe the source data used.
+##' **dpi** is the output file resolution. The default is set to 300. Other resolutions may be needed for publication, for example.
+##' **Exported** maps are in the folder /maps: As many png map files as there are different radii values used in the percolation analysis. Also a shp-file with the point data.
+##' For more information and a code and data example please check the vignette.
+##'
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt
 #' @import sp
@@ -35,7 +41,7 @@ path_results <- file.path(getwd(), "analysis_results")
 path_maps <- file.path(getwd(), "maps")
 dir.create(path_maps, showWarnings = FALSE)
 
-# read in nodes list
+# read in nodes list and coordinates
 data_file <- paste(file.path(path_working,"nodes_list_d.txt"))
 
 # Read in distance thresholds - this ensures same values used as in clustering script, where it was saved
@@ -83,7 +89,7 @@ if (radius_unit == 1)
 unit_text <- paste(radius_unit, "m", sep="")}
 
 radius_values <- seq(upper_radius,lower_radius,by=-step_value)
-# Changes to accomodate non-integer radius values
+# this accomodates non-integer radius values
 radii_count <- length(radius_values)
 loop_count <- seq(radii_count,1,by=-1)
 
@@ -91,7 +97,8 @@ loop_count <- seq(radii_count,1,by=-1)
 top15_colours <- colors()[c(553,29,258,654,91,115,456,122,48,8,149,86,102,40,12)]
 the_rest_colour <- "#AEAEAE"
 
-# this code can be used to plot all sites as pdf as an alternative
+# this code can be used to plot all outputs as pdf as an alternative
+# this code would need to be substiuted for the png plot code below, and in the for loop
 # Maps plotted on multipage pdf
[…]

### 2020-04-21 R/percolate.v2.3.R

@@ -1,17 +1,35 @@
 ##' Percolation
 ##' 
-##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and cluster_frequency_script.v2.17 
-##' by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under :  
-##' E. Arcaute, C. Molinero, E. Hatna, R. Murcio, C. Vargas-Ruiz, A.P. Masucci and M. Batty. Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. doi:10.1098/rsos.150691, 2016. 
+##' This is a function built based on the scripts by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under:  
+##' E.Arcaute, C.Molinero, E.Hatna, R.Murcio, C.Vargas-Ruiz, A.P.Masucci and M.Batty. 
+##'  Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. 
+##'  doi:10.1098/rsos.150691, 2016. 
 ##' 
-##' It creates a file structure in which working data and analysis results are saved
-##' input data required, which consists of a dataframe with the PLCINDEX, EASTING, NORTHING - header. A distance table with the headers 'ID1','ID2','d12' may be used if a computation of the euclidean distance between points is not required. 
-##' input of radius values needed 
-##' NOTE that if the distance table option is used the Spatial dataframe MUST ALSO BE PROVIDED for the mapping!
-##' both file types need to be comma delimited!
-##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
-##' output in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
-##' both output-folders will be used by following functions
+##' The input needed for the percolate-function is as follows: 
+##' _percolate(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value)_
+##' **data** = A data.frame, with the format and example data below:
+##' PlcIndex,Easting,Northing
+##' 1,350350,233050
+##' 2,354700,260200
+##' 3,358700,238900
+##' *PlcIndex* is an assigned index number to distinguish the points. This does not need to be sequential and can for example be drawn from a source database.
+##' *Easting* and *Northing* are self-explanatory, and are to the metre. (Note that additional columns, if any, will be ignored).
[…]

### 2020-04-21 R/plotClustFreq.v2.2.R

@@ -1,12 +1,17 @@
 #' Plot Cluster Frequency
 #'
-#' based on CLUSTER FREQENCY PLOTTING SCRIPTv2.17 by Simon Maddison, 10th May 2015
-#' This script extracts cluster frequency data and plots it for a range of percolation radii
-#' The data is in the analysis_results-directory in text files created by the nodes_clust_freq-function;
-#' 	each file is a list of Place indices, with the identity of each cluster
-#' 	which it is a member of.
-#' 	radius-values have been stored in the working_data-directory.
-#' 	output will be put into /analysis_results
+#' Percolation cluster size and rank analyses – this program processes the cluster data generated by the cluster extraction program to give various different frequency and ranking plots. 
+#' *plotClutsFreq(source_file_name)*
+#' **source_file_name** is a string, which will be used to label the plots and describes the source data set. If already input in mapClusters this doesn’t need to be done again. 
+#' Three png-files are generated:
+#' a) radius to maximum cluster size, 
+#' b) radius to mean cluster size and 
+#' c) radius to normalized max. cluster size
+
+#' and they will include the information of the source file as a subtitle.
+#' They are stored as png files in the /analysis_results directory as “radius_to_max_cluster_size”, “radius_to_mean_cluster_size” and “radius_to_norm_max_cluster_size”.
+#' For more information and a code and data example please check the vignette.
+
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt
 #' 
@@ -17,7 +22,8 @@
 #' @import graphics
 #' @import utils
 #' @param source_file_name needs input of source file name for plotting
-#' @return plotClustFreq 3 plots of radius to maximum cluster size, radius to mean cluster size and radius to normalized max. cluster size
+#' @return three plots of radius to maximum cluster size, radius to 
+#'  mean cluster size and radius to normalized max. cluster size
 #' 
 #' @export plotClustFreq
 #'
@@ -34,7 +40,6 @@ file_name <- paste(file.path(path_results,"analysis_by_radius.csv"))
 analysis_by_radius <- read.csv2(file_name,sep=",")
 
 # load source_file_name from mapClusters, if it was saved there. Otherwise use input
-
 
 if ( file.exists(file.path(path_working, "source_file_name_out.csv"))) {
 source_file_name <- read.csv(file.path(path_working, "source_file_name_out.csv"), sep = " ")

### 2020-04-21 README.Rmd
Update README.Rmd
uups
gave DOI
DOI 10.17605/OSF.IO/7EXTC
more information in readme

@@
 
-# percolatransect
+# percopackage
 
-The goal of percopackage is to create functions for the percolation analysis from Simon Maddison's scripts.
+Percolation Analysis as implemented here is a 2D point pattern analysis technique for identifying clusters of any size and form. It recognises noise and produces repeatable result.
+
+Recently the algorithm has been used in geography to identify metropolitan areas, based on population density.
+The City Clustering Algorithm (CCA) has been developed out of percolation theory by Rozenfeld et al.
+(2008) based on distance within a cellular lattice; it has been further developed by Rozenfeld et al.
+(2011) to use the Euclidean distance between points.
+The algorithm implemented here is based on Arcaute et al.
+(2016), who adopted the technique for defining urban areas, using the density of street interconnections rather than population.
+
+A cluster consists of at least two points.
+Around each point in the given set a defined distance threshold is drawn as a radius and all points falling within this threshold are connected to the cluster.
+The test is then re-applied for each of these neighbours in turn, and any further points meeting this criterion are also part of the cluster.
+This technique can be applied at any scale, from the molecular to the geographical and beyond.
+The implementation here can therefore use radius values of decimal meters and kilometers.
+
+The algorithm has been implemented as an exploratory  tool, meaning that in the percolate-function a set of radii is defined (values from, values to, and step values), for which the percolation is run.
+The results can be compared via maps (mapClusters-function) and graphs (plotClustFreq-function).
+
+Two archaeological case studies using this algorithm and software package are to be published by Maddison & Schmidt 2020.
 
@@
 
-You can install percolatransect from github with:
+You can install percopackage from github with:
 

### 2020-04-21 README.Rmd
readme is now old vignette

@@
 
+## Percolation Analysis via the R package “percopackage” – Workflow and Descriptions
+
+Percopackage is an R-package, which takes scripts developed by Simon Maddison and Elsa Arcaute to create three functions, which perform
+
+  a) the actual percolation analysis (function called “percolate”), 
+  b) maps the clusters created by percolation (function “mapClusters”) and 
+  c) creates three different plots of the analysis results (function “plotClustFreq”)
+
+The percolate function does the actual computing of the percolation analysis and exports different tables on which the following functions operate. 
+Two different data inputs are possible: A set of points in Euclidian space, for which a distance matrix will be calculated OR a distance matrix, which may for example have been calculated using least cost paths.
+If a distance matrix is provided, the point set is still needed for the mapping function.
+
+### Directory Structure
+The functions create subdirectories of the working directory the user is working in (using getwd() ), therefore we describe here the relative structure, which is being set up:
+
+  * /analysis_results – output plots from the analysis, now principally the cluster size vs radius plots and the csv of the analyis results (described further down)
+
+  * /maps – outputs from the mapping, showing clusters and nodes overlaid on given outline shape files, as well as output shape files with the point data (shape file called “map_name.shp”)
+
+  * /working_data – working data generated by the programs and used to pass intermediate data between them.
+
+### Percolate - function
+The input needed for the percolate-function is as follows:
+
+_percolate(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value)_
+
+**data** = A data.frame, with the format below:
+
+PlcIndex,Easting,Northing
+
+1,350350,233050
+
+2,354700,260200
+
+3,358700,238900
+
+*PlcIndex* is an assigned index number to distinguish the points. This does not need to be sequential and can for example be drawn from a source database.
+
+*Easting* and *Northing* are self-explanatory, and are to the metre. (Note that additional columns, if any, will be ignored).
+
+**distance_table** is set to be NULL as a default, which means, from the data input (coordinates) a distance matrix is calculated using Euclidean distance.
+If not NULL, the data frame given here needs to adhere to this format:
+
+ID1, ID2, d12
+
+1,2,12.1
+
+1,3,14.2
+
+2,3,2.9
+
+*ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and
+
+*d12* denotes the weighted distance between them, if a non-euclidian distance is whished to be used.
+
+**limit** is an integer, the value above which distances will not be calculated between sites.
+
+**radius_unit**  is either 1 for meter or 1000 for km for all input radii.
+
+**upper_radius** is an integer, the upper value of the radius range to be used.
+
+**lower_radius** is an integer, the lower value of the radius range to be used.
+
+**step_value** is numeric or integer and the step value to be used between lower and upper radius.
+
+**Exported** are in the folder *working_data*: tables (csv) with the input-data, the list of PlcIndex, null_entries and duplicate_entries to be used by following functions.
+
+In the folder *analysis_results* the tables (csv) analysis_by_radius and member_cluster_by_radius are exported.
+They will be used by the following functions as well, but may be useful for other applications as well, therefore they are considered analysis results.
+
+#### Note 
+The function creates the Inter-site distance matrix – given the dataset of sites and XY coordinates, this computes a partial matrix of inter-site distances.
+The limit is set by the **limit** parameter in the function call.
+The inter-site distance is computed using Pythagoras’ theorem.
+The output file is located in */working_data* and is called: nodes_list_d.txt.
+See below for examples and explanation of the limit parameter.
+
+It also creates a file listing the nodes that have been used in creating this list, which omits duplicates and null values etc. This is called PlcIndex.csv.
+
+Cluster extraction is the second step: This program identifies all clusters for a specific radius.
+It steps through a range of radii, the range being set by input-parameters.
+The data is output as a text csv file called: member_cluster_by_radius.csv.
+This program is the heart of the analysis; the method of creating a graph where nodes are connected when the distance between them is the given radius or less, then extracting each cluster, remains as written by Elsa Arcaute.
+
+Note that for large numbers of points, and large number of selected radius values, the computation time can be quite long.
+We recommend experimenting initially with only a small number of steps, e.g.
+with a small radius range, or with a large step value, in order to see which range of values is the most interesting.
+
+For Hillforts in Britain, Simon Maddison ran the analysis with 1 km steps between 2 and 40km, but also ran an analysis for 3-6km with 0.1km steps to investigate clusters in high density areas of Scotland and Wales.
+To run with 0.1km steps over the full range would not only take excessive time but also produce large numbers of very similar plots.
+
+Duplicate and null entries are also listed in files with these names, but should have no values if the data is clean.
+(Historically there was a lot of cleaning to do, which is why this runs as a separate program).
+
+#### Example:
+
+*percolate(data = database,, limit = 50, radius_unit = 1000, upper_radius = 40, lower_radius = 2, step_value = 1)*
+
+A coordinates dataset is the database input.
+In the example above, percolation analysis will run for radius values between 40 and 2 km, with a step value of 1km (determined by the radius_unit parameter, set to 1000).
+When computing the inter-site distances, values greater than 50km will not be stored.
+This restricts the intermediate file size and improves performance.
+(There is no point in computing the distance between sites in Scotland and Cornwall for example, when all sites are within a single cluster above a radius of say 40km).
+
+### mapClusters - function
+
+This function will map the clusters created by percolation. It needs the following input:
+
+*mapClusters(shape, map_name, source_file_name, dpi=300)*
+
+**shape** is a SpatialPolygonDataFrame (sp), which will be used for the plotting as a background map, and determining the coordinate system.
+
+**map_name** is a string, which will be used to title the maps.
+
+**source_file_name** is a string, which will be used to label the maps and describes the source data used.
+
+**dpi** is the output file resolution. The default is set to 300.
+
+**Exported** maps are in the folder /maps: As many png map files as there are different radii values used in the percolation analysis. Also a shp-file with the point data.
+
+#### Note
+Mapping clusters – this function maps clusters for each radius on an outline map overlay.
+The same data can for example be mapped on a coastal outline, an outline with modern counties, or an outline with historic counties.
+The outline is defined by an ESRI shape file, which needs to be read, and passed to the function as an appropriate data frame.
+The outputs generated were originally a multi-page pdf file, but this proved unwieldy, and it was changed to generate png files, which are much easier to import into Microsoft Word and other applications, as well as to display.
+Point data is also exported as an ESRI shape file for import directly into ArcGIS etc.
+Outputs are placed in the /maps sub-directory.
+
+Clusters are ranked in order of size for each different threshold radius.
+The top 15 clusters are assigned a colour code with Red the largest, Blue the next and so on.
+A legend is plotted with the assigned cluster number against the colour.
+The plots also include the map name and the name of the source file used to generate the data, as well as the radius value.
+
+The map projection is extracted from the given shape file and used for configuring the point plots and output shape files.
+This has not been extensively tested for different projection/ coordinate systems, and may need further development/modification for different input shape files.
+If necessary experiment by omitting the shape file plot by commenting out, and simply plot the points, in the first instance.
+Points and shp need to have the same coordinate system and projection.
+
+#### Example
+
+*mapClusters(data = database, shape = outline_GB, map_name = “Britain Iron Age Hillforts”, source_file_name = “Hillfort Sites”)*
+
+The output-maps will be called e.g.
+“percolation_plots_Britain Iron Age Hillforts_rad_40.png” (number changing regarding to which percolation radius is depicted).
+On top of the map, the title will be: “Britain Iron Age Hillforts” and it will have a subtitle with a string like: “Source File: Hillfort Sites, percolation distance: 40 km”.
+
+## plotClustFreq - function
+
+Percolation cluster size and rank analyses – this program processes the cluster data generated by the cluster extraction program to give various different frequency and ranking plots.
+
+*plotClutsFreq(source_file_name)*
+
+**source_file_name** is a string, which will be used to label the plots and describes the source data set. If already input in mapClusters this doesn’t need to be done again.
+
+Three png-files are generated:
+
+  a) radius to maximum cluster size, 
+  b) radius to mean cluster size and 
+  c) radius to normalized max. cluster size
+
+and they will include the information of the source file as a subtitle.
+
+At the moment they are stored in the /analysis_results directory as “radius_to_max_cluster_size”, “radius_to_mean_cluster_size” and “radius_to_norm_max_cluster_size”.
+
+#### Note
+
+This program evolved significantly as various different statistical analyses were experimented with, under the guidance of Mark Lake.
+The final version reflects the latest work by Elsa Arcaute.
+The outputs are placed in the /analysis_results sub-directory.
+The most useful plot is the cluster transition plot, showing the maximum cluster size (normalized) vs. radius, which shows the transitions.
+
+### CONTACT DETAILS:
+Simon Maddison
+simon.maddison@btinternet.com
++44 797 089 2171
+
+Sophie C. Schmidt
+s.c.schmidt@uni-koeln.de
+
+# Bibliography
+
+Arcaute, E., Molinero, C., Hatna, E., Murcio, R., Vargas-Ruiz, C., Masucci, A P & Batty, M 2016 Cities and regions in Britain through hierarchical percolation.
+Royal Society Open Science, 3 (4): 150691.DOI: 10.1098/rsos.150691
+
+Rozenfeld, H.
+D., Rybski, D., Andrade, J.
+S., Batty, M., Stanley, H.
+E.
+& Makse, H.
+A.
+2008, Laws of population growth.
+Proceedings of the National Academy of Sciences of the United States of America, 105 (48): 18702.DOI: 10.1073/pnas.0807435105
+
+Rozenfeld, H. D., Rybski, D., Gabaix, X. & Makse, H. A. 2011, The Area and Population of Cities: New Insights from a Different Perspective on Cities. American Economic Review 101 (5): 2205-25.
+
 ### Citation

### 2020-04-21 R/example_data.R
data for example.

@@ -1,0 +1,28 @@
+#' Atlas of Hillforts of Britain and Ireland data plus shapefile
+#'
+#' 
+#' The example point coordinate data is taken from the:
+#' Atlas of Hillforts of Britain and Ireland 
+#' Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
+#' This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License
+#' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017
+#' The example shape file is an outline of Britain, taken from: 
+#' Ordnance Survey OS Open Data, uner a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
+#' This file Contains OS data © Crown Copyright (2020)
+#' For example of usage, please see the vignette.
+
+
+#'
+#' @docType data
+#'
+#' @usage data(data)
+#'
+#' @format One object of class \code{"Large SpatialPolygonsDataFrame"} called "shape"; two objects  of class \code{"Dataframe"} called "data" and "distance_table"
+#'
+#' @keywords datasets
+#'
+#' @references Atlas of Hillforts of Britain and Ireland, Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
+#' @references Ordnance Survey OS Open Data, uner a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
+#'
+#'
+"data"

### 2020-04-21 R/example_distance_table.R
more data documentation files.

@@ -1,22 +1,24 @@
-#' Atlas of Hillforts of Britain and Ireland data 
+#' Atlas of Hillforts of Britain and Ireland data: distance table
 #' 
-#' The example point coordinate data is taken from the:
+#' The example distance table is the square root of the point coordinate data taken from the:
 #' Atlas of Hillforts of Britain and Ireland 
 #' Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #' This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License
 #' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017
-
+#' 
 #' For example of usage, please see the vignette.
 
+
+#'
 #' @docType data
 #'
 #' @usage data(data)
 #'
-#' @format Object of class \code{"Dataframe"} called "data" 
+#' @format Object of class \code{"Dataframe"} called "distance_table" 
 #'
 #' @keywords datasets
 #'
 #' @references Atlas of Hillforts of Britain and Ireland, Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #'
 #'
-"data"
+"distance_table"

### 2020-04-21 R/example_shape.R

@@ -1,0 +1,21 @@
+#' Shapefile: Outline of Great Britain
+#'
+#' 
+#' Ordnance Survey OS Open Data, uner a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
+#' This file Contains OS data © Crown Copyright (2020)
+#' For example of usage, please see the vignette.
+
+
+#'
+#' @docType data
+#'
+#' @usage data(data)
+#'
+#' @format Object of class \code{"Large SpatialPolygonsDataFrame"} called "shape
+#'
+#' @keywords datasets
+#'
+#' @references Ordnance Survey OS Open Data, uner a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
+#'
+#'
+"shape"

### 2020-04-21 R/percolate.v2.3.R
update order of parameters to be consistent to documentation

@@ -21,11 +21,12 @@
 ##' 2,3,2.9
 ##' *ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and 
 ##' *d12* denotes the weighted distance between them, if a non-euclidian distance is to be used. 
-##' **limit** is an integer, the value above which distances will not be calculated between sites.
-##' **radius_unit**  is either 1 for meter or 1000 for km for all input radii.
 ##' **upper_radius** is an integer, the upper value of the radius range to be used.
 ##' **lower_radius** is an integer, the lower value of the radius range to be used.
 ##' **step_value** is numeric or integer and the step value to be used between lower and upper radius.
+##' **limit** is an integer, the value above which distances will not be calculated between sites.
+##' **radius_unit**  is either 1 for meter or 1000 for km for all input radii.
+##' 
 ##' **Exported** are in the folder *working_data*: tables (csv) with the input-data, the list of PlcIndex, null_entries and duplicate_entries to be used by following functions.
 ##' In the folder *analysis_results* the tables (csv) analysis_by_radius and member_cluster_by_radius are exported. They will be used by the following functions as well, but may also be useful for other applications, therefore they are considered analysis results.
 
@@ -42,15 +43,15 @@
 
 #' @param data needs input of dataframe as specified above
 #' @param distance_table to give a distance matrix instead of calculating one. Default is NULL, and Euclidean distance will be calculated from the given point data.
-#' @param limit needs input of integer: is the value above which distances between sites will not be stored
-#' @param radius_unit is either 1 for meter or 1000 for km; applied to all input values
 #' @param upper_radius needs input of integer, is the upper value of the radius range to be used
 #' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
 #' @param step_value integer or numeric, is the step value to be used between these two values
+#' @param limit needs input of integer: is the value above which distances between sites will not be stored
+#' @param radius_unit is either 1 for meter or 1000 for km; applied to all input values
 #' @return the function generates the data files analysis_by_radius.csv and member_cluster_by_radius.csv
 #' @export
 
-percolate <- function(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value) {
+percolate <- function(data, distance_table = NULL, upper_radius, lower_radius, step_value, limit, radius_unit) {
 
 # create directories
 # file.path creates paths according to working directory used on user's computer

### 2020-04-21 R/example_data.R
changed example data set names. better designed the help manuals for functions
rewrote vignette accordingly

@@ -12,11 +12,11 @@
 #'
 #' @usage data(data)
 #'
-#' @format Object of class \code{"Dataframe"} called "data" 
+#' @format Object of class \code{"Dataframe"} called "hillforts" 
 #'
 #' @keywords datasets
 #'
 #' @references Atlas of Hillforts of Britain and Ireland, Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #'
 #'
-"data"
+"hillforts"

### 2020-04-21 R/example_distance_table.R

@@ -14,11 +14,11 @@
 #'
 #' @usage data(data)
 #'
-#' @format Object of class \code{"Dataframe"} called "distance_table" 
+#' @format Object of class \code{"Dataframe"} called "hillfort_distances" 
 #'
 #' @keywords datasets
 #'
 #' @references Atlas of Hillforts of Britain and Ireland, Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #'
 #'
-"distance_table"
+"hillfort_distances"

### 2020-04-21 R/example_shape.R

@@ -11,11 +11,11 @@
 #'
 #' @usage data(data)
 #'
-#' @format Object of class \code{"Large SpatialPolygonsDataFrame"} called "shape
+#' @format Object of class \code{"Large SpatialPolygonsDataFrame"} called "GB_shape"
 #'
 #' @keywords datasets
 #'
 #' @references Ordnance Survey OS Open Data, uner a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
 #'
 #'
-"shape"
+"GB_shape"

### 2020-04-21 R/mapClusters.v.2.2.R

@@ -1,12 +1,17 @@
 ##' Map clusters
 ##' 
-##' This function will map the clusters created by percolation. It needs the following input:
-##' *mapClusters(shape, map_name, source_file_name, dpi=300)*
-##' **shape** is a SpatialPolygonDataFrame (sp), which will be used for plotting as a background map, and determining the coordinate system.
-##' **map_name** is a string, which will be used to title the maps.
-##' **source_file_name** is a string, which will be used in a subtitle within the maps and should describe the source data used.
-##' **dpi** is the output file resolution. The default is set to 300. Other resolutions may be needed for publication, for example.
-##' **Exported** maps are in the folder /maps: As many png map files as there are different radii values used in the percolation analysis. Also a shp-file with the point data.
+##' This function will map the clusters created by percolation. 
+##' 
+##' shape is a SpatialPolygonDataFrame (sp), which will be used for plotting as a background map, and determining the coordinate system.
+##' 
+##' map_name is a string, which will be used to title the maps.
+##' 
+##' source_file_name is a string, which will be used in a subtitle within the maps and should describe the source data used.
+##' 
+##' dpi is the output file resolution. The default is set to 300. Other resolutions may be needed for publication, for example.
+##' 
+##' Exported maps are in the folder "/maps": As many png map files as there are different radii values used in the percolation analysis. Also a shp-file with the point data.
+##' 
 ##' For more information and a code and data example please check the vignette.
 ##'
 #' @author Simon Maddison

### 2020-04-21 R/percolate.v2.3.R

@@ -5,30 +5,49 @@
 ##'  Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. 
 ##'  doi:10.1098/rsos.150691, 2016. 
 ##' 
-##' The input needed for the percolate-function is as follows: 
-##' _percolate(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value)_
-##' **data** = A data.frame, with the format and example data below:
-##' PlcIndex,Easting,Northing
-##' 1,350350,233050
-##' 2,354700,260200
-##' 3,358700,238900
-##' *PlcIndex* is an assigned index number to distinguish the points. This does not need to be sequential and can for example be drawn from a source database.
-##' *Easting* and *Northing* are self-explanatory, and are to the metre. (Note that additional columns, if any, will be ignored).
-##' **distance_table** is set to be NULL as a default, which means, using the data input (coordinates) a distance matrix is calculated using Euclidean distance. If not NULL, the data frame given here needs to adhere to this format and example values:
-##' ID1, ID2, d12
-##' 1,2,12.1
-##' 1,3,14.2
-##' 2,3,2.9
-##' *ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and 
-##' *d12* denotes the weighted distance between them, if a non-euclidian distance is to be used. 
-##' **upper_radius** is an integer, the upper value of the radius range to be used.
-##' **lower_radius** is an integer, the lower value of the radius range to be used.
-##' **step_value** is numeric or integer and the step value to be used between lower and upper radius.
-##' **limit** is an integer, the value above which distances will not be calculated between sites.
-##' **radius_unit**  is either 1 for meter or 1000 for km for all input radii.
 ##' 
-##' **Exported** are in the folder *working_data*: tables (csv) with the input-data, the list of PlcIndex, null_entries and duplicate_entries to be used by following functions.
-##' In the folder *analysis_results* the tables (csv) analysis_by_radius and member_cluster_by_radius are exported. They will be used by the following functions as well, but may also be useful for other applications, therefore they are considered analysis results.
+##' data = A data.frame, with the format and example data below:
+##' 
+##' PlcIndex,Easting,Northing
+##' 
+##' 1,350350,233050
+##' 
+##' 2,354700,260200
+##' 
+##' 3,358700,238900
+##' 
+##' PlcIndex is an assigned index number to distinguish the points. This does not need to be sequential and can for example be drawn from a source database.
+##' 
[…]

### 2020-04-21 R/plotClustFreq.v2.2.R

@@ -1,15 +1,23 @@
 #' Plot Cluster Frequency
 #'
-#' Percolation cluster size and rank analyses – this program processes the cluster data generated by the cluster extraction program to give various different frequency and ranking plots. 
-#' *plotClutsFreq(source_file_name)*
-#' **source_file_name** is a string, which will be used to label the plots and describes the source data set. If already input in mapClusters this doesn’t need to be done again. 
+#' Percolation cluster size and rank analyses 
+#' – this program processes the cluster data generated by the cluster extraction program to give various different frequency and ranking plots. 
+#' 
+#' **source_file_name** is a string, which will be used to label the plots and describes the source data set. 
+#' If already input in mapClusters this doesn’t need to be done again. 
+#' 
 #' Three png-files are generated:
+#' 
 #' a) radius to maximum cluster size, 
+#' 
 #' b) radius to mean cluster size and 
+#' 
 #' c) radius to normalized max. cluster size
 
 #' and they will include the information of the source file as a subtitle.
+#' 
 #' They are stored as png files in the /analysis_results directory as “radius_to_max_cluster_size”, “radius_to_mean_cluster_size” and “radius_to_norm_max_cluster_size”.
+#' 
 #' For more information and a code and data example please check the vignette.
 
 #' @author Simon Maddison

### 2020-04-21 README.Rmd
added vignette information + renamed vignette to be easier found
corrected order of parameters in readme

@@
 
-_percolate(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value)_
+_percolate(data, distance_table = NULL, upper_radius, lower_radius, step_value, limit, radius_unit)_
 
@@
 
-*ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and
-
-*d12* denotes the weighted distance between them, if a non-euclidian distance is whished to be used.
-
-**limit** is an integer, the value above which distances will not be calculated between sites.
-
-**radius_unit**  is either 1 for meter or 1000 for km for all input radii.
+*ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and *d12* denotes the weighted distance between them, if a non-euclidian distance is whished to be used.
 
@@
 **step_value** is numeric or integer and the step value to be used between lower and upper radius.
+
+**limit** is an integer, the value above which distances will not be calculated between sites.
+
+**radius_unit**  is either 1 for meter or 1000 for km for all input radii.
 
@@
 
-*percolate(data = database,, limit = 50, radius_unit = 1000, upper_radius = 40, lower_radius = 2, step_value = 1)*
+*percolate(data = database,, upper_radius = 40, lower_radius = 2, step_value = 1, limit = 50, radius_unit = 1000)*
 

### 2020-04-21 R/example_data.R

@@ -4,9 +4,9 @@
 #' Atlas of Hillforts of Britain and Ireland 
 #' Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #' This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License
-#' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017
+#' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017.
 
-#' For example of usage, please see the vignette.
+#' For example of usage, please see the vignette "percolation".
 
 #' @docType data
 #'

### 2020-04-21 R/example_distance_table.R

@@ -4,9 +4,9 @@
 #' Atlas of Hillforts of Britain and Ireland 
 #' Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #' This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License
-#' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017
+#' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017.
 #' 
-#' For example of usage, please see the vignette.
+#' For example of usage, please see the vignette "percolation".
 
 
 #'

### 2020-04-21 R/example_shape.R

@@ -1,9 +1,10 @@
 #' Shapefile: Outline of Great Britain
 #'
 #' 
-#' Ordnance Survey OS Open Data, uner a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
+#' Ordnance Survey OS Open Data, under a UK Open Government Licence: https://www.ordnancesurvey.co.uk/opendatadownload/products.html#OVERGB
 #' This file Contains OS data © Crown Copyright (2020)
-#' For example of usage, please see the vignette.
+#' 
+#' For example of usage, please see the vignette "percolation".
 
 
 #'

### 2020-04-21 R/mapClusters.v.2.2.R

@@ -12,7 +12,7 @@
 ##' 
 ##' Exported maps are in the folder "/maps": As many png map files as there are different radii values used in the percolation analysis. Also a shp-file with the point data.
 ##' 
-##' For more information and a code and data example please check the vignette.
+##' For more information and a code and data example please check the vignette "percolation".
 ##'
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt

### 2020-04-21 R/percolate.v2.3.R

@@ -49,7 +49,7 @@
 ##' In the folder "analysis_results" the tables (csv) analysis_by_radius and member_cluster_by_radius are exported. 
 ##' They will be used by the following functions as well, but may also be useful for other applications, therefore they are considered analysis results.
 
-##' For more information and a code and data example please check the vignette.
+##' For more information and a code and data example please check the vignette "percolation".
 
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt

### 2020-04-21 R/plotClustFreq.v2.2.R

@@ -3,7 +3,7 @@
 #' Percolation cluster size and rank analyses 
 #' – this program processes the cluster data generated by the cluster extraction program to give various different frequency and ranking plots. 
 #' 
-#' **source_file_name** is a string, which will be used to label the plots and describes the source data set. 
+#' source_file_name is a string, which will be used to label the plots and describes the source data set. 
 #' If already input in mapClusters this doesn’t need to be done again. 
 #' 
 #' Three png-files are generated:
@@ -18,7 +18,7 @@
 #' 
 #' They are stored as png files in the /analysis_results directory as “radius_to_max_cluster_size”, “radius_to_mean_cluster_size” and “radius_to_norm_max_cluster_size”.
 #' 
-#' For more information and a code and data example please check the vignette.
+#' For more information and a code and data example please check the vignette "percolation".
 
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt

### 2020-04-27 R/percolate.v2.4.R
updated to Simons clearer version + tried around with importfrom

@@ -1,76 +1,43 @@
 ##' Percolation
 ##' 
-##' This is a function built based on the scripts by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under:  
+##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and 
+##'  cluster_frequency_script.v2.17 
+##' by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under:  
 ##' E.Arcaute, C.Molinero, E.Hatna, R.Murcio, C.Vargas-Ruiz, A.P.Masucci and M.Batty. 
 ##'  Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. 
 ##'  doi:10.1098/rsos.150691, 2016. 
 ##' 
+##' It creates a file structure in which working data and analysis results are saved
 ##' 
-##' data = A data.frame, with the format and example data below:
-##' 
-##' PlcIndex,Easting,Northing
-##' 
-##' 1,350350,233050
-##' 
-##' 2,354700,260200
-##' 
-##' 3,358700,238900
-##' 
-##' PlcIndex is an assigned index number to distinguish the points. This does not need to be sequential and can for example be drawn from a source database.
-##' 
-##' Easting and Northing are self-explanatory, and are to the metre. (Note that additional columns, if any, will be ignored).
-##' 
-##' distance_table is set to be NULL as a default, which means, using the data input (coordinates) a distance matrix is calculated using Euclidean distance. If not NULL, the data frame given here needs to adhere to this format and example values:
-##' 
-##' ID1, ID2, d12
-##' 
-##' 1,2,12.1
-##' 
-##' 1,3,14.2
-##' 
-##' 2,3,2.9
-##' 
-##' ID1 and ID2 are point IDs (i.e. the PlcIndex values) and 
-##' 
-##' d12 denotes the weighted distance between them, if a non-euclidian distance is to be used. 
-##' 
-##' upper_radius is an integer, the upper value of the radius range to be used.
-##' 
-##' lower_radius is an integer, the lower value of the radius range to be used.
-##' 
-##' step_value is numeric or integer and the step value to be used between lower and upper radius.
-##' 
-##' limit is an integer, the value above which distances will not be calculated between sites.
-##' 
-##' radius_unit  is either 1 for meter or 1000 for km for all input radii.
-##' 
[…]

### 2020-04-27 R/percolate.v2.4.R
updated information again
importFrom didn't remove warnings, so removed again.

@@ -1,32 +1,64 @@
 ##' Percolation
 ##' 
-##' This is a function built based on the scripts create_nodes_list_d.v4.7, clustering_script.v.3.6 and 
-##'  cluster_frequency_script.v2.17 
-##' by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under:  
+##' This is a function built based on the scripts by Simon Maddison, who based it on code developed by Elsa Arcaute, which is published under:  
 ##' E.Arcaute, C.Molinero, E.Hatna, R.Murcio, C.Vargas-Ruiz, A.P.Masucci and M.Batty. 
 ##'  Cities and Regions in Britain through hierarchical percolation. J. R. Soc. Open Science, 3 (4),150691. 
 ##'  doi:10.1098/rsos.150691, 2016. 
 ##' 
-##' It creates a file structure in which working data and analysis results are saved
 ##' 
-##' The input data required consists of a dataframe with the: PlcIndex, Easting, Northing - header. 
-##' A distance table with the headers 'ID1','ID2','d12' may also be used if a computation of the euclidean distance 
-##'  between points is not needed and an alternative to this is desired. 
-##' Input: radius values need to be passed as parameters 
-##' NOTE: if the distance table option is used the coordinate file MUST ALSO BE PROVIDED for the mapping!
-##' NOTE: both file types need to be comma delimited!
-##' output: in working_data: csv with the radius-input data, PlcIndex, null_entries and duplicate_entries
-##' output: in analysis_results: analysis_by_radius.csv and member_cluster_by_radius.csv
-##' both output-folders will be used by following functions
+##' data = A data.frame, with the format and example data below:
+##' 
+##' PlcIndex,Easting,Northing
+##' 
+##' 1,350350,233050
+##' 
+##' 2,354700,260200
+##' 
+##' 3,358700,238900
+##' 
+##' PlcIndex is an assigned index number to distinguish the points. This does not need to be sequential and can for example be drawn from a source database.
+##' 
+##' Easting and Northing are self-explanatory, and are to the metre. (Note that additional columns, if any, will be ignored).
+##' 
+##' distance_table is set to be NULL as a default, which means, using the data input (coordinates) a distance matrix is calculated using Euclidean distance. If not NULL, the data frame given here needs to adhere to this format and example values:
+##' 
+##' ID1, ID2, d12
+##' 
[…]

### 2020-04-27 R/percolate.v2.4.R
merged the two versions.

@@ -49,7 +49,7 @@
 ##' In the folder "analysis_results" the tables (csv) analysis_by_radius and member_cluster_by_radius are exported. 
 ##' They will be used by the following functions as well, but may also be useful for other applications, therefore they are considered analysis results.
 
-##' For more information and a code and data example please check the vignette.
+##' For more information and a code and data example please check the vignette "percolation".
 
 #' @author Simon Maddison
 #' @author Sophie C. Schmidt
@@ -63,13 +63,13 @@
 #' @param data needs input of dataframe as specified above
 #' @param distance_table to give a distance matrix instead of calculating one. Default is NULL, and Euclidean distance will be calculated from the given point data.
 #' @param limit needs input of integer: is the value above which distances between sites will not be stored
-#' @param radius_unit is either 1 for meter or 1000 for km; applied to all input values
-#' @param upper_radius needs input of integer, is the upper value of the radius range to be used
 #' @param lower_radius  needs input of integer, is the lower value of the radius range to be used
 #' @param step_value integer or numeric, is the step value to be used between these two values
 #' @return the function generates the data files analysis_by_radius.csv and member_cluster_by_radius.csv
+#' @param radius_unit is either 1 for meter or 1000 for km; applied to all input values
+#' @param upper_radius needs input of integer, is the upper value of the radius range to be used
 #' @export
-percolate <- function(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value) {
+percolate <- function(data, distance_table = NULL, upper_radius, lower_radius, step_value, limit, radius_unit) {
 
 # create directories
 # file.path creates paths according to working directory used on user's computer

### 2020-04-28 R/example_distance_table.R
some small typo corrections in help
+ created percopackage.R to have a help page for the whole package

@@ -1,7 +1,8 @@
 #' Atlas of Hillforts of Britain and Ireland data: distance table
 #' 
-#' The example distance table is the square root of the point coordinate data taken from the:
-#' Atlas of Hillforts of Britain and Ireland 
+#' The example distance table is the the actual distance between the point coordinate data taken from the
+#' the data set "hillforts" added to the square root of this distance. 
+#' 
 #' Lock, G. and Ralston, I. 2017.  Atlas of Hillforts of Britain and Ireland. [ONLINE] Available at: https://hillforts.arch.ox.ac.uk
 #' This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License
 #' The point coordinate data was extracted from the database for hillforts in Britain (England, Scotland, Wales and the Isle of Man) which have status of interpretation as "confirmed". This was extracted on: 25/07/2017.

### 2020-04-28 R/mapClusters.v.2.2.R

@@ -26,7 +26,7 @@
 #' @import rgdal
 #' @import raster
 #' @import utils
-#' @param shape needs input of SpatialPolygonDataFrame from 'sp' for background map (same ESPG!)
+#' @param shape needs input of SpatialPolygonDataFrame from 'sp' for background map. This needs to have the same ESPG as the point data!
 #' @param map_name needs string for how the maps shall be named
 #' @param source_file_name string for the name of data set used, to include on maps
 #' @param dpi dots per inch for the images. set to 300 as standard

### 2020-04-28 R/percolate.v2.4.R

@@ -60,7 +60,7 @@
 #' @import utils
 #' @import igraph
 
-#' @param data needs input of dataframe as specified above
+#' @param data needs input of data.frame as specified below
 #' @param distance_table to give a distance matrix instead of calculating one. Default is NULL, and Euclidean distance will be calculated from the given point data.
 #' @param limit needs input of integer: is the value above which distances between sites will not be stored
 #' @param lower_radius  needs input of integer, is the lower value of the radius range to be used

### 2020-04-28 R/percopackage.R

@@ -1,0 +1,31 @@
+#' percopackage: A package for percolation analysis as a 2D spatial clustering algorithm
+#'
+#'Three functions are implemented in this package:
+#'
+#'@section percolate():
+#'This function processes this data set to generate the 
+#'clusters for a range of percolation radius values. 
+#'It also generates and stores a set of data tables for 
+#'use by the other functions, as well as optional external 
+#'processing. For details see \code{\link{percolate}}
+#'
+#'@section mapClusters(): 
+#'which allows for the mapping of the 
+#'clusters together with a shape file as a background. For details see 
+#' \code{\link{mapClusters}}
+#'
+#'@section plotClustFreq(): 
+#'which plots three different analyses an png files:
+#'
+#'a) radius to maximum cluster size, 
+#'
+#'b) radius to mean cluster size and 
+#'
+#'c) radius to normalized max. cluster size. 
+#'
+#'For details see \code{\link{plotClustFreq}}
+#'    
+#'
+#' @docType package
+#' @name percopackage
+NULL

### 2020-04-28 R/plotClustFreq.v2.2.R

@@ -13,7 +13,7 @@
 #' b) radius to mean cluster size and 
 #' 
 #' c) radius to normalized max. cluster size
-
+#'
 #' and they will include the information of the source file as a subtitle.
 #' 
 #' They are stored as png files in the /analysis_results directory as “radius_to_max_cluster_size”, “radius_to_mean_cluster_size” and “radius_to_norm_max_cluster_size”.
